### 2015-03-11 main.tex
Initial version: Ashish report
With just a pinch of cleaning

\documentclass{acm_proc_article-sp}

\usepackage{graphicx} 
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{url}

\graphicspath{{figs/}}

\begin{document}

\title{Eye-tracking measures for Anthropomorphism in Human Robot Interaction}

\numberofauthors{4} %  
\author{
\alignauthor Ashish Ranjan Jha\\
       \affaddr{Master Student}\\
       \affaddr{Computer Science, EPFL}\\
       \email{ashish.jha@epfl.ch} \\
\alignauthor Kshitij Sharma \\
       \affaddr{PhD, CHILI Lab}\\
       \affaddr{EPFL}\\
       \email{kshitij.sharma@epfl.ch}
\and
\alignauthor S\'{e}verin Lemaignan
       \affaddr{PostDoc, CHILI Lab}\\
       \affaddr{EPFL}\\
       \email{severin.lemaignan@epfl.ch}
\alignauthor Pierre Dillenbourg
        \affaddr{Professor}\\
       \affaddr{EPFL}\\
       \email{pierre.dillenbourg@epfl.ch}
}

\maketitle
\begin{abstract}

We present a study that investigates the relation between anthropomorphism and
gaze patterns of the observers. Anthropomorphism usually refers to attributing
human-like characteristics by a human to a non-human agent/entity; in this
study, the non-human entity is a robot.

We hypothesize that while observing a human-robot interaction in a particular
setting, the observer develops an anthropomorphic behavior for the robot.
Moreover, the resulting anthropomorphism can be correlated with the gaze
patterns of the observer as well as with the recorded response of the
participants about their experience of the interaction (in the form of a
questionnaire), both before and after the experiment. We try to seek the answer
to the question whether anthropomorphism goes beyond the shape and body
features, and we indeed observe that just by the use of audio commands of
different cognitive levels, anthropomorphic attitude gets affected. We obtain
two other useful results. First, eye tracking serves to be an effective way for
measuring anthropomorphism. Second, in our study, the standard anthropomorphism
tests are also validated such as, a person who can anthropomorphize more, in
general, responds to a human scene and a robot scene in a similar manner.

We observe a significant increase in the gaze fixations over the actor's head
for a high cognitive scene compared to a low cognitive scene. We also achieve
the result that the high cognitive interaction scenarios are capable of inducing
anthropomorphic behavior more than the low cognitive scenarios.

\end{abstract}

\keywords{anthropomorphism, eye tracking, gaze patterns, robot}

\section{Introduction}

It is widely accepted that anthropomorphism describes a set of human-like
features of a robot (like shape, speech capabilities, facial expression).
Lemaignan et al. \cite{mc5}  refer to these characteristics as the
anthropomorphic design of the robot .  Anthropomorphism, as described by
Lemaignan et al., refers to the social phenomenon that emerges from the
interaction between a robot and an user. According to Epley et al. \cite{mc4},
this includes for instance emotional states, motivations, intentions ascribed by
the user to the robot.

Anthropomorphism is seen as a special kind of social (human-like) engagement
with robots. We made an attempt to analyze anthropomorphism in a
\textit{human-robot} interaction by utilizing the gaze patterns of the
participants (who watched this interaction). These gaze patterns were compared
to the gaze patterns for a similar \textit{human-human} interaction setting. The
``human'' part of the human-robot and human-human interactions mentioned above
is only in the form of an audio command and not physically present in the scene.
Hence, we represent the interactions with $\mathcal{R}$ and $\mathcal{H}$ in
this report for the human-robot and human-human settings respectively.\\ \\
There were four hypotheses made in this experiment. We hypothesized
(\textbf{H1}) that the gaze patterns can distinguish between $\mathcal{H}$ and
$\mathcal{R}$ interaction scenarios. Further, this gaze pattern difference can
be denoted as the distribution of gaze on areas of interest in the scene.
Secondly, we hypothesized (\textbf{H2}) that the difference in gaze patterns
between $\mathcal{H}$ and $\mathcal{R}$ conditions
($\delta_{\mathcal{H},\mathcal{R}}$) correlate with the participants'
\textit{initial capital of anthropomorphism} (ICA), where the ICA was measured
as the sum of the ratings (responses) given by the participants to the questions
of the pre-questionnaire. This means that for participants whose ICA is low, the
gaze patterns should be significantly different for the $\mathcal{R}$ as
compared to that for the $\mathcal{H}$ videos and vice-versa.

We also hypothesized (\textbf{H3}) that the gaze patterns can distinguish
between high-cognitive and low-cognitive tasks. Finally, we hypothesized
(\textbf{H4}) that the cognitive priming will have an effect on the difference
between ICA and \textit{adaptive anthropomorphic perception} (AAP) \textit{i.e.}
$\Delta_{ICA,AAP}$ (where AAP is measured for the post-questionnaire in a
similar way as the ICA). \\ \\ We used stationary eye tracking technique for
tracking the gaze patterns and ``Nao"\cite{mc3}, a robot manufactured by
Aldebaran Robotics was used in this experiment. We prepared the scripts for the
robot using Choreographe. The interactions were recorded as videos and were then
shown to the participants. The scenarios that were covered in the videos were
aimed at eliciting the human-like or high-cognitive (HC) feelings for the robot
in one setting and robot-like or low-cognitive (LC) feelings in the other
setting. For example, we had a scene, where the robot is asked by the human to
\textit{``pick up the brown toy"} and in another scene, with the same video, the
robot is asked to \textit{``pick up its favorite toy"}. We tried to keep our
distribution of participants uniform across all variations of the scenarios to
avoid any biases to our results. The change in the feelings of participants were
recorded in the form of response to two questionnaires before and after the
experiment. The difference in the response of the two questionnaires was used to
measure the impact the videos had on the participants. \\ \\ As mentioned
earlier, the human element in the $\mathcal{R}$ interaction was in the form of
only a human voice, basically a command given by the human to the robot. This
command (\textit{e.g} ``pick up the brown toy") was used to prime the context
thereby classifying the scenario as LC or HC. Initially we had three different
scenarios where the robot/human was asked:\\ \\ (i) \ \ to pick up a toy \\ (ii)
\ to point to a sound/noise \\ (iii) to show some movements (or dance) \\ \\
Differing from first two scenarios, the third scenario had only one object in
the video i.e. the actor (human or robot). In the first two scenarios, a
participant could make gaze transitions, say, between the robot and the toys for
the first scene. In contrast, in the third scene, a participant could only look
at the robot showing its movements. The third scene, hence, was more related to
observing the various body movements and was not helpful in identifying
differences in gaze patterns based on LC and HC scenarios and therefore, we did
not consider it for our study. First, a pilot experiment was conducted with a
small number of participants and then a full-fledged experiment was carried out.

\section{Related Work}

In a human-robot interaction, studying anthropomorphism would essentially mean
the assessment of human's tendency to engage in a human like way with robots
(that are not deliberately made to buttress such relationship). In broader
terms, anthropomorphism can be understood as the phenomenon between a human and
a non-human, where the human tends to attribute human characteristics to the
non-human in order to establish a meaningful contact\cite{c9}. But there have
been a plethora of definitions of anthropomorphism not only across but within
disciplines(Duffy, 2002)\cite{mc1}. Even within HRI (human robot interaction)
and robotics, there has not been a single unique definition of anthropomorphism,
but a variety of them. Bartneck et al. (2008, p. 74)\cite{mc2} refer to it as
\textit{``the attribution of a human form, human characteristics, or human
behavior to nonhuman things such as robots, computers, and animals."}
Contrarily, Waytz et al. (2010)\cite{c2} apply a more psychological-cognitive
view and define anthropomorphism as \textit{``a process of inductive inference
whereby people imbue the real or imagined behavior of other agents with human
like characteristics, motivations, intentions, or underlying mental states".} \\
\\ Etymologically, anthropomorphism is a term composed of two Greek words :
\textit{anthropos} for ``man" (or ``human") and \textit{morphe} for ``from /
structure" (or ``shape"). Although anthropomorphism" literally would mean
``human form", it should \textit{not} be used to refer to the \textit{form/
design} of a non-human agent. The term \textbf{anthropomorphic design} would
rather be a better choice to refer to imitating human-like form / design of a
robot. Bartneck and Forlizzi (2004b)\cite{c3} recommend that \textit{form}
refers not just to the physical shape of a robot but to all ascertainable parts
of it. Therefore, ``form" could be seen as the overall expression of the robot,
that includes its shape, materials, and behavioral characteristics.
Anthropomorphic form can be broadly classified, but there is no fine line
dividing these categories: anthropomorphic, caricatured, functional,
zoomorphic, (Fong et al., 2003a)\cite{c4}.

Another key aspect in the discussion of anthropomorphism is the change in
people's perception of robots over their time of interaction with robots. And as
the perception changes, the tendency to anthropomorphize the robot is likely to
change. Such a gap related to the perceived agency of the robot was discussed by
Takayama (2012)\cite{c6}. She noticed that among people who own a robot, while
some people perceive their robot as an agentic object, others feel  it as only a
plain machine. In order to distinguish between these two patterns and make sense
out of them in relation to people's perception of robots in general, Takayama
differentiated between what she calls an \textit{in-the-moment} and a
\textit{reflective} perspective on agency. Hence, an \textit{in-the-moment}
perspective would refer to one's most immediate response/sense in a given
situation. On the other hand, a \textit{reflective} perspective would indicate
one's reaction/sense of a situation based on a more in-depth  consideration and
contemplation (Takayama, 2012)\cite{c6}. \\ \\ Quite often, these two
distinctions are not considered differently, leading to errors and confusions.
In other words, in an initial phase of interaction with a non-human agent,
people might respond ``mindlessly" instead of responding consciously (Nass and
Moon, 2000)\cite{c7}. Only post a due amount of time of, what is generally
called as ``familiarization" with the robot, one might respond in a more
reflective manner instead of an in-the-moment reaction. This can be demonstrated
by the fact that when participants who had interacted with a technology, were
asked about whether the interaction with the technology was in a human-like way,
most of them denied this which shows the reflective perspective . However, the
same participants had actually reacted ( in the moment of the interaction) to
the system in many ways that were quite close to how they would react to people
(Reeves and Nass, 1996)\cite{c8}.

\section{Study}

We report on a study conducted to find the relation between anthropomorphism and
gaze patterns while observing a human robot interaction.

\subsection{Variables}

\subsubsection{Independent Variables}

As stated earlier, the videos were identical in all respects but the commands
used for priming in the LC and HC scenarios. So, we had the following
independent variables.

\paragraph{High-cognitive vs Low-cognitive}

This variable was kept between subject, i.e., a participant was either shown a
LC or a HC scenario, not both. So, out of the 40 participants, 22 watched the HC
tasks and 18 watched the LC tasks.

\paragraph{Human-Human vs Human-Robot Interaction}

This variable was kept within subject, \textit{i.e.} a participant watched both
human as well as robot videos for either LC or HC task. To avoid any order
effect among the human and robot videos for a participant, we had an equal
distribution among participants where 20 of them watched human videos before the
robot videos and the other 20 watched the videos in reverse order (robot videos
before human)

\subsubsection{Dependent Variables}

We have a dependent variable that is the difference between the ICA and AAP.
This represents how much a participant has been affected by watching the videos
because it reflects the difference in the response of a participant in the pre
and post questionnaires.

\subsubsection{Gaze variables}

\paragraph{Areas Of Interest(AOI)}

Among the two scenarios, the first was one was about the robot/human picking up
a toy and the second one about pointing to the noise. As seen in figure 1(b), in
the first scenario, we had 10 AOIs: 1 for the actor's (robot/human) head, 2 for
arms (left and right), 2 for hands, 2 for legs and 1 for torso, and also 2 for
the two toys (green and brown). Similarly, as shown in figure 1(c), we had 10
AOIs for the second scenario, where the 2 AOIs for toys were replaced by two
speakers that produced sound. We fetched the gaze patterns that fall into one of
these 10 AOIs and analyzed the gaze distribution among them.

\begin{figure}
    \subfigure[$\mathcal{R}$ : Toy Scene (without AOIs)]
    {\includegraphics[width=3.3in]{stimulus-toys}\label{Toy Scene (without AOIs)}}
    \subfigure[$\mathcal{R}$ : Toy Scene (with AOIs)]
    {\includegraphics[width=3.3in]{aoi-robot}\label{Toy Scene(with AOIs)}}
    \subfigure[$\mathcal{H}$ : Sound Scene (with AOIs)]
    {\includegraphics[width=3.3in]{aoi-human}\label{Sound Scene(with AOIs)}}
    \caption{Areas of interest (AOI)}
\end{figure}

\paragraph{Proportion of time on the AOIs}

We fetch only the gaze patterns that fall into one of these 10 AOIs and analyze
the gaze distribution among them based on the proportion of time spent in
viewing each of these AOIs. This helps in drawing comparisons between various
objects present in the scene.

\paragraph{Difference in gaze patterns}

An important data to be obtained here is $\delta_{H,R}$. This is calculated by
taking the difference between the ratio of net dwell time of an AOI and the AOI
fixation coverage summed over all the AOIs in the scene. Hence,
$\delta_{\mathcal{H},\mathcal{R}}$ is expressed as a ratio in the range of 0 to
1. Similarly, the differences between gaze patterns of two participants, where
one watches the LC task, given by $\delta_{low}^{\mathcal{H},\mathcal{R}}$ and
the other watches the HC task, given by
$\delta_{high}^{\mathcal{H},\mathcal{R}}$ are important gaze variables.

\subsection{Data Collection}

\subsubsection{Video Stimuli}

Participants were made to watch the $\mathcal{R}$ and $\mathcal{H}$ interaction
videos. There were two scenarios of interaction, each for $\mathcal{H}$ and
$\mathcal{R}$. Hence, there were a total of 4 videos to be watched by each
participant. These 4 videos were replicated in 2 sets : HC and LC tasks, out of
which only one was shown to a participant. The videos for a scenario were
identical in all regards except that the length of human videos was 57 seconds
whereas it was 110 seconds for the robot videos. This difference of duration was
because of the fact that the robot usually took longer time to perform an action
as compared to human. The difference in the HC and LC videos was only of the
initial audio command that was given to the robot or human. For example, in a LC
task, the command was \textit{``Pick up the brown toy"} whereas in HC, it was
\textit{``Pick up your favorite toy"}. Otherwise all the videos had the same
architecture starting with a human voice command followed by the response from
the robot/human.

\subsubsection{Questionnaires}

\paragraph{Pre-questionnaire}

The participants were asked to fill a questionnaire which had 49 questions. The
responses to the questions were scaled in the 5-point likert scale, numerically
ranging from -2 to 2. The questionnaire had ten questions from the 10 item
big-five personality questionnaire. And then there were questions taken from
godspeed questionnaire and other questionnaires. Please refer to the appendix
for a sample questionnaire used in this study. The ICA was calculated as the sum
of the ratings/points provided by the participants for questions 30 to 39 as
these were the questions most closely resembling anthropomorphism. In this
report, we refer to this questionnaire as the pre-questionnaire i.e. before the
experiment, and it typically took 5 minutes for participants to fill it.

\paragraph{Post-questionnaire}

There was another questionnaire form that was almost identical to the
pre-questionnaire that the participants had to fill after watching the videos.
This questionnaire typically took 3 to 4 minutes to fill and we refer to this as
the post-questionnaire. A sample is provided in the appendix of this report.
Based on the responses filled in this questionnaire, the AAP was calculated as
the sum of the ratings/points provided by the participants for questions 17 to
26 (similar to ICA).

\subsection{Course of the study}

We did a pilot test using 10 participants first, and then after some
modifications, we did the final experiment on 40 participants.

\subsubsection{Participants}

Participants on an average were around 21 years of age, with a standard
deviation of 4.5 . Among 40 participants, 21 were females and 19 were males.  We
tried and managed to avoid having participants from Computer Science or
Electronics background as they are generally perceived to have a lower
anthropomorphic attitude by default. As per our questionnaire responses, we
observed that the participants were not so familiar with robots and only a few
out of 40 had ever owned a robot.

It took approximately 15 minutes per participant for one experiment session.
Each participant was invited for only one session.

\subsubsection{Consent Form}

Before the experiment, participants were made to read, understand and sign a
standard consent form.

\subsubsection{Initial Interaction}

After the pre questionnaire, we kept a 2 to 3 minutes session for initial
interaction, where we let the participant spend some time with Nao\cite{mc3}.
The purpose of this interaction was to familiarize the participants with the
robot and mitigate the novelty effect, so that they do not get surprised seeing
a robot for the first time in the videos.

\subsubsection{Pre-questionnaire}

Participants were asked to fill the 49 questions questionnaire right after the
initial interaction.

\subsubsection{Videos}

After filling the pre-questionnaire, participants watched the $\mathcal{R}$ and
$\mathcal{H}$ interaction videos.

\subsubsection{Post-questionnaire}

After watching the videos, participants were asked to fill the post
questionnaire, which was the last step in the procedure of this study.

\subsubsection{Reward}

Each of the participants were given a reward equivalent to CHF 10.

\begin{figure}
    {\includegraphics[width=3.3in]{ManipulationCheck}}
    \caption{ManipulationCheck}
    \label{fig:ManipulationCheck}
\end{figure}

\section{Results}

Based on the experiments conducted on 40 participants in the $\mathcal{H}$ and
$\mathcal{R}$ interactions across LC and HC conditions, we have the following
results. (The detailed statistics and code used for obtaining the results are
available here : \\
\textit{https://github.com/chili-epfl/anthropomorphism-eyetracking})

\subsection{General Biases}

While testing for all the 4 hypotheses, we observed no significant bias with
respect to age, gender , EPFL status, familiarity with robot and robot ownership
of the participants, i.e., there was no correlation found between these factors
and the gaze patterns in the videos.

\subsection{Manipulation check}

In our post-questionnaire, we had a question asking the participants about
whether the video has a robot kind of task or a human kind of task on a scale of
-2 to 2 where -2 refers to robot kind of task. As can be seen in figure 2, we
got a significant correlation in this manipulation check (F[1,36] = 20.42, p <
.01) which means that the participants that were shown the LC videos identified
the task as the robot-like and participants watching HC videos perceived the
tasks as more human-like.

\subsection{H1: Gaze patterns for Human vs Robot}

Among the 10 AOIs, we grouped the AOIs corresponding to the actor into 4
categories : Head, Arm (containing both arms and hands), Torso, Leg(containing
both legs). And this is the result that we obtained from the ANOVA between gaze
patterns on the AOIs versus the $\mathcal{H}$ and $\mathcal{R}$ conditions :

\textit{\textbf{head}}: the fixations on the head for the $\mathcal{H}$ scene
were observed to more than that for the $\mathcal{R}$ scene (F[1,36] = \ 6.60, p
< .05)

\textit{\textbf{arm}}\ : the fixations on the arms for the $\mathcal{H}$ scene
were also greater than that for the $\mathcal{R}$ scene (F[1,36] = 18.65, p <
.01)

\textit{\textbf{leg}}\hspace{0.18cm} : the fixations on the legs were much lower
for the $\mathcal{H}$ scene as compared to the $\mathcal{R}$ scene (F[1,36] = \
2.89, p < .1)

\textit{\textbf{torso}} : the fixations on the torso was more for the
$\mathcal{H}$ scene than for the $\mathcal{R}$ scene (F[1,36] = \ 3.54, p < .1)

\subsection{H2: Difference in gaze patterns vs ICA}

We got a significant correlation between $\delta_{\mathcal{H},\mathcal{R}}$ and
the ICA. As can be seen in figure 3(a), there is a significant negative
correlation between the two quantities (Pearson Correlation Coefficient = -0.42,
p < .01).

\begin{figure}
    \subfigure[Difference in gaze patterns vs ICA]
    {\includegraphics[width=3.3in]{H2}\label{GazeDifference-vs-ICA}}
    \subfigure[Gaze patterns for high vs low condition]
    {\includegraphics[width=3.3in]{GazeHighLow}\label{GazeHighLow}}
    \subfigure[Difference between ICA and AAP versus High/Low]
    {\includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}}
    \caption{Hypotheses H2, H3, H4}
\end{figure}

\subsection{H3: Gaze patterns for high vs low cognitive condition}

This test was done only for $\mathcal{R}$ scenario as the $\mathcal{H}$ case is
by default a source of HC condition, hence, would not make a big impact in
changing the patterns across the LC and HC conditions. Based on ANOVA results,
taking just the 5 AOI groups (head, arms, hands, torso, legs) for the robot in
both LC and HC conditions, the fixations on the head in the HC condition was
found to be significantly higher than that in the LC condition (F[1,36] = 4.55,
p < .05). For all other AOI groups, the fixations across LC and HC were almost
the same. Figure 3(b) shows the distribution of proportion of time spent gazing
on the 5 AOIs for LC and HC conditions.

\subsection{H4: Difference between ICA and AAP versus High/Low}

ANOVA between $\Delta_{ICA,AAP}$ and the category of cognitive task
\textit{i.e.} HC or LC tells us that $\Delta_{ICA,AAP}$ is greater for HC tasks
than that for the LC tasks (F[1,36] = 6.54, p < .05). The results are shown in
figure 3(c).

\section{Discussion}

Based on the results that we obtained, we can now verify our four hypotheses.
For the first hypothesis where we state that the gaze patterns can distinguish
between $\mathcal{H}$ and $\mathcal{R}$ interaction scenarios, we get greater
amount of fixation on the head, arms and torso for the $\mathcal{H}$ scenario as
compared to the $\mathcal{R}$ scenario. This can be explained by the fact that
human is by default perceived as a high cognitive agent compared to a robot.
Hence, the proportion of time spent on looking at the head is more in case of
human videos as compared to robot videos. But the trend is opposite for legs.
This might be explained by the fact that the participants are fascinated by the
joints on the robot's legs \textit{i.e.} the novelty effect. Overall, this
result weakly validates our hypothesis.

In the second hypothesis, where we claim that $\delta_{\mathcal{H},\mathcal{R}}$
should correlate with the participants' ICA, we obtain in our results, a
significant negative correlation between the two quantities. From the negative
correlation, we can understand that if ICA is high, it means that the
\textit{human likeliness ascription} (HLA) is high (which means that there is a
greater tendency to anthropomorphize) which indicates that
$\delta_{\mathcal{H},\mathcal{R}}$ should be low. This supports our hypothesis
and can be explained by the fact that if HLA is high for a participant, then
even the $\mathcal{R}$ videos are quite human-like for such participant.

The third hypothesis where we state that the gaze patterns can distinguish
between HC and LC tasks, can also be supported by our results. As can be seen in
figure 3(b), the proportion of time spent by participants on looking at the head
is significantly higher in HC task as compared to LC task. When participants
ascribe more anthropomorphic features to robot, they look more at the head than
when they ascribe less anthropomorphic features.

Finally for the fourth hypothesis where we state that the cognitive priming will
have an effect on $\Delta_{ICA,AAP}$, as seen in the results, $\Delta_{ICA,AAP}$
for participants that watched the HC task is greater than that for the
participants who watched LC task. This proves the fact that HLA was induced by
the videos and in fact, the HC tasks impose a greater HLA on the minds of
participants than the LC tasks. This shows the typical priming effect of the
audio command given in the beginning of the video and highlights the variation
in HLA based on the interaction scenario (LC versus HC) thereby supporting our
hypothesis.

We analyze the gaze distribution in this study only based on the AOI net dwell
times . Apart from this, the gaze transition among AOIs can be another way of
fetching gaze patterns which is not used in this study.

\section{Conclusion}

In our experiment, we created two kinds of scenarios each for $\mathcal{H}$ and
$\mathcal{R}$ interaction and just by changing the audio commands (priming
effect), we replicated these videos to create a HC and a LC scene. We recorded
the gaze patterns of the 40 participants who were made to watch these videos and
also the participants were asked to fill two questionnaires before and after the
experiment. These data were analyzed and compared to our four hypotheses. We
hypothesized that one who anthropomorphizes more would have a similar reaction
to $\mathcal{H}$ and $\mathcal{R}$ conditions, and also that in the HC case, a
participant's fixations would be more on the head of the actor as compared to
that in the LC case. We also hypothesized that the HC scene would induce more
anthropomorphic attitude than the LC scene. We found that the results were
successful and supported our hypotheses. We also had another scenario where the
robot/human was asked to move/dance, but this scenario had only one object
(\textit{i.e.} the actor) showing movements, and hence participants would focus
more on seeing the movements leaving behind the cognition aspect, which made it
difficult to differentiate between the LC and HC cases and, therefore, we
discarded this scenario from our analysis.

\begin{thebibliography}{99}

\bibitem{mc5}S. Lemaignan, J. Fink, P. Dillenbourg, The Dynamics of Anthropomorphism in Robotics, 2014

\bibitem{mc4}N. Epley, A. Waytz, S. Akalis, and J. T. Cacioppo, ``When we need a human: Motivational determinants of anthropomorphism,'' Social Cognition,
vol. 26, no. 2, pp. 143-155, Apr. 2008.

\bibitem{mc3}NAO NEXT Gen H25 Datasheet. Aldebaran Robotics. 
December 2011.

\bibitem{c9}Fink, J., September 2014. Dynamics of Human-Robot 
Interaction in Domestic Environments (EPFL).

\bibitem{mc1}Duffy, B. R., 2002. Anthropomorphism and robotics. AISB'02: Social Intelligence and Interaction
in Animals, Robots and Agents. SSAISB, Imperial College, London, UK.
%URL http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.60.297

\bibitem{mc2}Bartneck, C., Kuli\'{c}, D., Croft, E., Zoghbi, S., Nov. 2008. Measurement instruments for the
anthropomorphism, animacy, likeability, perceived intelligence, and perceived safety of robots.
International Journal of Social Robotics 1 (1), 71-81.
%URL http://www.springerlink.com/content/d422u846113572qn/

\bibitem{c2}Waytz, A., Morewedge, C. K., Epley, N., Monteleone, G., Gao, J.-H., Cacioppo, J. T., Sep. 2010.
Making sense by making sentient: effectance motivation increases anthropomorphism. Journal
of personality and social psychology 99 (3), 410-435.

\bibitem{c3} Bartneck, C., Forlizzi, J., 2004b. Shaping human-robot interaction: understanding the social
aspects of intelligent robotic products. In: CHI '04 extended abstracts on Human factors in
computing systems. CHI EA '04. ACM, New York, NY, USA, p. 1731-1732.
%URL http://doi.acm.org/10.1145/985921.986205

\bibitem{c4}Fong, T., Nourbakhsh, I., Dautenhahn, K., Mar. 2003a. A survey of socially interactive robots.
Robotics and Autonomous Systems 42 (3-4), 143-166.
%URL http://www.sciencedirect.com/science/article/pii/S092188900200372X

%\bibitem{c5}Persson, P., Laaksolahti, J., L\"{o}nnqvist, P., 2000. Anthropomorphism: a multi-layered phenomenon.
%North Falmouth, Massachusetts, USA.
%URL http://soda.swedish-ict.se/3187/

\bibitem{c6}Takayama, L., Jan. 2012. Perspectives on agency interacting with and through personal robots. In:
Zacarias, M., Oliveira, J. V. d. (Eds.), Human-Computer Interaction: The Agency Perspective.
No. 396 in Studies in Computational Intelligence. Springer Berlin Heidelberg, pp. 195-214.
%URL http://link.springer.com/chapter/10.1007/978-3-642-25691-2_8

\bibitem{c7}Nass, C., Moon, Y., Jan. 2000. Machines and mindlessness: Social responses to computers.
Journal of Social Issues 56 (1), 81-103.
%URL http://onlinelibrary.wiley.com/doi/10.1111/0022-4537.00153/abstract

\bibitem{c8}Reeves, B., Nass, C., 1996. The Media Equation: How People Treat Computers, Television, and
New Media Like Real People and Places. Cambridge University Press.

%\bibitem{c10}NAO NEXT Gen H25 Datasheet. Aldebaran Robotics.

\end{thebibliography}

%\appendix
%\includepdf[pages={1,2}]{pre-questionnaire.pdf}
%\includepdf[pages={1,2}]{post-questionnaire.pdf}

\end{document}

### 2015-03-11 main.tex
More cleaning, including a separate bibliography

@@
 \documentclass{acm_proc_article-sp}
+
+\usepackage[utf8x]{inputenc}
 
@@
 \usepackage{url}
+\usepackage{xspace}
 
@@
 
-\begin{document}
+\newcommand{\eg}{{\textit{e.g.\xspace}}}
+\newcommand{\etal}{{\textit{et al.\xspace}}}
+\newcommand{\ie}{{\textit{i.e.\xspace}}}
 
@@
 
-\numberofauthors{4} %  
+\numberofauthors{1} %  
 \author{
-\alignauthor Ashish Ranjan Jha\\
-       \affaddr{Master Student}\\
-       \affaddr{Computer Science, EPFL}\\
-       \email{ashish.jha@epfl.ch} \\
-\alignauthor Kshitij Sharma \\
-       \affaddr{PhD, CHILI Lab}\\
-       \affaddr{EPFL}\\
-       \email{kshitij.sharma@epfl.ch}
-\and
-\alignauthor S\'{e}verin Lemaignan
-       \affaddr{PostDoc, CHILI Lab}\\
-       \affaddr{EPFL}\\
-       \email{severin.lemaignan@epfl.ch}
-\alignauthor Pierre Dillenbourg
-        \affaddr{Professor}\\
-       \affaddr{EPFL}\\
-       \email{pierre.dillenbourg@epfl.ch}
+\alignauthor Ashish Ranjan Jha, Kshitij Sharma, Séverin Lemaignan, Pierre Dillenbourg\\
+    \affaddr{CHILI Lab, École Polytechnique Fédérale de Lausanne}\\
+       \email{firstname.lastname@epfl.ch}
 }
 
+\begin{document}
 \maketitle
@@
 features of a robot (like shape, speech capabilities, facial expression).
-Lemaignan et al. \cite{mc5}  refer to these characteristics as the
+Lemaignan~\etal~\cite{lemaignan2014dynamics}  refer to these characteristics as the
 anthropomorphic design of the robot .  Anthropomorphism, as described by
-Lemaignan et al., refers to the social phenomenon that emerges from the
-interaction between a robot and an user. According to Epley et al. \cite{mc4},
+Lemaignan~\etal, refers to the social phenomenon that emerges from the
+interaction between a robot and an user. According to Epley~\etal
+\cite{epley_when_2008},
 this includes for instance emotional states, motivations, intentions ascribed by
@@
 Hence, we represent the interactions with $\mathcal{R}$ and $\mathcal{H}$ in
-this report for the human-robot and human-human settings respectively.\\ \\
+this report for the human-robot and human-human settings respectively.
+
 There were four hypotheses made in this experiment. We hypothesized
@@
 (\textbf{H4}) that the cognitive priming will have an effect on the difference
-between ICA and \textit{adaptive anthropomorphic perception} (AAP) \textit{i.e.}
+between ICA and \textit{adaptive anthropomorphic perception} (AAP) \ie
 $\Delta_{ICA,AAP}$ (where AAP is measured for the post-questionnaire in a
-similar way as the ICA). \\ \\ We used stationary eye tracking technique for
-tracking the gaze patterns and ``Nao"\cite{mc3}, a robot manufactured by
-Aldebaran Robotics was used in this experiment. We prepared the scripts for the
-robot using Choreographe. The interactions were recorded as videos and were then
-shown to the participants. The scenarios that were covered in the videos were
-aimed at eliciting the human-like or high-cognitive (HC) feelings for the robot
-in one setting and robot-like or low-cognitive (LC) feelings in the other
-setting. For example, we had a scene, where the robot is asked by the human to
-\textit{``pick up the brown toy"} and in another scene, with the same video, the
-robot is asked to \textit{``pick up its favorite toy"}. We tried to keep our
-distribution of participants uniform across all variations of the scenarios to
-avoid any biases to our results. The change in the feelings of participants were
-recorded in the form of response to two questionnaires before and after the
-experiment. The difference in the response of the two questionnaires was used to
-measure the impact the videos had on the participants. \\ \\ As mentioned
-earlier, the human element in the $\mathcal{R}$ interaction was in the form of
-only a human voice, basically a command given by the human to the robot. This
-command (\textit{e.g} ``pick up the brown toy") was used to prime the context
-thereby classifying the scenario as LC or HC. Initially we had three different
-scenarios where the robot/human was asked:\\ \\ (i) \ \ to pick up a toy \\ (ii)
-\ to point to a sound/noise \\ (iii) to show some movements (or dance) \\ \\
+similar way as the ICA).
+
+We used stationary eye tracking technique for tracking the gaze patterns and
+``Nao", a robot manufactured by Aldebaran Robotics was used in this
+experiment. We prepared the scripts for the robot using Choreographe. The
+interactions were recorded as videos and were then shown to the participants.
+The scenarios that were covered in the videos were aimed at eliciting the
+human-like or high-cognitive (HC) feelings for the robot in one setting and
+robot-like or low-cognitive (LC) feelings in the other setting. For example, we
+had a scene, where the robot is asked by the human to \textit{``pick up the
+brown toy"} and in another scene, with the same video, the robot is asked to
+\textit{``pick up its favorite toy"}. We tried to keep our distribution of
+participants uniform across all variations of the scenarios to avoid any biases
+to our results. The change in the feelings of participants were recorded in the
+form of response to two questionnaires before and after the experiment. The
+difference in the response of the two questionnaires was used to measure the
+impact the videos had on the participants.
+
+As mentioned earlier, the human element in the $\mathcal{R}$ interaction was in
+the form of only a human voice, basically a command given by the human to the
+robot. This command (\eg ``pick up the brown toy") was used to prime
+the context thereby classifying the scenario as LC or HC. Initially we had three
+different scenarios where the robot/human was asked:
+
+\begin{enumerate}
+    \item to pick up a toy
+    \item to point to a sound/noise
+    \item to show some movements (or dance)
+\end{enumerate}
+
 Differing from first two scenarios, the third scenario had only one object in
-the video i.e. the actor (human or robot). In the first two scenarios, a
+the video \ie~the actor (human or robot). In the first two scenarios, a
 participant could make gaze transitions, say, between the robot and the toys for
@@
 a non-human, where the human tends to attribute human characteristics to the
-non-human in order to establish a meaningful contact\cite{c9}. But there have
-been a plethora of definitions of anthropomorphism not only across but within
-disciplines(Duffy, 2002)\cite{mc1}. Even within HRI (human robot interaction)
-and robotics, there has not been a single unique definition of anthropomorphism,
-but a variety of them. Bartneck et al. (2008, p. 74)\cite{mc2} refer to it as
-\textit{``the attribution of a human form, human characteristics, or human
-behavior to nonhuman things such as robots, computers, and animals."}
-Contrarily, Waytz et al. (2010)\cite{c2} apply a more psychological-cognitive
-view and define anthropomorphism as \textit{``a process of inductive inference
-whereby people imbue the real or imagined behavior of other agents with human
-like characteristics, motivations, intentions, or underlying mental states".} \\
-\\ Etymologically, anthropomorphism is a term composed of two Greek words :
+non-human in order to establish a meaningful contact\cite{fink2014dynamics}. But
+there have been a plethora of definitions of anthropomorphism not only across
+but within disciplines\cite{duffy_anthropomorphism_2002}. Even
+within HRI (human robot interaction) and robotics, there has not been a single
+unique definition of anthropomorphism, but a variety of them.
+Bartneck~\etal\cite{bartneck_measurement_2008} refer to it as \emph{``the
+attribution of a human form, human characteristics, or human behavior to
+nonhuman things such as robots, computers, and animals."} Contrarily,
+Waytz~\etal\cite{Waytz2010} apply a more psychological-cognitive view and
+define anthropomorphism as \textit{``a process of inductive inference whereby
+    people imbue the real or imagined behavior of other agents with human like
+    characteristics, motivations, intentions, or underlying mental states".}
+
+Etymologically, anthropomorphism is a term composed of two Greek words :
 \textit{anthropos} for ``man" (or ``human") and \textit{morphe} for ``from /
@@
 rather be a better choice to refer to imitating human-like form / design of a
-robot. Bartneck and Forlizzi (2004b)\cite{c3} recommend that \textit{form}
+robot. Bartneck and Forlizzi\cite{bartneck_shaping_2004} recommend that \emph{form}
 refers not just to the physical shape of a robot but to all ascertainable parts
@@
 dividing these categories: anthropomorphic, caricatured, functional,
-zoomorphic, (Fong et al., 2003a)\cite{c4}.
+zoomorphic (Fong \etal \cite{fong_survey_2003}).
 
@@
 change. Such a gap related to the perceived agency of the robot was discussed by
-Takayama (2012)\cite{c6}. She noticed that among people who own a robot, while
-some people perceive their robot as an agentic object, others feel  it as only a
-plain machine. In order to distinguish between these two patterns and make sense
-out of them in relation to people's perception of robots in general, Takayama
-differentiated between what she calls an \textit{in-the-moment} and a
-\textit{reflective} perspective on agency. Hence, an \textit{in-the-moment}
-perspective would refer to one's most immediate response/sense in a given
-situation. On the other hand, a \textit{reflective} perspective would indicate
-one's reaction/sense of a situation based on a more in-depth  consideration and
-contemplation (Takayama, 2012)\cite{c6}. \\ \\ Quite often, these two
-distinctions are not considered differently, leading to errors and confusions.
-In other words, in an initial phase of interaction with a non-human agent,
-people might respond ``mindlessly" instead of responding consciously (Nass and
-Moon, 2000)\cite{c7}. Only post a due amount of time of, what is generally
-called as ``familiarization" with the robot, one might respond in a more
-reflective manner instead of an in-the-moment reaction. This can be demonstrated
-by the fact that when participants who had interacted with a technology, were
-asked about whether the interaction with the technology was in a human-like way,
-most of them denied this which shows the reflective perspective . However, the
-same participants had actually reacted ( in the moment of the interaction) to
-the system in many ways that were quite close to how they would react to people
-(Reeves and Nass, 1996)\cite{c8}.
+Takayama \cite{takayama_perspectives_2012}. She noticed that among people who
+own a robot, while some people perceive their robot as an agentic object, others
+feel  it as only a plain machine. In order to distinguish between these two
+patterns and make sense out of them in relation to people's perception of robots
+in general, Takayama differentiated between what she calls an
+\emph{in-the-moment} and a \emph{reflective} perspective on agency. Hence, an
+\emph{in-the-moment} perspective would refer to one's most immediate
+response/sense in a given situation. On the other hand, a \emph{reflective}
+perspective would indicate one's reaction/sense of a situation based on a more
+in-depth  consideration and contemplation \cite{takayama_perspectives_2012}.
+
+Quite often, these two distinctions are not considered differently, leading to
+errors and confusions.  In other words, in an initial phase of interaction with
+a non-human agent, people might respond ``mindlessly" instead of responding
+consciously\cite{nass_machines_2000}. Only post a due amount of
+time of, what is generally called as ``familiarization" with the robot, one
+might respond in a more reflective manner instead of an in-the-moment reaction.
+This can be demonstrated by the fact that when participants who had interacted
+with a technology, were asked about whether the interaction with the technology
+was in a human-like way, most of them denied this which shows the reflective
+perspective . However, the same participants had actually reacted ( in the
+moment of the interaction) to the system in many ways that were quite close to
+how they would react to people\cite{reeves_media_1996}.
 
@@
 
-This variable was kept between subject, i.e., a participant was either shown a
+This variable was kept between subject, \ie a participant was either shown a
 LC or a HC scenario, not both. So, out of the 40 participants, 22 watched the HC
@@
 
-This variable was kept within subject, \textit{i.e.} a participant watched both
+This variable was kept within subject, \ie a participant watched both
 human as well as robot videos for either LC or HC task. To avoid any order
@@
     {\includegraphics[width=3.3in]{stimulus-toys}\label{Toy Scene (without AOIs)}}
+
     \subfigure[$\mathcal{R}$ : Toy Scene (with AOIs)]
     {\includegraphics[width=3.3in]{aoi-robot}\label{Toy Scene(with AOIs)}}
+
     \subfigure[$\mathcal{H}$ : Sound Scene (with AOIs)]
     {\includegraphics[width=3.3in]{aoi-human}\label{Sound Scene(with AOIs)}}
+
     \caption{Areas of interest (AOI)}
@@
 these were the questions most closely resembling anthropomorphism. In this
-report, we refer to this questionnaire as the pre-questionnaire i.e. before the
+report, we refer to this questionnaire as the pre-questionnaire \ie before the
 experiment, and it typically took 5 minutes for participants to fill it.
@@
 Participants on an average were around 21 years of age, with a standard
-deviation of 4.5 . Among 40 participants, 21 were females and 19 were males.  We
+deviation of 4.5. Among 40 participants, 21 were females and 19 were males.  We
 tried and managed to avoid having participants from Computer Science or
@@
 observed that the participants were not so familiar with robots and only a few
-out of 40 had ever owned a robot.
-
-It took approximately 15 minutes per participant for one experiment session.
-Each participant was invited for only one session.
+out of 40 had ever owned a robot.  It took approximately 15 minutes per
+participant for one experiment session.  Each participant was invited for only
+one session.
 
@@
 After the pre questionnaire, we kept a 2 to 3 minutes session for initial
-interaction, where we let the participant spend some time with Nao\cite{mc3}.
+interaction, where we let the participant spend some time with Nao.
 The purpose of this interaction was to familiarize the participants with the
@@
 results. (The detailed statistics and code used for obtaining the results are
-available here : \\
-\textit{https://github.com/chili-epfl/anthropomorphism-eyetracking})
+available here : \url{https://github.com/chili-epfl/anthropomorphism-eyetracking})
 
@@
 While testing for all the 4 hypotheses, we observed no significant bias with
-respect to age, gender , EPFL status, familiarity with robot and robot ownership
-of the participants, i.e., there was no correlation found between these factors
+respect to age, gender, EPFL status, familiarity with robot and robot ownership
+of the participants, \ie there was no correlation found between these factors
 and the gaze patterns in the videos.
@@
 ANOVA between $\Delta_{ICA,AAP}$ and the category of cognitive task
-\textit{i.e.} HC or LC tells us that $\Delta_{ICA,AAP}$ is greater for HC tasks
+\ie HC or LC tells us that $\Delta_{ICA,AAP}$ is greater for HC tasks
 than that for the LC tasks (F[1,36] = 6.54, p < .05). The results are shown in
@@
 This might be explained by the fact that the participants are fascinated by the
-joints on the robot's legs \textit{i.e.} the novelty effect. Overall, this
+joints on the robot's legs \ie the novelty effect. Overall, this
 result weakly validates our hypothesis.
@@
 robot/human was asked to move/dance, but this scenario had only one object
-(\textit{i.e.} the actor) showing movements, and hence participants would focus
+(\ie the actor) showing movements, and hence participants would focus
 more on seeing the movements leaving behind the cognition aspect, which made it
@@
 
-\begin{thebibliography}{99}
-
-\bibitem{mc5}S. Lemaignan, J. Fink, P. Dillenbourg, The Dynamics of Anthropomorphism in Robotics, 2014
-
-\bibitem{mc4}N. Epley, A. Waytz, S. Akalis, and J. T. Cacioppo, ``When we need a human: Motivational determinants of anthropomorphism,'' Social Cognition,
-vol. 26, no. 2, pp. 143-155, Apr. 2008.
-
-\bibitem{mc3}NAO NEXT Gen H25 Datasheet. Aldebaran Robotics. 
-December 2011.
-
-\bibitem{c9}Fink, J., September 2014. Dynamics of Human-Robot 
-Interaction in Domestic Environments (EPFL).
-
-\bibitem{mc1}Duffy, B. R., 2002. Anthropomorphism and robotics. AISB'02: Social Intelligence and Interaction
-in Animals, Robots and Agents. SSAISB, Imperial College, London, UK.
-%URL http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.60.297
-
-\bibitem{mc2}Bartneck, C., Kuli\'{c}, D., Croft, E., Zoghbi, S., Nov. 2008. Measurement instruments for the
-anthropomorphism, animacy, likeability, perceived intelligence, and perceived safety of robots.
-International Journal of Social Robotics 1 (1), 71-81.
-%URL http://www.springerlink.com/content/d422u846113572qn/
-
-\bibitem{c2}Waytz, A., Morewedge, C. K., Epley, N., Monteleone, G., Gao, J.-H., Cacioppo, J. T., Sep. 2010.
-Making sense by making sentient: effectance motivation increases anthropomorphism. Journal
-of personality and social psychology 99 (3), 410-435.
-
-\bibitem{c3} Bartneck, C., Forlizzi, J., 2004b. Shaping human-robot interaction: understanding the social
-aspects of intelligent robotic products. In: CHI '04 extended abstracts on Human factors in
-computing systems. CHI EA '04. ACM, New York, NY, USA, p. 1731-1732.
-%URL http://doi.acm.org/10.1145/985921.986205
-
-\bibitem{c4}Fong, T., Nourbakhsh, I., Dautenhahn, K., Mar. 2003a. A survey of socially interactive robots.
-Robotics and Autonomous Systems 42 (3-4), 143-166.
-%URL http://www.sciencedirect.com/science/article/pii/S092188900200372X
-
-%\bibitem{c5}Persson, P., Laaksolahti, J., L\"{o}nnqvist, P., 2000. Anthropomorphism: a multi-layered phenomenon.
-%North Falmouth, Massachusetts, USA.
-%URL http://soda.swedish-ict.se/3187/
-
-\bibitem{c6}Takayama, L., Jan. 2012. Perspectives on agency interacting with and through personal robots. In:
-Zacarias, M., Oliveira, J. V. d. (Eds.), Human-Computer Interaction: The Agency Perspective.
-No. 396 in Studies in Computational Intelligence. Springer Berlin Heidelberg, pp. 195-214.
-%URL http://link.springer.com/chapter/10.1007/978-3-642-25691-2_8
-
-\bibitem{c7}Nass, C., Moon, Y., Jan. 2000. Machines and mindlessness: Social responses to computers.
-Journal of Social Issues 56 (1), 81-103.
-%URL http://onlinelibrary.wiley.com/doi/10.1111/0022-4537.00153/abstract
-
-\bibitem{c8}Reeves, B., Nass, C., 1996. The Media Equation: How People Treat Computers, Television, and
-New Media Like Real People and Places. Cambridge University Press.
-
-%\bibitem{c10}NAO NEXT Gen H25 Datasheet. Aldebaran Robotics.
-
-\end{thebibliography}
+\bibliographystyle{abbrv}
+\bibliography{biblio}
 

### 2015-03-12 main.tex
Use default 'article' class
Rewrite the abstract to highlight the impact of this research

@@
-\documentclass{acm_proc_article-sp}
+%\documentclass{acm_proc_article-sp}
+\documentclass[a4,twocolumn,10pt]{article}
 
@@
 \usepackage{subfigure}
+\usepackage{paralist}
 \usepackage{hyperref}
@@
 \usepackage{xspace}
+
+\usepackage[draft,nomargin,footnote]{fixme}
 
@@
 
-\title{Eye-tracking measures for Anthropomorphism in Human Robot Interaction}
+\title{New Insights on the Role of Context in the Perception of a Human-like Robot}
 
-\numberofauthors{1} %  
 \author{
-\alignauthor Ashish Ranjan Jha, Kshitij Sharma, Séverin Lemaignan, Pierre Dillenbourg\\
-    \affaddr{CHILI Lab, École Polytechnique Fédérale de Lausanne}\\
-       \email{firstname.lastname@epfl.ch}
+Ashish Ranjan Jha, Kshitij Sharma, Séverin Lemaignan, Pierre Dillenbourg\\
+CHILI Lab, École Polytechnique Fédérale de Lausanne\\
+\url{firstname.lastname@epfl.ch}
 }
@@
 
-We present a study that investigates the relation between anthropomorphism and
-gaze patterns of the observers. Anthropomorphism usually refers to attributing
-human-like characteristics by a human to a non-human agent/entity; in this
-study, the non-human entity is a robot.
+What leads us to attribute human-like characteristics to robots? The physical
+appearance of the robot, as well as the design of the behaviours, certainly play a key
+role. This paper however evidences another mechanism at play, more subtle and partially
+unconscious: the \emph{cognitive context}\fxwarning{cognitive context, really?}
+of the interaction.
 
-We hypothesize that while observing a human-robot interaction in a particular
-setting, the observer develops an anthropomorphic behavior for the robot.
-Moreover, the resulting anthropomorphism can be correlated with the gaze
-patterns of the observer as well as with the recorded response of the
-participants about their experience of the interaction (in the form of a
-questionnaire), both before and after the experiment. We try to seek the answer
-to the question whether anthropomorphism goes beyond the shape and body
-features, and we indeed observe that just by the use of audio commands of
-different cognitive levels, anthropomorphic attitude gets affected. We obtain
-two other useful results. First, eye tracking serves to be an effective way for
-measuring anthropomorphism. Second, in our study, the standard anthropomorphism
-tests are also validated such as, a person who can anthropomorphize more, in
-general, responds to a human scene and a robot scene in a similar manner.
+To study this effect, we propose an original methodology based on eye-tracking
+and a serie of stimuli that are visually identical and yet elicit different
+assumptions regarding the cognitive capabilities of the robot. We then correlate
+the gaze patterns with established questionnaires that assess anthropomorphic
+attributions.
 
-We observe a significant increase in the gaze fixations over the actor's head
-for a high cognitive scene compared to a low cognitive scene. We also achieve
-the result that the high cognitive interaction scenarios are capable of inducing
-anthropomorphic behavior more than the low cognitive scenarios.
+\begin{inparaenum}[\itshape a\upshape)]
+As a result, we show that \item gaze patterns correlate with post-hoc anthropomorphic
+attributions, and hence, eye-tracking can be used as a novel \emph{in-the-moment}
+metric of anthropomorphism, \item fixations on the robot's head are a good
+predictor of anthropomorphic attributions, \item simple context priming is sufficient
+to elicit significantly different anthropomorphic attributions.
+\end{inparaenum}
+
+This last item has noteworthy implications regarding the design of human-like human-robot
+interactions, and we propose to discuss them at the end of the article.
+
+%We present a study that investigates the relation between anthropomorphism and
+%gaze patterns of the observers. Anthropomorphism usually refers to attributing
+%human-like characteristics by a human to a non-human agent/entity; in this
+%study, the non-human entity is a robot. 
+%
+%We hypothesize that while observing a human-robot interaction in a particular
+%setting, the observer develops an anthropomorphic behavior for the robot.
+%Moreover, the resulting anthropomorphism can be correlated with the gaze
+%patterns of the observer as well as with the recorded response of the
+%participants about their experience of the interaction (in the form of a
+%questionnaire), both before and after the experiment. We try to seek the answer
+%to the question whether anthropomorphism goes beyond the shape and body
+%features, and we indeed observe that just by the use of audio commands of
+%different cognitive levels, anthropomorphic attitude gets affected. We obtain
+%two other useful results. First, eye tracking serves to be an effective way for
+%measuring anthropomorphism. Second, in our study, the standard anthropomorphism
+%tests are also validated such as, a person who can anthropomorphize more, in
+%general, responds to a human scene and a robot scene in a similar manner.
+%
+%We observe a significant increase in the gaze fixations over the actor's head
+%for a high cognitive scene compared to a low cognitive scene. We also achieve
+%the result that the high cognitive interaction scenarios are capable of inducing
+%anthropomorphic behavior more than the low cognitive scenarios.
 
@@
 
-\keywords{anthropomorphism, eye tracking, gaze patterns, robot}
+%\keywords{anthropomorphism, eye tracking, gaze patterns, robot}
 

### 2015-03-12 main.tex
Created a 'Contributions' section with the main points we want to discuss in the paper

@@
 how they would react to people\cite{reeves_media_1996}.
+
+\subsection{Novel Contributions}
+
+The study and results presented in this article lead to two main contributions:
+new insights on the impact of the cognitive context of the interaction on the
+perception of a robot by humans; a novel unbiased\fxwarning{correct?}
+methodology based on eye-tracking to measure anthropomorphic attributions during
+a running human-robot interaction.
+
+Our first contribution extends our understanding of the attribution of
+human-like characteristics to robot by exploring the role of the interaction
+context. As we will show in the article, it appears that \textbf{even relatively
+subtle context priming may lead to significantly different anthropomorphic
+perceptions of the exact same robot, performing the exact same task}, as
+confirmed both by distinct gaze patterns, and different reported perceptions in
+questionnaires. As far as we know, this effect had not been previously
+evidenced.
+
+This leads to a second-order effect that we also evidence here: depending on the
+cognitive context, the tendency to attribute human-like characteristics to robot
+\textbf{evolves} in significantly different ways: after observing a robot in a
+context that pre-suppose deeper cognitive capabilities, \textbf{people increase
+their general tendency to anthropomorphize robots} compared to a shallow
+cognitive context, even though the robot appearance and behaviour is the exact
+same.
+
+The second contribution is a methodological one: we present in this article
+\textbf{a novel technique to assess anthropomorphic projections that relies on a
+biometric measurement (eye-tracking) to compare gaze fixation durations on
+the face of the robot}. We cross-validate this new metric with existing,
+established, questionnaires. Compared to current techniques (post-hoc
+annotations of videos and questionnaires), this new approach is objective,
+is less impacted by experimental biases (like the \emph{observer effect},
+where the subject's behaviour is impacted by the fact he/she knows that
+he/she is observed) and take place during the interaction itself
+(\emph{in-the-moment} measurement).
+
+Besides, we also introduce a new kind of visual stimuli, specifically designed
+to study the impact of non-appearance, non-behavioural related effects on the
+human-like perception of robots. We make these video stimuli available to the
+community, and therefore invite our colleagues to reproduce our experimental
+results.
+
+As a whole, we believe that this article provide a solid contribution, both in
+terms of methodology and experimental evidence, to our understanding of one of
+the intricate psychological effects that come to play when humans and robots
+interact.
 

### 2015-03-12 main.tex
[wip] Improve the presentation of conditions and stimuli

@@
 \usepackage{xspace}
+\usepackage{booktabs}
+
+\usepackage{tikz}
+\usetikzlibrary{decorations.pathreplacing}
+\newcommand{\tikzmark}[1]{\tikz[overlay,remember picture] \node (#1) {};}
 
@@
 
+\section{Experimental Design}
+
+\subsection{Conditions}
+
+\begin{figure}
+    \centering
+    \small
+
+    \tikzmark{top}
+
+    \tikzmark{left}
+    \begin{tabular}{l|p{2.5cm}|p{2.5cm}}
+        & \tikzmark{top1} Shallow cognitive context & Deep cognitive \tikzmark{top2} context  \\
+        \hline
+        \tikzmark{left1} Robot & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favorite toy''} \\
+                               & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''} \\
+        \hline
+        \tikzmark{left2} Human & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favorite toy''} \\ 
+                               & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''}\tikzmark{bottom} \\
+        \end{tabular}
+
+    % draw the over- and side-braces
+    \begin{tikzpicture}[overlay, remember picture]
+
+        \draw [decoration={brace,amplitude=0.5em},decorate,thick]
+            (top -| top1.west) --  (top -| top2.east) node[midway, above=0.5em] {\scriptsize between subjects};
+
+        \draw [decoration={brace,amplitude=0.5em},decorate,thick]
+            (left |- bottom) --  (left |- left1.north) node[midway,above=3em,left=1em,rotate=90] {\scriptsize within subject};
+    \end{tikzpicture}
+    %%%
+
+    \caption{\small 2x2 design: the \emph{robot} vs \emph{human} condition is within
+        subject, while the \emph{shallow cognitive context} vs \emph{deep
+        cognitive context} is between subject. Two stimuli (\emph{``toys''}
+        scene, {\bf A}, and \emph{``noise''} scene, {\bf B})
+        were shown to the participants, introduced by brief verbal commands, reproduced
+        here. While visually identical (see screenshots on
+        figure~\ref{fig:stimuli}), the stimuli were introduced with different
+        commands in the two conditions \emph{shallow} and \emph{deep cognitive
+        context}.}
+
+    \label{}
+\end{figure}
+
+\subsection{Video Stimuli}
+
+Participants were made to watch the $\mathcal{R}$ and $\mathcal{H}$ interaction
+videos. There were two scenarios of interaction, each for $\mathcal{H}$ and
+$\mathcal{R}$. Hence, there were a total of 4 videos to be watched by each
+participant. These 4 videos were replicated in 2 sets : HC and LC tasks, out of
+which only one was shown to a participant. The videos for a scenario were
+identical in all regards except that the length of human videos was 57 seconds
+whereas it was 110 seconds for the robot videos. This difference of duration was
+because of the fact that the robot usually took longer time to perform an action
+as compared to human. The difference in the HC and LC videos was only of the
+initial audio command that was given to the robot or human. For example, in a LC
+task, the command was \textit{``Pick up the brown toy"} whereas in HC, it was
+\textit{``Pick up your favorite toy"}. Otherwise all the videos had the same
+architecture starting with a human voice command followed by the response from
+the robot/human.
+
+\begin{figure}
+    \centering
+    \subfigure[\emph{Toys} scene, robot condition]{
+        \includegraphics[height=3cm]{stimulus-robot-toys}
+    }
+    \subfigure[\emph{Toys} scene, human condition]{
+        \includegraphics[height=3cm]{stimulus-human-toys}
+    }
+
+    \subfigure[\emph{Noise} scene, robot condition]{
+        \includegraphics[height=3cm]{stimulus-robot-noise}
+    }
+    \subfigure[\emph{Noise} scene, human condition]{
+        \includegraphics[height=3cm]{stimulus-human-noise}
+    }
+
+    \caption{\small Screenshots of the 2x2 stimuli. Note that the images above have been
+    slightly cropped: the original video are framed so that the agent (robot or
+    human) always remains entirely visible.}
+    \label{fig:stimuli}
+\end{figure}
+
 \section{Study}
@@
 \subsection{Data Collection}
-
-\subsubsection{Video Stimuli}
-
-Participants were made to watch the $\mathcal{R}$ and $\mathcal{H}$ interaction
-videos. There were two scenarios of interaction, each for $\mathcal{H}$ and
-$\mathcal{R}$. Hence, there were a total of 4 videos to be watched by each
-participant. These 4 videos were replicated in 2 sets : HC and LC tasks, out of
-which only one was shown to a participant. The videos for a scenario were
-identical in all regards except that the length of human videos was 57 seconds
-whereas it was 110 seconds for the robot videos. This difference of duration was
-because of the fact that the robot usually took longer time to perform an action
-as compared to human. The difference in the HC and LC videos was only of the
-initial audio command that was given to the robot or human. For example, in a LC
-task, the command was \textit{``Pick up the brown toy"} whereas in HC, it was
-\textit{``Pick up your favorite toy"}. Otherwise all the videos had the same
-architecture starting with a human voice command followed by the response from
-the robot/human.
 

### 2015-03-17 main.tex
Reorganized the sections Design/Study/Course of the Study + rewritten several of the corresponding subsections

@@
 
+This study is build as an eye-tracking experiment (mainly measuring fixation times on
+various body parts) where participants watch short videos of an agent (either a
+robot or a human) performing a very simple task (like picking an object), in
+two different \emph{socio-cognitive contexts}. These contexts, created by priming
+and/or audio cues, are designed to elicit either a shallow cognitive context
+(that participant would refer as a \emph{machine-like} situation) or a deeper
+cognitive context (refered as a \emph{human-like} situation).
+
 \subsection{Conditions}
 
-\begin{figure}
+The study follows a 2x2 design, summarized in table~\ref{table:design}. Our two
+independent variables are the level of socio-cognitive context (\emph{shallow
+cognitive context} vs \emph{deep cognitive context}) and the nature of the
+agent appearing in the stimulus (a \emph{robot}, eliciting a \emph{human-robot} interaction
+situation, or a \emph{human}, eliciting a \emph{human-human} interaction
+situation).
+
+\begin{table}
     \centering
@@
 
-    \caption{\small 2x2 design: the \emph{robot} vs \emph{human} condition is within
-        subject, while the \emph{shallow cognitive context} vs \emph{deep
-        cognitive context} is between subject. Two stimuli (\emph{``toys''}
-        scene, {\bf A}, and \emph{``noise''} scene, {\bf B})
-        were shown to the participants, introduced by brief verbal commands, reproduced
-        here. While visually identical (see screenshots on
-        figure~\ref{fig:stimuli}), the stimuli were introduced with different
-        commands in the two conditions \emph{shallow} and \emph{deep cognitive
+    \caption{\small The study follows a 2x2 design: the \emph{robot} vs
+        \emph{human} condition is within subject, while the \emph{shallow
+        cognitive context} vs \emph{deep cognitive context} is between subject.
+        Two stimuli (\emph{``toys''} scene, {\bf A}, and \emph{``noise''} scene,
+        {\bf B}) were shown to the participants, introduced by brief verbal
+        commands, reproduced in the table. While visually identical (see
+        screenshots on figure~\ref{fig:stimuli}), the stimuli were introduced
+        with different commands in the two conditions \emph{shallow} and
+        \emph{deep cognitive
         context}.}
 
-    \label{}
-\end{figure}
+    \label{table:design}
+\end{table}
+
+\subsubsection{Dependent Variables}
+
+We have a dependent variable that is the difference between the ICA and AAP.
+This represents how much a participant has been affected by watching the videos
+because it reflects the difference in the response of a participant in the pre
+and post questionnaires.
 
@@
 
-Participants were made to watch the $\mathcal{R}$ and $\mathcal{H}$ interaction
-videos. There were two scenarios of interaction, each for $\mathcal{H}$ and
-$\mathcal{R}$. Hence, there were a total of 4 videos to be watched by each
-participant. These 4 videos were replicated in 2 sets : HC and LC tasks, out of
-which only one was shown to a participant. The videos for a scenario were
-identical in all regards except that the length of human videos was 57 seconds
-whereas it was 110 seconds for the robot videos. This difference of duration was
-because of the fact that the robot usually took longer time to perform an action
-as compared to human. The difference in the HC and LC videos was only of the
-initial audio command that was given to the robot or human. For example, in a LC
-task, the command was \textit{``Pick up the brown toy"} whereas in HC, it was
-\textit{``Pick up your favorite toy"}. Otherwise all the videos had the same
-architecture starting with a human voice command followed by the response from
-the robot/human.
+Four different video stimuli where filmed (figure~\ref{fig:stimuli}): two
+different tasks (picking a stuffed animal, refered hereafter as the
+\emph{Picking} task, and pointing towards a source of sound, refered as the
+\emph{Sound} task) acted either by a human or a robot. Video stimuli were
+realised in studio conditions. All videos followed the same simple structure: an
+initial audio command (spoken by an invisible person), followed by the task
+being executed.
+
+The human actor was instructed to follow as closely as possible the actions and
+attitudes of the robot (left/right glances, hesitations\ldots), while keeping a
+natural, \emph{human-like} general behaviour.  Hence, the length of human videos
+(57 seconds in total for the two tasks) was shorter than robot videos (110
+seconds) due to the robot being usually slower in performing actions (in
+particular walks) compared to human.
+
+The audio (and audio only) of these four videos was edited to create two sets of
+stimuli: one for the \emph{shallow cognitive context} condition, one for the
+\emph{deep cognitive context} condition. The audio editing consisted in
+inserting \emph{different commands} to initiate the tasks (reported in
+table~\ref{table:design}), and, in the \emph{Sound} task, to use as sound source
+either a repetitive bip (\emph{shallow cognitive context}) or the sound of a
+crying baby (\emph{deep cognitive context}).
 
@@
     \centering
-    \subfigure[\emph{Toys} scene, robot condition]{
+    \subfigure[\emph{Picking} task, robot condition]{
         \includegraphics[height=3cm]{stimulus-robot-toys}
     }
-    \subfigure[\emph{Toys} scene, human condition]{
+    \subfigure[\emph{Picking} task, human condition]{
         \includegraphics[height=3cm]{stimulus-human-toys}
@@
 
-    \subfigure[\emph{Noise} scene, robot condition]{
+    \subfigure[\emph{Sound} task, robot condition]{
         \includegraphics[height=3cm]{stimulus-robot-noise}
     }
-    \subfigure[\emph{Noise} scene, human condition]{
+    \subfigure[\emph{Sound} task, human condition]{
         \includegraphics[height=3cm]{stimulus-human-noise}
@@
 
-\section{Study}
-
-We report on a study conducted to find the relation between anthropomorphism and
-gaze patterns while observing a human robot interaction.
-
-\subsection{Variables}
-
-\subsubsection{Independent Variables}
-
-As stated earlier, the videos were identical in all respects but the commands
-used for priming in the LC and HC scenarios. So, we had the following
-independent variables.
-
-\paragraph{High-cognitive vs Low-cognitive}
-
-This variable was kept between subject, \ie a participant was either shown a
-LC or a HC scenario, not both. So, out of the 40 participants, 22 watched the HC
-tasks and 18 watched the LC tasks.
-
-\paragraph{Human-Human vs Human-Robot Interaction}
-
-This variable was kept within subject, \ie a participant watched both
-human as well as robot videos for either LC or HC task. To avoid any order
-effect among the human and robot videos for a participant, we had an equal
-distribution among participants where 20 of them watched human videos before the
-robot videos and the other 20 watched the videos in reverse order (robot videos
-before human)
-
-\subsubsection{Dependent Variables}
-
-We have a dependent variable that is the difference between the ICA and AAP.
-This represents how much a participant has been affected by watching the videos
-because it reflects the difference in the response of a participant in the pre
-and post questionnaires.
-
-\subsubsection{Gaze variables}
-
-\paragraph{Areas Of Interest(AOI)}
-
-Among the two scenarios, the first was one was about the robot/human picking up
-a toy and the second one about pointing to the noise. As seen in figure 1(b), in
-the first scenario, we had 10 AOIs: 1 for the actor's (robot/human) head, 2 for
-arms (left and right), 2 for hands, 2 for legs and 1 for torso, and also 2 for
-the two toys (green and brown). Similarly, as shown in figure 1(c), we had 10
-AOIs for the second scenario, where the 2 AOIs for toys were replaced by two
-speakers that produced sound. We fetched the gaze patterns that fall into one of
-these 10 AOIs and analyzed the gaze distribution among them.
-
-\begin{figure}
-    \subfigure[$\mathcal{R}$ : Toy Scene (without AOIs)]
-    {\includegraphics[width=3.3in]{stimulus-toys}\label{Toy Scene (without AOIs)}}
-
-    \subfigure[$\mathcal{R}$ : Toy Scene (with AOIs)]
-    {\includegraphics[width=3.3in]{aoi-robot}\label{Toy Scene(with AOIs)}}
-
-    \subfigure[$\mathcal{H}$ : Sound Scene (with AOIs)]
-    {\includegraphics[width=3.3in]{aoi-human}\label{Sound Scene(with AOIs)}}
-
-    \caption{Areas of interest (AOI)}
-\end{figure}
-
-\paragraph{Proportion of time on the AOIs}
-
-We fetch only the gaze patterns that fall into one of these 10 AOIs and analyze
-the gaze distribution among them based on the proportion of time spent in
-viewing each of these AOIs. This helps in drawing comparisons between various
-objects present in the scene.
-
-\paragraph{Difference in gaze patterns}
-
-An important data to be obtained here is $\delta_{H,R}$. This is calculated by
-taking the difference between the ratio of net dwell time of an AOI and the AOI
-fixation coverage summed over all the AOIs in the scene. Hence,
-$\delta_{\mathcal{H},\mathcal{R}}$ is expressed as a ratio in the range of 0 to
-1. Similarly, the differences between gaze patterns of two participants, where
-one watches the LC task, given by $\delta_{low}^{\mathcal{H},\mathcal{R}}$ and
-the other watches the HC task, given by
-$\delta_{high}^{\mathcal{H},\mathcal{R}}$ are important gaze variables.
-
-\subsection{Data Collection}
-
-\subsubsection{Questionnaires}
-
-\paragraph{Pre-questionnaire}
-
-The participants were asked to fill a questionnaire which had 49 questions. The
-responses to the questions were scaled in the 5-point likert scale, numerically
-ranging from -2 to 2. The questionnaire had ten questions from the 10 item
-big-five personality questionnaire. And then there were questions taken from
-godspeed questionnaire and other questionnaires. Please refer to the appendix
-for a sample questionnaire used in this study. The ICA was calculated as the sum
-of the ratings/points provided by the participants for questions 30 to 39 as
-these were the questions most closely resembling anthropomorphism. In this
-report, we refer to this questionnaire as the pre-questionnaire \ie before the
-experiment, and it typically took 5 minutes for participants to fill it.
-
-\paragraph{Post-questionnaire}
-
-There was another questionnaire form that was almost identical to the
-pre-questionnaire that the participants had to fill after watching the videos.
-This questionnaire typically took 3 to 4 minutes to fill and we refer to this as
-the post-questionnaire. A sample is provided in the appendix of this report.
-Based on the responses filled in this questionnaire, the AAP was calculated as
-the sum of the ratings/points provided by the participants for questions 17 to
-26 (similar to ICA).
-
-\subsection{Course of the study}
+\section{Course of the study}
 
@@
 
-Participants on an average were around 21 years of age, with a standard
-deviation of 4.5. Among 40 participants, 21 were females and 19 were males.  We
-tried and managed to avoid having participants from Computer Science or
-Electronics background as they are generally perceived to have a lower
-anthropomorphic attitude by default. As per our questionnaire responses, we
-observed that the participants were not so familiar with robots and only a few
-out of 40 had ever owned a robot.  It took approximately 15 minutes per
-participant for one experiment session.  Each participant was invited for only
-one session.
+Participants on an average were around 21 years of age (SD=4.5). Among 40
+participants, 21 were females and 19 were males.
+
+The participants were recruited amongst students of our university. To avoid students
+with a higher familiarity with robots and artificial intelligent systems,
+Computer Science and Electronics curriculum were excluded. This was \textit{a
+posteriori} comforted as per the questionnaire responses: no
+participants\fxwarning{to be checked}
+reported itself as being familiar with robots and only a few\fxwarning{how
+many?} out of 40 had ever owned a robot.
+
+It took
+approximately 15 minutes per participant for one experiment session.  Each
+participant was invited for only one session.
+
+The \emph{shallow} vs \emph{deep cognitive context} condition was between
+subject: Out of the 40 participants, 22 watched the \emph{deep cognitive}
+tasks and 18 watched the \emph{shallow cognitive} tasks.
+
+The \emph{robot} vs \emph{human} condition was within subject. The order of
+stimuli presentation was counter-balanced over the 40 participants.
 
@@
     {\includegraphics[width=3.3in]{ManipulationCheck}}
-    \caption{ManipulationCheck}
+    \caption{Manipulation check}
     \label{fig:ManipulationCheck}
 \end{figure}
+
+\subsection{Data Collection}
+
+\subsubsection{Gaze variables}
+
+\paragraph{Areas Of Interest(AOI)}
+
+Among the two scenarios, the first was one was about the robot/human picking up
+a toy and the second one about pointing to the noise. As seen in
+figure~\ref{fig:aoi-toys}, in
+the first scenario, we had 10 AOIs: 1 for the actor's (robot/human) head, 2 for
+arms (left and right), 2 for hands, 2 for legs and 1 for torso, and also 2 for
+the two toys (green and brown). Similarly, as shown in
+figure~\ref{fig:aoi-noise}, we had 10
+AOIs for the second scenario, where the 2 AOIs for toys were replaced by two
+speakers that produced sound. We fetched the gaze patterns that fall into one of
+these 10 AOIs and analyzed the gaze distribution among them.
+
+\begin{figure}
+    \centering
+    \subfigure[\emph{Picking} task, robot condition]
+    {\includegraphics[width=0.8\columnwidth]{aoi-robot}\label{fig:aoi-toys}}
+
+    \subfigure[\emph{Sound} task, human condition]
+    {\includegraphics[width=0.8\columnwidth]{aoi-human}\label{fig:aoi-noise}}
+
+    \caption{Areas of interest used for the gaze analysis}
+    \label{fig:aoi}
+\end{figure}
+
+\paragraph{Proportion of time on the AOIs}
+
+We fetch only the gaze patterns that fall into one of these 10 AOIs and analyze
+the gaze distribution among them based on the proportion of time spent in
+viewing each of these AOIs. This helps in drawing comparisons between various
+objects present in the scene.
+
+\paragraph{Difference in gaze patterns}
+
+An important data to be obtained here is $\delta_{H,R}$. This is calculated by
+taking the difference between the ratio of net dwell time of an AOI and the AOI
+fixation coverage summed over all the AOIs in the scene. Hence,
+$\delta_{\mathcal{H},\mathcal{R}}$ is expressed as a ratio in the range of 0 to
+1. Similarly, the differences between gaze patterns of two participants, where
+one watches the LC task, given by $\delta_{low}^{\mathcal{H},\mathcal{R}}$ and
+the other watches the HC task, given by
+$\delta_{high}^{\mathcal{H},\mathcal{R}}$ are important gaze variables.
+
+\subsubsection{Questionnaires}
+
+\paragraph{Pre-questionnaire}
+
+The participants were asked to fill a questionnaire which had 49 questions. The
+responses to the questions were scaled in the 5-point likert scale, numerically
+ranging from -2 to 2. The questionnaire had ten questions from the 10 item
+big-five personality questionnaire. And then there were questions taken from
+godspeed questionnaire and other questionnaires. Please refer to the appendix
+for a sample questionnaire used in this study. The ICA was calculated as the sum
+of the ratings/points provided by the participants for questions 30 to 39 as
+these were the questions most closely resembling anthropomorphism. In this
+report, we refer to this questionnaire as the pre-questionnaire \ie before the
+experiment, and it typically took 5 minutes for participants to fill it.
+
+\paragraph{Post-questionnaire}
+
+There was another questionnaire form that was almost identical to the
+pre-questionnaire that the participants had to fill after watching the videos.
+This questionnaire typically took 3 to 4 minutes to fill and we refer to this as
+the post-questionnaire. A sample is provided in the appendix of this report.
+Based on the responses filled in this questionnaire, the AAP was calculated as
+the sum of the ratings/points provided by the participants for questions 17 to
+26 (similar to ICA).
+
+\subsection{Course of the study}
 

### 2015-03-17 main.tex
{ICA->initial tendency to anthropomorphize} + rewrite description of questionaires

@@
 \newcommand{\ie}{{\textit{i.e.\xspace}}}
+
+\newcommand{\anti}{{$\mathcal{A}_0$ }}
+\newcommand{\antf}{{$\mathcal{A}_1$ }}
+\newcommand{\deltaant}{{ $\Delta_{\mathcal{A}_0,\mathcal{A}_1}$ }}
 
@@
 is only in the form of an audio command and not physically present in the scene.
-Hence, we represent the interactions with $\mathcal{R}$ and $\mathcal{H}$ in
+Hence, we represent the interactions with robot($\mathcal{R}$) and human($\mathcal{H}$) in
 this report for the human-robot and human-human settings respectively.
 
-There were four hypotheses made in this experiment. We hypothesized
-(\textbf{H1}) that the gaze patterns can distinguish between $\mathcal{H}$ and
-$\mathcal{R}$ interaction scenarios. Further, this gaze pattern difference can
+There were four hypotheses made in this experiment\fxwarning{need to change order of hypotheses(as Kshitij suggested) but the flow breaks by placing H4 first, H1 last}. We hypothesized
+(\textbf{H1}) that the gaze patterns can distinguish between human and
+robot interaction scenarios. Further, this gaze pattern difference can
 be denoted as the distribution of gaze on areas of interest in the scene.
 Secondly, we hypothesized (\textbf{H2}) that the difference in gaze patterns
-between $\mathcal{H}$ and $\mathcal{R}$ conditions
+between human and robot conditions
 ($\delta_{\mathcal{H},\mathcal{R}}$) correlate with the participants'
-\textit{initial capital of anthropomorphism} (ICA), where the ICA was measured
+\textit{initial tendency to anthropomorphize} (\anti), where \anti was measured
 as the sum of the ratings (responses) given by the participants to the questions
-of the pre-questionnaire. This means that for participants whose ICA is low, the
-gaze patterns should be significantly different for the $\mathcal{R}$ as
-compared to that for the $\mathcal{H}$ videos and vice-versa.
+of the pre-questionnaire. This means that for participants whose \anti is low, the
+gaze patterns should be significantly different for the robot videos
+compared to the human videos.
 
@@
 (\textbf{H4}) that the cognitive priming will have an effect on the difference
-between ICA and \textit{adaptive anthropomorphic perception} (AAP) \ie
-$\Delta_{ICA,AAP}$ (where AAP is measured for the post-questionnaire in a
-similar way as the ICA).
+between \anti and \textit{final tendency to anthropomorphize} (\antf) \ie
+\deltaant (where \antf is measured for the post-questionnaire in a
+similar way as the \anti).
 
-We used stationary eye tracking technique for tracking the gaze patterns and
+\fxwarning{This whole para already being discussed under Experimental Design. Can remove this para}We used stationary eye tracking technique for tracking the gaze patterns and
 ``Nao", a robot manufactured by Aldebaran Robotics was used in this
-experiment. We prepared the scripts for the robot using Choreographe. The
+experiment. The
 interactions were recorded as videos and were then shown to the participants.
@@
 human-like or high-cognitive (HC) feelings for the robot in one setting and
-robot-like or low-cognitive (LC) feelings in the other setting. For example, we
-had a scene, where the robot is asked by the human to \textit{``pick up the
-brown toy"} and in another scene, with the same video, the robot is asked to
-\textit{``pick up its favorite toy"}. We tried to keep our distribution of
+robot-like or low-cognitive (LC) feelings in the other setting. We tried to keep our distribution of
 participants uniform across all variations of the scenarios to avoid any biases
-to our results. The change in the feelings of participants were recorded in the
+to our results. The change in the feelings\fxwarning{can we have a more specific word than 'feeling'?} of participants were recorded in the
 form of response to two questionnaires before and after the experiment. The
@@
 
-As mentioned earlier, the human element in the $\mathcal{R}$ interaction was in
-the form of only a human voice, basically a command given by the human to the
+\fxwarning{This para is here just to justify why 3rd scenario isn't used.
+Else the contents already being discussed in sections 3.1, 3.2}As mentioned earlier, the human element in the robot interaction was in
+the form of a command given by the human to the
 robot. This command (\eg ``pick up the brown toy") was used to prime
@@
 
-Differing from first two scenarios, the third scenario had only one object in
+\fxwarning{Is Introduction the best place for justification for not using 3rd scenario?}Differing from first two scenarios, the third scenario had only one object in
 the video \ie~the actor (human or robot). In the first two scenarios, a
@@
 differences in gaze patterns based on LC and HC scenarios and therefore, we did
-not consider it for our study. First, a pilot experiment was conducted with a
-small number of participants and then a full-fledged experiment was carried out.
+not consider it for our study.
 
 \section{Related Work}
-
+\fxwarning{Need to modify (as S\'everin suggested) and curtail it}
 In a human-robot interaction, studying anthropomorphism would essentially mean
@@
 
-This study is build as an eye-tracking experiment (mainly measuring fixation times on
-various body parts) where participants watch short videos of an agent (either a
-robot or a human) performing a very simple task (like picking an object), in
-two different \emph{socio-cognitive contexts}. These contexts, created by priming
-and/or audio cues, are designed to elicit either a shallow cognitive context
-(that participant would refer as a \emph{machine-like} situation) or a deeper
-cognitive context (refered as a \emph{human-like} situation).
+This study is build as an eye-tracking experiment (mainly measuring fixation
+times on various body parts) where participants watch short videos of an agent
+(either a robot or a human) performing very simple task (picking an object or
+pointing toward a sound source), in two different socio-cognitive contexts.
+These contexts, created by priming and/or audio cues, are designed to elicit
+either a shallow cognitive context (that participant would refer as a
+\emph{machine-like} situation) or a deeper cognitive context (refered as a
+\emph{human-like} situation).
 
@@
         cognitive context} vs \emph{deep cognitive context} is between subject.
-        Two stimuli (\emph{``toys''} scene, {\bf A}, and \emph{``noise''} scene,
+        Two stimuli (\emph{Picking} task, {\bf A}, and \emph{Sound} task,
         {\bf B}) were shown to the participants, introduced by brief verbal
@@
 \end{table}
-
-\subsubsection{Dependent Variables}
-
-We have a dependent variable that is the difference between the ICA and AAP.
-This represents how much a participant has been affected by watching the videos
-because it reflects the difference in the response of a participant in the pre
-and post questionnaires.
 
@@
 
-\section{Course of the study}
+\subsection{Questionnaires}
+
+Before starting the experiment, the participants were asked to fill a
+questionnaire which had 49 questions. The responses to the questions were scaled
+in the 5-point Likert scale, numerically ranging from -2 to 2. The questionnaire
+had ten questions from the 10 item big-five personality questionnaire. And then
+there were questions taken from Godspeed questionnaire and other
+questionnaires. In this report, we refer to this questionnaire as the
+pre-questionnaire \ie before the experiment, and it typically took 5 minutes for
+participants to fill it.
+
+A second questionnaire was administered at the end of the experiment, that was
+almost identical to the pre-questionnaire.  This questionnaire typically took 3
+to 4 minutes to fill and we refer to this as the post-questionnaire.
+
+The difference (noted \deltaant, computation detailed below) observed for
+each participant between the pre- and post-questionnaires form the dependent
+variable of our experiment. It reflects the impact of the video stimuli on the
+anthropomorphic perception that they have of robots \emph{in general}: the
+Godspeed questions used in the questionnaires are not specific to the Nao robot,
+and assess in a broader way how humans perceive robots.
+
+\section{Experiment}
+
+\subsection{Course of the study}
+
+\subsubsection{Participants}
 
@@
 modifications, we did the final experiment on 40 participants.
-
-\subsubsection{Participants}
 
@@
 posteriori} comforted as per the questionnaire responses: no
-participants\fxwarning{to be checked}
+participants\fxwarning{to be checked : actually 5 out of 40 reported to be familiar(they marked +1 or +2 in questionnaire)}
 reported itself as being familiar with robots and only a few\fxwarning{how
-many?} out of 40 had ever owned a robot.
+many? ( = 8 out of 40 )} out of 40 had ever owned a robot.
 
@@
 
-\subsubsection{Consent Form}
+\subsubsection{Pre-questionnaire and familiarization}
 
+\fxwarning{Was it first the pre-questionnaire or the familiarization?}
 Before the experiment, participants were made to read, understand and sign a
-standard consent form.
+standard consent form. Participants were then asked to fill the 49 questions of
+the pre-questionnaire, without time constraint\fxwarning{right?}.
 
-\subsubsection{Initial Interaction}
+After the pre questionnaire, we invited the participants to an initial
+free interaction with a \textbf{powered-off} Nao robot (we did not constraint
+the time, and participants played between 2 and 3 minutes ith the robot).
 
-After the pre questionnaire, we kept a 2 to 3 minutes session for initial
-interaction, where we let the participant spend some time with Nao.
-The purpose of this interaction was to familiarize the participants with the
-robot and mitigate the novelty effect, so that they do not get surprised seeing
-a robot for the first time in the videos.
-
-\subsubsection{Pre-questionnaire}
-
-Participants were asked to fill the 49 questions questionnaire right after the
-initial interaction.
+The purpose of this pre-interaction was to get the participants acquainted with the
+robot shape and kind of motions it could possibly perform, and therefore
+mitigate the (visual) novelty effect (so that they do not get surprised seeing
+a robot for the first time in the videos).
 
@@
 
-After filling the pre-questionnaire, participants watched the $\mathcal{R}$ and
-$\mathcal{H}$ interaction videos.
+After filling the pre-questionnaire, we conducted a brief eye-tracker
+calibration procedure, and the participants' gaze was recorded while they
+watched the \emph{robot} and \emph{human} interaction videos.
 
@@
 
-After watching the videos, participants were asked to fill the post
-questionnaire, which was the last step in the procedure of this study.
+Finally, the participants were asked to fill the post-questionnaire.
 
-\subsubsection{Reward}
-
-Each of the participants were given a reward equivalent to CHF 10.
-
-\begin{figure}
-    {\includegraphics[width=3.3in]{ManipulationCheck}}
-    \caption{Manipulation check}
-    \label{fig:ManipulationCheck}
-\end{figure}
+Before leaving, each of the participants were given a reward equivalent to CHF
+10.
 
@@
 
-\subsubsection{Questionnaires}
+\subsubsection{Questionnaires processing}
 
-\paragraph{Pre-questionnaire}
+\fxnote{TDB}
 
-The participants were asked to fill a questionnaire which had 49 questions. The
-responses to the questions were scaled in the 5-point likert scale, numerically
-ranging from -2 to 2. The questionnaire had ten questions from the 10 item
-big-five personality questionnaire. And then there were questions taken from
-godspeed questionnaire and other questionnaires. Please refer to the appendix
-for a sample questionnaire used in this study. The ICA was calculated as the sum
-of the ratings/points provided by the participants for questions 30 to 39 as
-these were the questions most closely resembling anthropomorphism. In this
-report, we refer to this questionnaire as the pre-questionnaire \ie before the
-experiment, and it typically took 5 minutes for participants to fill it.
+Questionnaires were coded and two values, the \emph{initial tendency to
+anthropomorphize} \anti and the \emph{final tendency to anthropomorphize} \antf
+were computed, respectively from the pre- and post-questionnaires.
 
-\paragraph{Post-questionnaire}
+These values were computed by a direct sum of the rating provided by the
+participants for the Godspeed's questions in the category
+\emph{Anthropomorphism} and \emph{\fxwarning{?}...}. These ten questions were
+rated between -2 and 2, hence \anti and \antf vary between -20 and 20.
 
-There was another questionnaire form that was almost identical to the
-pre-questionnaire that the participants had to fill after watching the videos.
-This questionnaire typically took 3 to 4 minutes to fill and we refer to this as
-the post-questionnaire. A sample is provided in the appendix of this report.
-Based on the responses filled in this questionnaire, the AAP was calculated as
-the sum of the ratings/points provided by the participants for questions 17 to
-26 (similar to ICA).
-
-\subsection{Course of the study}
+The other questions (including the Big-Five personality test) were not used for
+this study.
 
@@
 Based on the experiments conducted on 40 participants in the $\mathcal{H}$ and
-$\mathcal{R}$ interactions across LC and HC conditions, we have the following
+robot interactions across LC and HC conditions, we have the following
 results. (The detailed statistics and code used for obtaining the results are
@@
 \subsection{Manipulation check}
+
+\begin{figure}
+    {\includegraphics[width=3.3in]{ManipulationCheck}}
+    \caption{Manipulation check}
+    \label{fig:ManipulationCheck}
+\end{figure}
 
@@
 both legs). And this is the result that we obtained from the ANOVA between gaze
-patterns on the AOIs versus the $\mathcal{H}$ and $\mathcal{R}$ conditions :
+patterns on the AOIs versus the human and robot videos :
 
-\textit{\textbf{head}}: the fixations on the head for the $\mathcal{H}$ scene
-were observed to more than that for the $\mathcal{R}$ scene (F[1,36] = \ 6.60, p
+\textit{\textbf{head}}: the fixations on the head for the human video
+were observed to more than that for the robot video (F[1,36] = \ 6.60, p
 < .05)
 
-\textit{\textbf{arm}}\ : the fixations on the arms for the $\mathcal{H}$ scene
-were also greater than that for the $\mathcal{R}$ scene (F[1,36] = 18.65, p <
+\textit{\textbf{arm}}\ : the fixations on the arms for the $\mathcal{H}$ video
+were also greater than that for the robot video (F[1,36] = 18.65, p <
 .01)
@@
 \textit{\textbf{leg}}\hspace{0.18cm} : the fixations on the legs were much lower
-for the $\mathcal{H}$ scene as compared to the $\mathcal{R}$ scene (F[1,36] = \
+for the human video as compared to the robot video (F[1,36] = \
 2.89, p < .1)
@@
 \textit{\textbf{torso}} : the fixations on the torso was more for the
-$\mathcal{H}$ scene than for the $\mathcal{R}$ scene (F[1,36] = \ 3.54, p < .1)
+human video than for the robot video (F[1,36] = \ 3.54, p < .1)
 
-\subsection{H2: Difference in gaze patterns vs ICA}
+\subsection{H2: Difference in gaze patterns vs \anti}
 
 We got a significant correlation between $\delta_{\mathcal{H},\mathcal{R}}$ and
-the ICA. As can be seen in figure 3(a), there is a significant negative
+the \anti. As can be seen in figure 3(a), there is a significant negative
 correlation between the two quantities (Pearson Correlation Coefficient = -0.42,
@@
 \begin{figure}
-    \subfigure[Difference in gaze patterns vs ICA]
+    \subfigure[Difference in gaze patterns vs \anti]
     {\includegraphics[width=3.3in]{H2}\label{GazeDifference-vs-ICA}}
@@
     {\includegraphics[width=3.3in]{GazeHighLow}\label{GazeHighLow}}
-    \subfigure[Difference between ICA and AAP versus High/Low]
+    \subfigure[Difference between \anti and \antf versus High/Low]
     {\includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}}
@@
 
-This test was done only for $\mathcal{R}$ scenario as the $\mathcal{H}$ case is
+This test was done only for robot scenario as the human case is
 by default a source of HC condition, hence, would not make a big impact in
@@
 
-\subsection{H4: Difference between ICA and AAP versus High/Low}
+\subsection{H4: Difference between \anti and \antf versus High/Low}
 
-ANOVA between $\Delta_{ICA,AAP}$ and the category of cognitive task
-\ie HC or LC tells us that $\Delta_{ICA,AAP}$ is greater for HC tasks
+ANOVA between \deltaant and the category of cognitive task
+\ie HC or LC tells us that \deltaant is greater for HC tasks
 than that for the LC tasks (F[1,36] = 6.54, p < .05). The results are shown in
@@
 For the first hypothesis where we state that the gaze patterns can distinguish
-between $\mathcal{H}$ and $\mathcal{R}$ interaction scenarios, we get greater
-amount of fixation on the head, arms and torso for the $\mathcal{H}$ scenario as
-compared to the $\mathcal{R}$ scenario. This can be explained by the fact that
+between human and robot interaction scenarios, we get greater
+amount of fixation on the head, arms and torso for the human scenario as
+compared to the robot scenario. This can be explained by the fact that
 human is by default perceived as a high cognitive agent compared to a robot.
@@
 In the second hypothesis, where we claim that $\delta_{\mathcal{H},\mathcal{R}}$
-should correlate with the participants' ICA, we obtain in our results, a
+should correlate with the participants' \anti, we obtain in our results, a
 significant negative correlation between the two quantities. From the negative
-correlation, we can understand that if ICA is high, it means that the
+correlation, we can understand that if \anti is high, it means that the
 \textit{human likeliness ascription} (HLA) is high (which means that there is a
@@
 and can be explained by the fact that if HLA is high for a participant, then
-even the $\mathcal{R}$ videos are quite human-like for such participant.
+even the robot videos are quite human-like for such participant.
 
@@
 Finally for the fourth hypothesis where we state that the cognitive priming will
-have an effect on $\Delta_{ICA,AAP}$, as seen in the results, $\Delta_{ICA,AAP}$
+have an effect on \deltaant, as seen in the results, \deltaant
 for participants that watched the HC task is greater than that for the
@@
 
-In our experiment, we created two kinds of scenarios each for $\mathcal{H}$ and
-$\mathcal{R}$ interaction and just by changing the audio commands (priming
+In our experiment, we created two kinds of scenarios each for human and
+robot interaction and just by changing the audio commands (priming
 effect), we replicated these videos to create a HC and a LC scene. We recorded
@@
 hypothesized that one who anthropomorphizes more would have a similar reaction
-to $\mathcal{H}$ and $\mathcal{R}$ conditions, and also that in the HC case, a
+to human and robot conditions, and also that in the HC case, a
 participant's fixations would be more on the head of the actor as compared to

### 2015-04-09 main.tex
Update on Overleaf.

--- 2015-03-17 main.tex
@@
 To study this effect, we propose an original methodology based on eye-tracking
-and a serie of stimuli that are visually identical and yet elicit different
+and a series of stimuli that are visually identical and yet elicit different
 assumptions regarding the cognitive capabilities of the robot. We then correlate
@@
 is only in the form of an audio command and not physically present in the scene.
-Hence, we represent the interactions with $\mathcal{R}$ and $\mathcal{H}$ in
+Hence, we represent the interactions with robot($\mathcal{R}$) and human($\mathcal{H}$) in
 this report for the human-robot and human-human settings respectively.
 
-There were four hypotheses made in this experiment. We hypothesized
-(\textbf{H1}) that the gaze patterns can distinguish between $\mathcal{H}$ and
-$\mathcal{R}$ interaction scenarios. Further, this gaze pattern difference can
+There were four hypotheses made in this experiment\fxwarning{need to change order of hypotheses(as Kshitij suggested) but the flow breaks by placing H4 first, H1 last}. We hypothesized
+(\textbf{H1}) that the gaze patterns can distinguish between human and
+robot interaction scenarios. Further, this gaze pattern difference can
 be denoted as the distribution of gaze on areas of interest in the scene.
 Secondly, we hypothesized (\textbf{H2}) that the difference in gaze patterns
-between $\mathcal{H}$ and $\mathcal{R}$ conditions
+between human and robot conditions
 ($\delta_{\mathcal{H},\mathcal{R}}$) correlate with the participants'
@@
 of the pre-questionnaire. This means that for participants whose ICA is low, the
-gaze patterns should be significantly different for the $\mathcal{R}$ as
-compared to that for the $\mathcal{H}$ videos and vice-versa.
+gaze patterns should be significantly different for the robot videos
+compared to the human videos.
 
@@
 
-We used stationary eye tracking technique for tracking the gaze patterns and
+\fxwarning{This whole para already being discussed under Experimental Design. Can remove this para}We used stationary eye tracking technique for tracking the gaze patterns and
 ``Nao", a robot manufactured by Aldebaran Robotics was used in this
-experiment. We prepared the scripts for the robot using Choreographe. The
+experiment. The
 interactions were recorded as videos and were then shown to the participants.
@@
 
-After filling the pre-questionnaire, participants watched the $\mathcal{R}$ and
-$\mathcal{H}$ interaction videos.
+After filling the pre-questionnaire, participants watched the robot and
+human interaction videos.
 
@@
 \textit{\textbf{torso}} : the fixations on the torso was more for the
-$\mathcal{H}$ scene than for the $\mathcal{R}$ scene (F[1,36] = \ 3.54, p < .1)
+human video than for the robot video (F[1,36] = \ 3.54, p < .1)
 

### 2015-04-20 main.tex
Improved abstract, added stub on 'Context and Interaction Design'

--- 2015-03-17 main.tex
@@
 \author{
-Ashish Ranjan Jha, Kshitij Sharma, Séverin Lemaignan, Pierre Dillenbourg\\
+Séverin Lemaignan, Ashish Ranjan Jha, Kshitij Sharma, Pierre Dillenbourg\\
 CHILI Lab, École Polytechnique Fédérale de Lausanne\\
@@
 What leads us to attribute human-like characteristics to robots? The physical
-appearance of the robot, as well as the design of the behaviours, certainly play a key
+appearance of the robot and the design of its behaviours do obviously play a key
 role. This paper however evidences another mechanism at play, more subtle and partially
-unconscious: the \emph{cognitive context}\fxwarning{cognitive context, really?}
-of the interaction.
+unconscious: the context of the interaction, and more precisely, the cognitive
+prerequisites that the interaction presupposes.
 
@@
 \begin{inparaenum}[\itshape a\upshape)]
-As a result, we show that \item gaze patterns correlate with post-hoc anthropomorphic
+As a result, we show that \item specific gaze patterns (fixations on the head of
+the robot) correlate with post-hoc anthropomorphic
 attributions, and hence, eye-tracking can be used as a novel \emph{in-the-moment}
-metric of anthropomorphism, \item fixations on the robot's head are a good
-predictor of anthropomorphic attributions, \item simple context priming is sufficient
+metric of anthropomorphism, and \item simple context priming is sufficient
 to elicit significantly different anthropomorphic attributions.
@@
 
-This last item has noteworthy implications regarding the design of human-like human-robot
+This second point has important implications regarding the design of human-like human-robot
 interactions, and we propose to discuss them at the end of the article.
@@
 
+\subsection{Context and Interaction Design}
+
+\fxwarning{discuss here how context can be used to shape the interaction}
+
 \bibliographystyle{abbrv}

### 2015-04-20 main.tex
[wip] Reworking introduction

@@
 
-\newcommand{\eg}{{\textit{e.g.\xspace}}}
-\newcommand{\etal}{{\textit{et al.\xspace}}}
-\newcommand{\ie}{{\textit{i.e.\xspace}}}
+\newcommand{\eg}{\textit{e.g.}\xspace}
+\newcommand{\etal}{\textit{et al.}\xspace}
+\newcommand{\ie}{\textit{i.e.}\xspace}
+\newcommand{\etc}{\textit{etc.}\xspace}
+\newcommand{\vs}{\textit{vs.}\xspace}
 
@@
 
-It is widely accepted that anthropomorphism describes a set of human-like
-features of a robot (like shape, speech capabilities, facial expression).
-Lemaignan~\etal~\cite{lemaignan2014dynamics}  refer to these characteristics as the
-anthropomorphic design of the robot .  Anthropomorphism, as described by
-Lemaignan~\etal, refers to the social phenomenon that emerges from the
-interaction between a robot and an user. According to Epley~\etal
-\cite{epley_when_2008},
-this includes for instance emotional states, motivations, intentions ascribed by
-the user to the robot.
+Robotics researchers often tend to consider that anthropomorphism only describes
+a static set of human-like features of a robot (like its shape, its speech
+capabilities, facial expressions, etc.). We refer to these characteristics as
+the \emph{anthropomorphic design} of the
+robot~\cite{fink_anthropomorphism_2012}, and propose that
+\emph{anthropomorphism} in general refers to a \emph{social phenomenon} that
+emerges from the (real or imagined) interaction between a non-human agent (a
+robot in our case) and a human~\cite{persson_anthropomorphism_2000}.  According
+to~\cite{epley_when_2008}, anthropomorphism includes the human perception of
+emotional states, motivations, intentions in the non-human agent, and tends to
+ascribe those qualities to it. As such, the \textbf{dynamic and socio-cognitive
+dimensions of anthropomorphism are essential to understand the complex bonds
+that human users build with artificial agents such as
+robots}~\cite{lemaignan2014dynamics}, and, even further, we postulate that
+anthropomorphism can therefore be considered as a useful \emph{proxy} to these
+intricate psychological bonds. This article aims at advancing our understanding
+of this phenomenon \textbf{by evidencing the impact of the cognitive
+presuppositions implied by the context of the interaction}.
 
-Anthropomorphism is seen as a special kind of social (human-like) engagement
-with robots. We made an attempt to analyze anthropomorphism in a
-\textit{human-robot} interaction by utilizing the gaze patterns of the
-participants (who watched this interaction). These gaze patterns were compared
-to the gaze patterns for a similar \textit{human-human} interaction setting. The
-``human'' part of the human-robot and human-human interactions mentioned above
-is only in the form of an audio command and not physically present in the scene.
-Hence, we represent the interactions with robot($\mathcal{R}$) and human($\mathcal{H}$) in
-this report for the human-robot and human-human settings respectively.
+The study of context in HRI is not new. \textit{Context of use} is defined by
+the ISO as \textit{``users, tasks, equipment (hardware, software and materials),
+and the physical and social environments in which a product is used''}, and
+accordingly, there are various aspects that can impact how a robot is
+experienced. The real or imagined \textit{purpose} of a robot, including the
+application context in which it is typically used (\eg office environment, home,
+rehabilitation center, public space, \etc) as well as the task context (\eg
+serious or playful task; composition of human-robot team; number of users) and
+the (social) role in which the robot is used / experienced are taken into
+account. Generally, when the context of use of a robot is social, entertaining
+or playful, it will enhance anthropomorphism, compared to when the context is a
+routine or focused serious task (security, rescue, \etc).
+\cite{joosse_what_2013} showed, for instance, that when the same robot ({\sc
+nao}) was used in a different task context (cleaning task \vs tour guide), users
+ascribed different personalities to the robot. \cite{goetz_cooperation_2002}
+revealed a link between a robot's context of use and people's perception of the
+robot: the authors found that people prefer a serious robot for serious tasks
+and a less serious robot for more playful tasks. \cite{kaplan_free_2000}
+discussed the role of uselessness in the design of robots. The author argues
+that artificial pets like AIBO have no real purpose, in a sense that they do not
+provide any kind of service or, in other words, \textit{``they are not doing
+what you tell them to do''} and \textit{``they might refuse the order of its
+owner''}. It may be this very aspect that increases people's tendency to
+anthropomorphize the robot. According to Kaplan, it is in our daily use language
+that we tend to attribute intentions to devices that are not doing their job
+well.
 
-There were four hypotheses made in this experiment\fxwarning{need to change order of hypotheses(as Kshitij suggested) but the flow breaks by placing H4 first, H1 last}. We hypothesized
-(\textbf{H1}) that the gaze patterns can distinguish between human and
-robot interaction scenarios. Further, this gaze pattern difference can
-be denoted as the distribution of gaze on areas of interest in the scene.
-Secondly, we hypothesized (\textbf{H2}) that the difference in gaze patterns
-between human and robot conditions
+These previous studies investigated users' perception of robots in
+different prototyped tasks (routine vs playful, typically boring vs typically
+intellectual) and their results nicely supported our general intuition.
+In this article, we show that much more subtle variations in the task context do
+lead to very noticeable effects as well.
+
+Measuring anthropomorphism raises interesting methodological challenges, if only
+tbecause people's perception of robots change over the duration of their
+interaction with the robots. Takayama discusses the effects of this
+change~\cite{takayama_perspectives_2012} and differentiates between what she calls an
+\emph{in-the-moment} and a \emph{reflective} perspective on agency: an
+\emph{in-the-moment} perspective would refer to one's most immediate
+response/sense in a given situation, while a \emph{reflective}
+perspective would indicate one's reaction/sense of a situation based on a more
+in-depth  consideration and contemplation.
+
+Quite often, these two distinctions are not considered differently, leading to
+errors and confusions.  In other words, in an initial phase of interaction with
+a non-human agent, people might respond ``mindlessly'' instead of responding
+consciously~\cite{nass_machines_2000}. Only post a due amount of
+time of, what is generally called as ``familiarization'' with the robot, one
+might respond in a more reflective manner instead of an in-the-moment reaction.
+This can be demonstrated by the fact that when participants who had interacted
+with a technology, were asked about whether the interaction with the technology
+was in a human-like way, most of them denied this which shows the reflective
+perspective . However, the same participants had actually reacted ( in the
+moment of the interaction) to the system in many ways that were quite close to
+how they would react to people~\cite{reeves_media_1996}.
+
+Most of the experiments that investigate anthropomorphism in HRI are conducted
+in controlled lab-settings during a short-term scenario. For instance, pictures
+or videos of different robots are shown to human subjects who subsequently fill
+in a questionnaire, to assess how far the different types of robots were
+perceived human-like. Such experimental settings have limitations for studying a
+social phenomenon like anthropomorphism, and one may wonder if anthropomorphism
+can really be measured in a post-interaction closed questionnaire or by rating
+scales. Findings might possibly lead to interpretations that would not be
+generalizable to natural settings or real interaction scenarios (which is always
+an issue in social science research).
+
+The Godspeed questionnaire~\citep{bartneck_measurement_2008}, and in particular,
+its subpart focused on anthropomorphism, is the main validated questionnaire to
+assess anthropomorphism. On 5 point semantic differential scales, people are
+asked to rate the following constructs: fake \vs natural, machinelike \vs
+humanlike, unconscious \vs conscious, artificial \vs lifelike, moving rigidly
+\vs moving elegantly. Because the concept of ``human-likeness'' itself is
+complex and abstract, \cite{kahn_jr._robotic_2006} suggest to ask for more
+concrete constructs that are typical or unique of the concept of
+``human-likeness'', and \cite{ruijten_introducing_2014} propose for instance a
+25-item questionnaire to measure various concrete aspects of human-likeness.
+
+\subsection{Hypotheses}
+
+There were four hypotheses made in this experiment\fxwarning{need to change
+order of hypotheses(as Kshitij suggested) but the flow breaks by placing H4
+first, H1 last}. We hypothesized (\textbf{H1}) that the gaze patterns can
+distinguish between human and robot interaction scenarios. Further, this gaze
+pattern difference can be denoted as the distribution of gaze on areas of
+interest in the scene.  Secondly, we hypothesized (\textbf{H2}) that the
+difference in gaze patterns between human and robot conditions
 ($\delta_{\mathcal{H},\mathcal{R}}$) correlate with the participants'
@@
 as the sum of the ratings (responses) given by the participants to the questions
-of the pre-questionnaire. This means that for participants whose \anti is low, the
-gaze patterns should be significantly different for the robot videos
+of the pre-questionnaire. This means that for participants whose \anti is low,
+the gaze patterns should be significantly different for the robot videos
 compared to the human videos.
@@
 between \anti and \textit{final tendency to anthropomorphize} (\antf) \ie
-\deltaant (where \antf is measured for the post-questionnaire in a
-similar way as the \anti).
+\deltaant (where \antf is measured for the post-questionnaire in a similar way
+as the \anti).
 
-\fxwarning{This whole para already being discussed under Experimental Design. Can remove this para}We used stationary eye tracking technique for tracking the gaze patterns and
-``Nao", a robot manufactured by Aldebaran Robotics was used in this
-experiment. The
-interactions were recorded as videos and were then shown to the participants.
-The scenarios that were covered in the videos were aimed at eliciting the
-human-like or high-cognitive (HC) feelings for the robot in one setting and
-robot-like or low-cognitive (LC) feelings in the other setting. We tried to keep our distribution of
-participants uniform across all variations of the scenarios to avoid any biases
-to our results. The change in the feelings\fxwarning{can we have a more specific word than 'feeling'?} of participants were recorded in the
-form of response to two questionnaires before and after the experiment. The
-difference in the response of the two questionnaires was used to measure the
-impact the videos had on the participants.
+\fxwarning{This whole para already being discussed under Experimental Design.
+Can remove this para}We used stationary eye tracking technique for tracking the
+gaze patterns and ``Nao", a robot manufactured by Aldebaran Robotics was used in
+this experiment. The interactions were recorded as videos and were then shown to
+the participants.  The scenarios that were covered in the videos were aimed at
+eliciting the human-like or high-cognitive (HC) feelings for the robot in one
+setting and robot-like or low-cognitive (LC) feelings in the other setting. We
+tried to keep our distribution of participants uniform across all variations of
+the scenarios to avoid any biases to our results. The change in the
+feelings\fxwarning{can we have a more specific word than 'feeling'?} of
+participants were recorded in the form of response to two questionnaires before
+and after the experiment. The difference in the response of the two
+questionnaires was used to measure the impact the videos had on the
+participants.
 
-\fxwarning{This para is here just to justify why 3rd scenario isn't used.
-Else the contents already being discussed in sections 3.1, 3.2}As mentioned earlier, the human element in the robot interaction was in
-the form of a command given by the human to the
-robot. This command (\eg ``pick up the brown toy") was used to prime
-the context thereby classifying the scenario as LC or HC. Initially we had three
-different scenarios where the robot/human was asked:
+\fxwarning{This para is here just to justify why 3rd scenario isn't used. Else
+the contents already being discussed in sections 3.1, 3.2}As mentioned earlier,
+the human element in the robot interaction was in the form of a command given by
+the human to the robot. This command (\eg ``pick up the brown toy") was used to
+prime the context thereby classifying the scenario as LC or HC. Initially we had
+three different scenarios where the robot/human was asked:
 
@@
 
-\fxwarning{Is Introduction the best place for justification for not using 3rd scenario?}Differing from first two scenarios, the third scenario had only one object in
-the video \ie~the actor (human or robot). In the first two scenarios, a
-participant could make gaze transitions, say, between the robot and the toys for
-the first scene. In contrast, in the third scene, a participant could only look
-at the robot showing its movements. The third scene, hence, was more related to
-observing the various body movements and was not helpful in identifying
-differences in gaze patterns based on LC and HC scenarios and therefore, we did
-not consider it for our study.
-
-\section{Related Work}
-\fxwarning{Need to modify (as S\'everin suggested) and curtail it}
-In a human-robot interaction, studying anthropomorphism would essentially mean
-the assessment of human's tendency to engage in a human like way with robots
-(that are not deliberately made to buttress such relationship). In broader
-terms, anthropomorphism can be understood as the phenomenon between a human and
-a non-human, where the human tends to attribute human characteristics to the
-non-human in order to establish a meaningful contact\cite{fink2014dynamics}. But
-there have been a plethora of definitions of anthropomorphism not only across
-but within disciplines\cite{duffy_anthropomorphism_2002}. Even
-within HRI (human robot interaction) and robotics, there has not been a single
-unique definition of anthropomorphism, but a variety of them.
-Bartneck~\etal\cite{bartneck_measurement_2008} refer to it as \emph{``the
-attribution of a human form, human characteristics, or human behavior to
-nonhuman things such as robots, computers, and animals."} Contrarily,
-Waytz~\etal\cite{Waytz2010} apply a more psychological-cognitive view and
-define anthropomorphism as \textit{``a process of inductive inference whereby
-    people imbue the real or imagined behavior of other agents with human like
-    characteristics, motivations, intentions, or underlying mental states".}
-
-Etymologically, anthropomorphism is a term composed of two Greek words :
-\textit{anthropos} for ``man" (or ``human") and \textit{morphe} for ``from /
-structure" (or ``shape"). Although anthropomorphism" literally would mean
-``human form", it should \textit{not} be used to refer to the \textit{form/
-design} of a non-human agent. The term \textbf{anthropomorphic design} would
-rather be a better choice to refer to imitating human-like form / design of a
-robot. Bartneck and Forlizzi\cite{bartneck_shaping_2004} recommend that \emph{form}
-refers not just to the physical shape of a robot but to all ascertainable parts
-of it. Therefore, ``form" could be seen as the overall expression of the robot,
-that includes its shape, materials, and behavioral characteristics.
-Anthropomorphic form can be broadly classified, but there is no fine line
-dividing these categories: anthropomorphic, caricatured, functional,
-zoomorphic (Fong \etal \cite{fong_survey_2003}).
-
-Another key aspect in the discussion of anthropomorphism is the change in
-people's perception of robots over their time of interaction with robots. And as
-the perception changes, the tendency to anthropomorphize the robot is likely to
-change. Such a gap related to the perceived agency of the robot was discussed by
-Takayama \cite{takayama_perspectives_2012}. She noticed that among people who
-own a robot, while some people perceive their robot as an agentic object, others
-feel  it as only a plain machine. In order to distinguish between these two
-patterns and make sense out of them in relation to people's perception of robots
-in general, Takayama differentiated between what she calls an
-\emph{in-the-moment} and a \emph{reflective} perspective on agency. Hence, an
-\emph{in-the-moment} perspective would refer to one's most immediate
-response/sense in a given situation. On the other hand, a \emph{reflective}
-perspective would indicate one's reaction/sense of a situation based on a more
-in-depth  consideration and contemplation \cite{takayama_perspectives_2012}.
-
-Quite often, these two distinctions are not considered differently, leading to
-errors and confusions.  In other words, in an initial phase of interaction with
-a non-human agent, people might respond ``mindlessly" instead of responding
-consciously\cite{nass_machines_2000}. Only post a due amount of
-time of, what is generally called as ``familiarization" with the robot, one
-might respond in a more reflective manner instead of an in-the-moment reaction.
-This can be demonstrated by the fact that when participants who had interacted
-with a technology, were asked about whether the interaction with the technology
-was in a human-like way, most of them denied this which shows the reflective
-perspective . However, the same participants had actually reacted ( in the
-moment of the interaction) to the system in many ways that were quite close to
-how they would react to people\cite{reeves_media_1996}.
+\fxwarning{Is Introduction the best place for justification for not using 3rd
+scenario?}Differing from first two scenarios, the third scenario had only one
+object in the video \ie~the actor (human or robot). In the first two scenarios,
+a participant could make gaze transitions, say, between the robot and the toys
+for the first scene. In contrast, in the third scene, a participant could only
+look at the robot showing its movements. The third scene, hence, was more
+related to observing the various body movements and was not helpful in
+identifying differences in gaze patterns based on LC and HC scenarios and
+therefore, we did not consider it for our study.
 

### 2015-04-21 main.tex
Reworked the related work

@@
 
+\newcommand{\h}[1]{\textbf{H#1}\xspace}
+
 \newcommand{\anti}{{$\mathcal{A}_0$ }}
@@
 To study this effect, we propose an original methodology based on eye-tracking
-and a serie of stimuli that are visually identical and yet elicit different
+and a set of stimuli that are visually identical and yet elicit different
 assumptions regarding the cognitive capabilities of the robot. We then correlate
@@
 
-Measuring anthropomorphism raises interesting methodological challenges, if only
-tbecause people's perception of robots change over the duration of their
-interaction with the robots. Takayama discusses the effects of this
-change~\cite{takayama_perspectives_2012} and differentiates between what she calls an
-\emph{in-the-moment} and a \emph{reflective} perspective on agency: an
+\paragraph{Measuring anthropomorphism} Measuring anthropomorphism raises
+interesting methodological challenges, if only because people's perception of
+robots change over the duration of their interaction with the
+robots~\cite{lemaignan2014dynamics}. Takayama discusses the effects of these
+changes~\cite{takayama_perspectives_2012} and differentiates between what she
+calls an \emph{in-the-moment} and a \emph{reflective} perspective on agency: an
 \emph{in-the-moment} perspective would refer to one's most immediate
-response/sense in a given situation, while a \emph{reflective}
-perspective would indicate one's reaction/sense of a situation based on a more
-in-depth  consideration and contemplation.
+response/sense in a given situation, while a \emph{reflective} perspective would
+indicate one's reaction/sense of a situation based on a more in-depth
+consideration and contemplation.  In the first phase of interaction with a
+non-human agent (a robot in our case), people might respond ``mindlessly''
+instead of responding consciously~\cite{nass_machines_2000}, and only after what
+is called the \emph{familiarization} period, one might respond in a more
+reflective manner instead of an in-the-moment reaction: Reeves
+\etal~\cite{reeves_media_1996} showed for instance that subjects interacting
+with technologies in ways close to how they would behave towards people, would
+deny any human-like interaction in a post-hoc questionnaire, illustrating this
+reflective perspective.
 
-Quite often, these two distinctions are not considered differently, leading to
-errors and confusions.  In other words, in an initial phase of interaction with
-a non-human agent, people might respond ``mindlessly'' instead of responding
-consciously~\cite{nass_machines_2000}. Only post a due amount of
-time of, what is generally called as ``familiarization'' with the robot, one
-might respond in a more reflective manner instead of an in-the-moment reaction.
-This can be demonstrated by the fact that when participants who had interacted
-with a technology, were asked about whether the interaction with the technology
-was in a human-like way, most of them denied this which shows the reflective
-perspective . However, the same participants had actually reacted ( in the
-moment of the interaction) to the system in many ways that were quite close to
-how they would react to people~\cite{reeves_media_1996}.
+Yet, most of the experiments that investigate anthropomorphism in HRI are based
+on post-interaction, closed questionnaires or rating scales.  The Godspeed
+questionnaire~\cite{bartneck_measurement_2008}, and in particular, its subpart
+focused on anthropomorphism, is the main validated questionnaire to assess
+anthropomorphism. On 5 point semantic differential scales, people are asked to
+rate the following constructs: fake \vs natural, machinelike \vs humanlike,
+unconscious \vs conscious, artificial \vs lifelike, moving rigidly \vs moving
+elegantly. Because the concept of ``human-likeness'' itself is complex and
+abstract, Kahn \etal~\cite{kahn_jr._robotic_2006} suggest to ask for more
+concrete constructs that are typical or unique of the concept of
+``human-likeness'', and Ruijten \etal~\cite{ruijten_introducing_2014} propose
+for instance a 25-item questionnaire to measure various concrete aspects of
+human-likeness. Other researchers~\cite{zlotowski2014dimensions,salem2015would}
+also applied a two-dimensional scale measuring \emph{Human Nature} and
+\emph{Uniquely Human} traits of robots, based on an original proposal by Haslam
+\etal~\cite{haslam2008attributing}.
 
-Most of the experiments that investigate anthropomorphism in HRI are conducted
-in controlled lab-settings during a short-term scenario. For instance, pictures
-or videos of different robots are shown to human subjects who subsequently fill
-in a questionnaire, to assess how far the different types of robots were
-perceived human-like. Such experimental settings have limitations for studying a
-social phenomenon like anthropomorphism, and one may wonder if anthropomorphism
-can really be measured in a post-interaction closed questionnaire or by rating
-scales. Findings might possibly lead to interpretations that would not be
-generalizable to natural settings or real interaction scenarios (which is always
-an issue in social science research).
-
-The Godspeed questionnaire~\citep{bartneck_measurement_2008}, and in particular,
-its subpart focused on anthropomorphism, is the main validated questionnaire to
-assess anthropomorphism. On 5 point semantic differential scales, people are
-asked to rate the following constructs: fake \vs natural, machinelike \vs
-humanlike, unconscious \vs conscious, artificial \vs lifelike, moving rigidly
-\vs moving elegantly. Because the concept of ``human-likeness'' itself is
-complex and abstract, \cite{kahn_jr._robotic_2006} suggest to ask for more
-concrete constructs that are typical or unique of the concept of
-``human-likeness'', and \cite{ruijten_introducing_2014} propose for instance a
-25-item questionnaire to measure various concrete aspects of human-likeness.
+We take here a different approach to measure anthropomorphism, based on
+eye-tracking.  By looking at the eyes fixation on the head of the robot, we have
+been able to evidence significantly different patterns in two experimental
+conditions subtly different in terms of human-likeness. This eye-tracking based
+metric is behavioural and hence does not suffer post-hoc reconstruction by the
+subjects, possibly providing a better, ``noise-less'', access to the human
+attitude towards the machine, and, as such, a better proxy to the cognitive and
+affective bonds that the human establishes with the robot.
 
 \subsection{Hypotheses}
+
+The study has been designed out of the following intuition: \emph{the more we
+ascribe cognitive capabilities to an agent, the more we focus on its head when
+interacting with it}.  Eye-tracking was a natural methodology to investigate
+this intuition, and we crafted audio-visual stimuli that would elicit different
+levels of cognitive ascription onto the robot while being identical in every
+other way.
+
+Several hypotheses ensued: \h{1}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%
+
+No correlation between delta opinion and gaze fixation on head: are we measuring
+two different things? or hidden variable?
+
+If different things, then, gaze is possibly a better metric: in-the-moment, does
+not suffer post-hoc reconstruction.
+
+%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusion}
@@
 
+Anthropomorphism as a proxy for cognitive/affective bonds that are esthablishing
+between humans and robots.
+
+\fxnote{discuss extensions towards mobile eyetrackers}
+
 \bibliographystyle{abbrv}

### 2015-06-15 main.tex
JHRI template + partial update with 57 subjects + formatting

@@
-%\documentclass{acm_proc_article-sp}
-\documentclass[a4,twocolumn,10pt]{article}
+\documentclass[lettersize, apacite, twoside, HRI]{apa_HRI}
 
 \usepackage[utf8x]{inputenc}
+
+\usepackage{times}
 
@@
 
-\title{New Insights on the Role of Context in the Perception of a Human-like Robot}
+\rightheader{Impact of Context in the Perception of  a Robot}   % This should be the title, or a shortened version of the title if your title is long.
+\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
+\title{Insights on the Impact of Context in the Perception of a Robot}
 
-\author{
-Séverin Lemaignan, Ashish Ranjan Jha, Kshitij Sharma, Pierre Dillenbourg\\
-CHILI Lab, École Polytechnique Fédérale de Lausanne\\
-\url{firstname.lastname@epfl.ch}
-}
+\author{Séverin Lemaignan, Ashish Ranjan Jha, Kshitij Sharma, Pierre
+Dillenbourg}
+\affiliation{CHILI Lab, École Polytechnique Fédérale de Lausanne}
 
-\begin{document}
-\maketitle
-\begin{abstract}
+\acknowledgements{\url{firstname.lastname@epfl.ch}}
 
+\abstract{
 What leads us to attribute human-like characteristics to robots? The physical
@@
 interactions, and we propose to discuss them at the end of the article.
+}
 
-%We present a study that investigates the relation between anthropomorphism and
-%gaze patterns of the observers. Anthropomorphism usually refers to attributing
-%human-like characteristics by a human to a non-human agent/entity; in this
-%study, the non-human entity is a robot. 
-%
-%We hypothesize that while observing a human-robot interaction in a particular
-%setting, the observer develops an anthropomorphic behavior for the robot.
-%Moreover, the resulting anthropomorphism can be correlated with the gaze
-%patterns of the observer as well as with the recorded response of the
-%participants about their experience of the interaction (in the form of a
-%questionnaire), both before and after the experiment. We try to seek the answer
-%to the question whether anthropomorphism goes beyond the shape and body
-%features, and we indeed observe that just by the use of audio commands of
-%different cognitive levels, anthropomorphic attitude gets affected. We obtain
-%two other useful results. First, eye tracking serves to be an effective way for
-%measuring anthropomorphism. Second, in our study, the standard anthropomorphism
-%tests are also validated such as, a person who can anthropomorphize more, in
-%general, responds to a human scene and a robot scene in a similar manner.
-%
-%We observe a significant increase in the gaze fixations over the actor's head
-%for a high cognitive scene compared to a low cognitive scene. We also achieve
-%the result that the high cognitive interaction scenarios are capable of inducing
-%anthropomorphic behavior more than the low cognitive scenarios.
+\keywords{human-robot interaction, anthropomorphism, cognitive context, eye tracking, gaze patterns}
 
-\end{abstract}
-
-%\keywords{anthropomorphism, eye tracking, gaze patterns, robot}
+\begin{document}
+\maketitle
 
@@
 
-    \caption{\small The study follows a 2x2 design: the \emph{robot} vs
+    \caption{\small The study follows a 2$\times$2 design: the \emph{robot} vs
         \emph{human} condition is within subject, while the \emph{shallow
@@
 
-We did a pilot test using 10 participants first, and then after some
-modifications, we did the final experiment on 40 participants.
+We ran first a pilot study with 10 participants, followed by an experiment with
+57 subjects (mean age: 20.9, $SD=3.9$, 32 females and 25 males).
 
-Participants on an average were around 21 years of age (SD=4.5). Among 40
-participants, 21 were females and 19 were males.
+The participants were recruited amongst students of our university. To avoid
+students with a high familiarity with robots and artificial intelligent systems,
+Computer Science and Electronics curriculum were excluded. This was \textit{a
+posteriori} comforted as per the questionnaire responses: no participants
+reported itself as being very familiar with robots, 8 reported some familiarity
+and 7 out of 57 own a domestic robot (vacuum cleaner).
 
-The participants were recruited amongst students of our university. To avoid students
-with a higher familiarity with robots and artificial intelligent systems,
-Computer Science and Electronics curriculum were excluded. This was \textit{a
-posteriori} comforted as per the questionnaire responses: no
-participants\fxwarning{to be checked : actually 5 out of 40 reported to be familiar(they marked +1 or +2 in questionnaire)}
-reported itself as being familiar with robots and only a few\fxwarning{how
-many? ( = 8 out of 40 )} out of 40 had ever owned a robot.
+The study lasted about 15 minutes per participant; each participant was invited
+for one session only. Before leaving, each participant was given a reward
+equivalent to EUR 10.
 
-It took
-approximately 15 minutes per participant for one experiment session.  Each
-participant was invited for only one session.
-
-The \emph{shallow} vs \emph{deep cognitive context} condition was between
-subject: Out of the 40 participants, 22 watched the \emph{deep cognitive}
-tasks and 18 watched the \emph{shallow cognitive} tasks.
-
-The \emph{robot} vs \emph{human} condition was within subject. The order of
-stimuli presentation was counter-balanced over the 40 participants.
+The study follows a 2$\times$2 design (table~\ref{table:design}): the
+\emph{deep} vs {shallow cognitive context} condition was between-subject ( 31
+subjects performed the \emph{deep cognitive} tasks while 26 were in the
+\emph{shallow cognitive} condition); the \emph{robot} vs \emph{human} condition
+was within-subject (the order of stimuli presentation was counter-balanced over
+the 57 participants).
 
@@
 
-Before leaving, each of the participants were given a reward equivalent to CHF
-10.
-
 \subsection{Data Collection}
@@
 
-\paragraph{Areas Of Interest(AOI)}
+\paragraph{Areas Of interest}
 
@@
 a toy and the second one about pointing to the noise. As seen in
-figure~\ref{fig:aoi-toys}, in
-the first scenario, we had 10 AOIs: 1 for the actor's (robot/human) head, 2 for
-arms (left and right), 2 for hands, 2 for legs and 1 for torso, and also 2 for
-the two toys (green and brown). Similarly, as shown in
-figure~\ref{fig:aoi-noise}, we had 10
-AOIs for the second scenario, where the 2 AOIs for toys were replaced by two
-speakers that produced sound. We fetched the gaze patterns that fall into one of
-these 10 AOIs and analyzed the gaze distribution among them.
+figure~\ref{fig:aoi}, we defined 10 areas of interest (AOIs): one on the head of
+the agent (robot or human), two on the arms (left and right), two on the hands,
+two on the legs and one on the torso. Besides, we defined one area of interest
+per toy or speaker (depending on the stimulus).
 
@@
 
-\paragraph{Proportion of time on the AOIs}
-
-We fetch only the gaze patterns that fall into one of these 10 AOIs and analyze
-the gaze distribution among them based on the proportion of time spent in
-viewing each of these AOIs. This helps in drawing comparisons between various
-objects present in the scene.
+We collected the gazes falling into one of these 10 zones and analyzed
+their distribution (producing what we call \emph{gaze patterns}).
 
@@
 
-An important data to be obtained here is $\delta_{H,R}$. This is calculated by
-taking the difference between the ratio of net dwell time of an AOI and the AOI
+An important data to be obtained here is $\delta_{\mathcal{H},\mathcal{R}}$. This is calculated by
+taking the difference between the ratio of net dwell time on an AOI and the AOI
 fixation coverage summed over all the AOIs in the scene. Hence,
@@
 1. Similarly, the differences between gaze patterns of two participants, where
-one watches the LC task, given by $\delta_{low}^{\mathcal{H},\mathcal{R}}$ and
+one watches the LC task, given by $\delta_{shallow}^{\mathcal{H},\mathcal{R}}$ and
 the other watches the HC task, given by
-$\delta_{high}^{\mathcal{H},\mathcal{R}}$ are important gaze variables.
+$\delta_{deep}^{\mathcal{H},\mathcal{R}}$ are important gaze variables.
 
@@
 
-Based on the experiments conducted on 40 participants in the $\mathcal{H}$ and
-robot interactions across LC and HC conditions, we have the following
-results. (The detailed statistics and code used for obtaining the results are
-available here : \url{https://github.com/chili-epfl/anthropomorphism-eyetracking})
+Based on the experiments conducted on 57 participants in the human
+($\mathcal{H}$) and robot ($\mathcal{R}$) interactions across \emph{shallow} and
+\emph{deep cognitive context} conditions, we have the following results. (the
+detailed statistics and code used for obtaining the results are available here :
+\url{https://github.com/chili-epfl/anthropomorphism-eyetracking})
 
@@
 -2 to 2 where -2 refers to robot kind of task. As can be seen in figure 2, we
-got a significant correlation in this manipulation check (F[1,36] = 20.42, p <
-.01) which means that the participants that were shown the LC videos identified
-the task as the robot-like and participants watching HC videos perceived the
-tasks as more human-like.
+got a significant correlation in this manipulation check ($F[1,36] = 20.42, p <
+.01$) which means that the participants that were shown the \emph{shallow
+cognitive context} videos identified the task as more robot-like and
+participants watching \emph{deep cognitive context} videos perceived the tasks
+as more human-like.
 
-\subsection{H1: Gaze patterns for Human vs Robot}
+\subsection{H1: Gaze differences between human and robot conditions}
 
-Among the 10 AOIs, we grouped the AOIs corresponding to the actor into 4
-categories : Head, Arm (containing both arms and hands), Torso, Leg(containing
-both legs). And this is the result that we obtained from the ANOVA between gaze
-patterns on the AOIs versus the human and robot videos :
+We grouped the 8 areas of interest located on the agent into 4 categories : {\sf
+head}, {\sf arm} (containing both arms and hands), {\sf torso}, {\sf leg}
+(including both legs). And this is the result that we obtained from the ANOVA
+between gaze patterns on the AOIs versus the human and robot videos :
 
-\textit{\textbf{head}}: the fixations on the head for the human video
-were observed to more than that for the robot video (F[1,36] = \ 6.60, p
-< .05)
+{\sf head}: the fixations on the head for the human video
+were observed to more than that for the robot video ($F[1,36] = 6.60, p < .05$)
 
-\textit{\textbf{arm}}\ : the fixations on the arms for the $\mathcal{H}$ video
-were also greater than that for the robot video (F[1,36] = 18.65, p <
-.01)
+{\sf arm}: the fixations on the arms for the $\mathcal{H}$ video
+were also greater than that for the robot video ($F[1,36] = 18.65, p < .01$)
 
-\textit{\textbf{leg}}\hspace{0.18cm} : the fixations on the legs were much lower
-for the human video as compared to the robot video (F[1,36] = \
-2.89, p < .1)
+{\sf leg}: the fixations on the legs were much lower
+for the human video as compared to the robot video ($F[1,36] = 2.89, p < .1$)
 
-\textit{\textbf{torso}} : the fixations on the torso was more for the
-human video than for the robot video (F[1,36] = \ 3.54, p < .1)
+{\sf torso}: the fixations on the torso was more for the
+human video than for the robot video ($F[1,36] = 3.54, p < .1$)
 
-\subsection{H2: Difference in gaze patterns vs \anti}
+\subsection{H2: Interaction between \anti and gaze patterns}
 
@@
 effect), we replicated these videos to create a HC and a LC scene. We recorded
-the gaze patterns of the 40 participants who were made to watch these videos and
+the gaze patterns of the 57 participants who were made to watch these videos and
 also the participants were asked to fill two questionnaires before and after the
@@
 
-\bibliographystyle{abbrv}
 \bibliography{biblio}

### 2015-06-15 main.tex
Fixed rendering of citations by switching to Lualatex

@@
-\documentclass[lettersize, apacite, twoside, HRI]{apa_HRI}
+\documentclass[lettersize, noapacite, twoside, HRI]{apa_HRI}
 
-\usepackage[utf8x]{inputenc}
-
+%\usepackage[utf8x]{inputenc}
 \usepackage{times}
@@
 \usepackage{paralist}
+
 \usepackage{hyperref}
+
 \usepackage{amsfonts}
@@
 \usepackage{booktabs}
+
+\usepackage[natbibapa]{apacite}
 
@@
 
-\author{Séverin Lemaignan, Ashish Ranjan Jha, Kshitij Sharma, Pierre
+\author{S\'everin Lemaignan, Ashish Ranjan Jha, Kshitij Sharma, Pierre
 Dillenbourg}
-\affiliation{CHILI Lab, École Polytechnique Fédérale de Lausanne}
+\affiliation{CHILI Lab, \'Ecole Polytechnique F\'ed\'erale de Lausanne}
 
@@
 
+\bibliographystyle{apacite}
 \bibliography{biblio}

### 2015-06-15 main.tex
Fixed citation style + resize figures for single column

@@
 \leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
-\title{Insights on the Impact of Context in the Perception of a Robot}
+\title{Impact of Context in the Perception of a Robot}
 
@@
 the \emph{anthropomorphic design} of the
-robot~\cite{fink_anthropomorphism_2012}, and propose that
+robot~\citep{fink_anthropomorphism_2012}, and propose that
 \emph{anthropomorphism} in general refers to a \emph{social phenomenon} that
 emerges from the (real or imagined) interaction between a non-human agent (a
-robot in our case) and a human~\cite{persson_anthropomorphism_2000}.  According
-to~\cite{epley_when_2008}, anthropomorphism includes the human perception of
+robot in our case) and a human~\citep{persson_anthropomorphism_2000}.  According
+to~\citet{epley_when_2008}, anthropomorphism includes the human perception of
 emotional states, motivations, intentions in the non-human agent, and tends to
@@
 that human users build with artificial agents such as
-robots}~\cite{lemaignan2014dynamics}, and, even further, we postulate that
+robots}~\citep{lemaignan2014dynamics}, and, even further, we postulate that
 anthropomorphism can therefore be considered as a useful \emph{proxy} to these
@@
 routine or focused serious task (security, rescue, \etc).
-\cite{joosse_what_2013} showed, for instance, that when the same robot ({\sc
+\citet{joosse_what_2013} showed, for instance, that when the same robot ({\sc
 nao}) was used in a different task context (cleaning task \vs tour guide), users
-ascribed different personalities to the robot. \cite{goetz_cooperation_2002}
+ascribed different personalities to the robot. \citet{goetz_cooperation_2002}
 revealed a link between a robot's context of use and people's perception of the
 robot: the authors found that people prefer a serious robot for serious tasks
-and a less serious robot for more playful tasks. \cite{kaplan_free_2000}
+and a less serious robot for more playful tasks. \citet{kaplan_free_2000}
 discussed the role of uselessness in the design of robots. The author argues
@@
 robots change over the duration of their interaction with the
-robots~\cite{lemaignan2014dynamics}. Takayama discusses the effects of these
-changes~\cite{takayama_perspectives_2012} and differentiates between what she
-calls an \emph{in-the-moment} and a \emph{reflective} perspective on agency: an
+robots~\citep{lemaignan2014dynamics}. \citet{takayama_perspectives_2012}
+discusses the effects of these changes and differentiates between what she calls
+an \emph{in-the-moment} and a \emph{reflective} perspective on agency: an
 \emph{in-the-moment} perspective would refer to one's most immediate
@@
 non-human agent (a robot in our case), people might respond ``mindlessly''
-instead of responding consciously~\cite{nass_machines_2000}, and only after what
-is called the \emph{familiarization} period, one might respond in a more
-reflective manner instead of an in-the-moment reaction: Reeves
-\etal~\cite{reeves_media_1996} showed for instance that subjects interacting
+instead of responding consciously~\citep{nass_machines_2000}, and only after
+what is called the \emph{familiarization} period, one might respond in a more
+reflective manner instead of an in-the-moment reaction: \citet{reeves_media_1996} showed for instance that subjects interacting
 with technologies in ways close to how they would behave towards people, would
@@
 on post-interaction, closed questionnaires or rating scales.  The Godspeed
-questionnaire~\cite{bartneck_measurement_2008}, and in particular, its subpart
+questionnaire~\citep{bartneck_measurement_2008}, and in particular, its subpart
 focused on anthropomorphism, is the main validated questionnaire to assess
@@
 elegantly. Because the concept of ``human-likeness'' itself is complex and
-abstract, Kahn \etal~\cite{kahn_jr._robotic_2006} suggest to ask for more
-concrete constructs that are typical or unique of the concept of
-``human-likeness'', and Ruijten \etal~\cite{ruijten_introducing_2014} propose
-for instance a 25-item questionnaire to measure various concrete aspects of
-human-likeness. Other researchers~\cite{zlotowski2014dimensions,salem2015would}
-also applied a two-dimensional scale measuring \emph{Human Nature} and
-\emph{Uniquely Human} traits of robots, based on an original proposal by Haslam
-\etal~\cite{haslam2008attributing}.
+abstract, \citet{kahn_jr._robotic_2006} suggest to ask for more concrete
+constructs that are typical or unique of the concept of ``human-likeness'', and
+\citet{ruijten_introducing_2014} propose for instance a 25-item questionnaire to
+measure various concrete aspects of human-likeness. Other
+researchers~\citep{zlotowski2014dimensions,salem2015would} also applied a
+two-dimensional scale measuring \emph{Human Nature} and \emph{Uniquely Human}
+traits of robots, based on an original proposal by \citet{haslam2008attributing}.
 
@@
     \subfigure[\emph{Picking} task, robot condition]{
-        \includegraphics[height=3cm]{stimulus-robot-toys}
+        \includegraphics[height=5cm]{stimulus-robot-toys}
     }
     \subfigure[\emph{Picking} task, human condition]{
-        \includegraphics[height=3cm]{stimulus-human-toys}
+        \includegraphics[height=5cm]{stimulus-human-toys}
     }
@@
     \subfigure[\emph{Sound} task, robot condition]{
-        \includegraphics[height=3cm]{stimulus-robot-noise}
+        \includegraphics[height=5cm]{stimulus-robot-noise}
     }
     \subfigure[\emph{Sound} task, human condition]{
-        \includegraphics[height=3cm]{stimulus-human-noise}
+        \includegraphics[height=5cm]{stimulus-human-noise}
     }
@@
     \subfigure[\emph{Picking} task, robot condition]
-    {\includegraphics[width=0.8\columnwidth]{aoi-robot}\label{fig:aoi-toys}}
-
+    {\includegraphics[height=5cm]{aoi-robot}\label{fig:aoi-toys}}
     \subfigure[\emph{Sound} task, human condition]
-    {\includegraphics[width=0.8\columnwidth]{aoi-human}\label{fig:aoi-noise}}
+    {\includegraphics[height=5cm]{aoi-human}\label{fig:aoi-noise}}
 

### 2015-06-19 main.tex
Large update to the whole article

@@
 
-\rightheader{Impact of Context in the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
+\rightheader{Impact of Cognitive Context in the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
 \leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
@@
 
-\author{S\'everin Lemaignan, Ashish Ranjan Jha, Kshitij Sharma, Pierre
+\author{S\'everin Lemaignan, Kshitij Sharma, Ashish Ranjan Jha, Pierre
 Dillenbourg}
@@
 
-This second point has important implications regarding the design of human-like human-robot
-interactions, and we propose to discuss them at the end of the article.
 }
 
-\keywords{human-robot interaction, anthropomorphism, cognitive context, eye tracking, gaze patterns}
+\keywords{human-robot interaction, anthropomorphism, cognitive context, eye-tracking, gaze patterns}
 
@@
 a static set of human-like features of a robot (like its shape, its speech
-capabilities, facial expressions, etc.). We refer to these characteristics as
-the \emph{anthropomorphic design} of the
-robot~\citep{fink_anthropomorphism_2012}, and propose that
-\emph{anthropomorphism} in general refers to a \emph{social phenomenon} that
-emerges from the (real or imagined) interaction between a non-human agent (a
-robot in our case) and a human~\citep{persson_anthropomorphism_2000}.  According
+capabilities, facial expressions, etc.).
+Following~\citet{fink_anthropomorphism_2012}, we refer to these characteristics
+as the \emph{anthropomorphic design} of the robot, and we call
+\emph{anthropomorphism} the general \emph{social phenomenon} that emerges from
+the (real or imagined) interaction between a non-human agent (a robot in our
+case) and a human~\citep{persson_anthropomorphism_2000}.  According
 to~\citet{epley_when_2008}, anthropomorphism includes the human perception of
 emotional states, motivations, intentions in the non-human agent, and tends to
-ascribe those qualities to it. As such, the \textbf{dynamic and socio-cognitive
+ascribe those qualities to it. As such, the dynamic and socio-cognitive
 dimensions of anthropomorphism are essential to understand the complex bonds
 that human users build with artificial agents such as
-robots}~\citep{lemaignan2014dynamics}, and, even further, we postulate that
-anthropomorphism can therefore be considered as a useful \emph{proxy} to these
-intricate psychological bonds. This article aims at advancing our understanding
-of this phenomenon \textbf{by evidencing the impact of the cognitive
-presuppositions implied by the context of the interaction}.
+robots~\citep{lemaignan2014dynamics}, and we propose therefore that
+anthropomorphism can be a useful \emph{proxy} to these intricate psychological
+bonds. This article aims at advancing our understanding of this phenomenon
+\textbf{by evidencing the impact of the cognitive presuppositions implied by the
+context of the interaction}.
 
@@
 These previous studies investigated users' perception of robots in
-different prototyped tasks (routine vs playful, typically boring vs typically
-intellectual) and their results nicely supported our general intuition.
+prototypical situations (routine \vs playful, typically boring \vs typically
+intellectual) and their results nicely supports our general intuition.
 In this article, we show that much more subtle variations in the task context do
@@
 
-\paragraph{Measuring anthropomorphism} Measuring anthropomorphism raises
+\subsection*{Measuring anthropomorphism}
+
+Measuring anthropomorphism raises
 interesting methodological challenges, if only because people's perception of
@@
 consideration and contemplation.  In the first phase of interaction with a
-non-human agent (a robot in our case), people might respond ``mindlessly''
-instead of responding consciously~\citep{nass_machines_2000}, and only after
-what is called the \emph{familiarization} period, one might respond in a more
-reflective manner instead of an in-the-moment reaction: \citet{reeves_media_1996} showed for instance that subjects interacting
-with technologies in ways close to how they would behave towards people, would
-deny any human-like interaction in a post-hoc questionnaire, illustrating this
-reflective perspective.
+robot, people might respond ``mindlessly'' instead of responding
+consciously~\citep{nass_machines_2000}, and only after what is called the
+\emph{familiarization} period, one might respond in a more reflective manner
+instead of an in-the-moment reaction: \citet{reeves_media_1996} showed for
+instance that subjects interacting with technologies in ways close to how they
+would behave towards people, would deny any human-like interaction in a post-hoc
+questionnaire, illustrating this reflective perspective.
 
@@
 focused on anthropomorphism, is the main validated questionnaire to assess
-anthropomorphism. On 5 point semantic differential scales, people are asked to
+anthropomorphism. On 5-points semantic differential scales, people are asked to
 rate the following constructs: fake \vs natural, machinelike \vs humanlike,
@@
 
-\subsection{Hypotheses}
+\subsection*{Hypotheses}
 
@@
 
-Several hypotheses ensued: \h{1}
+Several hypotheses ensued, our baseline hypothesis \h{0} being that \emph{shallow
+cognitive contexts} and \emph{deep cognitive contexts} are recognized
+(manipulation check) and interpreted by the participants as being respectively
+\emph{machine-like} (low level of anthropomorphic attributions) or
+\emph{human-like} (higher level of anthropomorphic attributions).
 
-There were four hypotheses made in this experiment\fxwarning{need to change
-order of hypotheses(as Kshitij suggested) but the flow breaks by placing H4
-first, H1 last}. We hypothesized (\textbf{H1}) that the gaze patterns can
-distinguish between human and robot interaction scenarios. Further, this gaze
-pattern difference can be denoted as the distribution of gaze on areas of
-interest in the scene.  Secondly, we hypothesized (\textbf{H2}) that the
-difference in gaze patterns between human and robot conditions
-($\delta_{\mathcal{H},\mathcal{R}}$) correlate with the participants'
-\textit{initial tendency to anthropomorphize} (\anti), where \anti was measured
-as the sum of the ratings (responses) given by the participants to the questions
-of the pre-questionnaire. This means that for participants whose \anti is low,
-the gaze patterns should be significantly different for the robot videos
-compared to the human videos.
+Our first hypothesis \h{1} is then that gaze behaviour only is sufficient to
+know if a subject is looking at a robot or at a human.  More precisely, we
+hypothesize that the distribution of gaze fixations on the different body parts
+is significantly different when watching a robot or a human performing the same
+task.
 
-We also hypothesized (\textbf{H3}) that the gaze patterns can distinguish
-between high-cognitive and low-cognitive tasks. Finally, we hypothesized
-(\textbf{H4}) that the cognitive priming will have an effect on the difference
-between \anti and \textit{final tendency to anthropomorphize} (\antf) \ie
-\deltaant (where \antf is measured for the post-questionnaire in a similar way
-as the \anti).
+Secondly, we hypothesize (\h{2}) that the \emph{difference} of gaze
+behaviours between the human and robot conditions correlates with the
+participants' initial tendency to anthropomorphize, measured from a standard
+pre-questionnaire: we expect that people with high tendency to anthropomorphize
+will tend to have similar gaze behaviours while watching either a robot or a
+human performing the same task.
 
-\fxwarning{This whole para already being discussed under Experimental Design.
-Can remove this para}We used stationary eye tracking technique for tracking the
-gaze patterns and ``Nao", a robot manufactured by Aldebaran Robotics was used in
-this experiment. The interactions were recorded as videos and were then shown to
-the participants.  The scenarios that were covered in the videos were aimed at
-eliciting the human-like or high-cognitive (HC) feelings for the robot in one
-setting and robot-like or low-cognitive (LC) feelings in the other setting. We
-tried to keep our distribution of participants uniform across all variations of
-the scenarios to avoid any biases to our results. The change in the
-feelings\fxwarning{can we have a more specific word than 'feeling'?} of
-participants were recorded in the form of response to two questionnaires before
-and after the experiment. The difference in the response of the two
-questionnaires was used to measure the impact the videos had on the
-participants.
+Then, we hypothesize (\h{3}) that the gaze fixations on the head are significantly
+different depending on the cognitive context, and that a deeper cognitive
+context corresponds to longer gaze fixations on the head. This would in turn
+interpreted at \emph{gaze fixations on the head is a proxy for an higher
+level of human-likeness attribution}, the core hypothesis of this article.
 
-\fxwarning{This para is here just to justify why 3rd scenario isn't used. Else
-the contents already being discussed in sections 3.1, 3.2}As mentioned earlier,
-the human element in the robot interaction was in the form of a command given by
-the human to the robot. This command (\eg ``pick up the brown toy") was used to
-prime the context thereby classifying the scenario as LC or HC. Initially we had
-three different scenarios where the robot/human was asked:
-
-\begin{enumerate}
-    \item to pick up a toy
-    \item to point to a sound/noise
-    \item to show some movements (or dance)
-\end{enumerate}
-
-\fxwarning{Is Introduction the best place for justification for not using 3rd
-scenario?}Differing from first two scenarios, the third scenario had only one
-object in the video \ie~the actor (human or robot). In the first two scenarios,
-a participant could make gaze transitions, say, between the robot and the toys
-for the first scene. In contrast, in the third scene, a participant could only
-look at the robot showing its movements. The third scene, hence, was more
-related to observing the various body movements and was not helpful in
-identifying differences in gaze patterns based on LC and HC scenarios and
-therefore, we did not consider it for our study.
-
-\subsection{Novel Contributions}
-
-The study and results presented in this article lead to two main contributions:
-new insights on the impact of the cognitive context of the interaction on the
-perception of a robot by humans; a novel unbiased\fxwarning{correct?}
-methodology based on eye-tracking to measure anthropomorphic attributions during
-a running human-robot interaction.
-
-Our first contribution extends our understanding of the attribution of
-human-like characteristics to robot by exploring the role of the interaction
-context. As we will show in the article, it appears that \textbf{even relatively
-subtle context priming may lead to significantly different anthropomorphic
-perceptions of the exact same robot, performing the exact same task}, as
-confirmed both by distinct gaze patterns, and different reported perceptions in
-questionnaires. As far as we know, this effect had not been previously
-evidenced.
-
-This leads to a second-order effect that we also evidence here: depending on the
-cognitive context, the tendency to attribute human-like characteristics to robot
-\textbf{evolves} in significantly different ways: after observing a robot in a
-context that pre-suppose deeper cognitive capabilities, \textbf{people increase
-their general tendency to anthropomorphize robots} compared to a shallow
-cognitive context, even though the robot appearance and behaviour is the exact
-same.
-
-The second contribution is a methodological one: we present in this article
-\textbf{a novel technique to assess anthropomorphic projections that relies on a
-biometric measurement (eye-tracking) to compare gaze fixation durations on
-the face of the robot}. We cross-validate this new metric with existing,
-established, questionnaires. Compared to current techniques (post-hoc
-annotations of videos and questionnaires), this new approach is objective,
-is less impacted by experimental biases (like the \emph{observer effect},
-where the subject's behaviour is impacted by the fact he/she knows that
-he/she is observed) and take place during the interaction itself
-(\emph{in-the-moment} measurement).
-
-Besides, we also introduce a new kind of visual stimuli, specifically designed
-to study the impact of non-appearance, non-behavioural related effects on the
-human-like perception of robots. We make these video stimuli available to the
-community, and therefore invite our colleagues to reproduce our experimental
-results.
-
-As a whole, we believe that this article provide a solid contribution, both in
-terms of methodology and experimental evidence, to our understanding of one of
-the intricate psychological effects that come to play when humans and robots
-interact.
+Finally, the hypothesis \h{4} examines whether the cognitive context affects the
+general tendency to anthropomorphize, \ie whether observing a
+robot acting in an \emph{human-like} context leads to an increased level of
+anthropomorphic attributions to robots (and vice versa).
 
@@
 
-This study is build as an eye-tracking experiment (mainly measuring fixation
-times on various body parts) where participants watch short videos of an agent
-(either a robot or a human) performing very simple task (picking an object or
-pointing toward a sound source), in two different socio-cognitive contexts.
-These contexts, created by priming and/or audio cues, are designed to elicit
-either a shallow cognitive context (that participant would refer as a
-\emph{machine-like} situation) or a deeper cognitive context (refered as a
-\emph{human-like} situation).
+As hinted, this study is build as an eye-tracking experiment (using a stationary
+eye-tracker) where participants watch short videos of an agent -- either a robot
+(Aldebaran Robotics' Nao) or a human -- performing very simple task (picking an
+object or pointing toward a sound source), in two different socio-cognitive
+contexts.  These contexts, created by priming and/or audio cues, are designed to
+elicit either a shallow cognitive context (that participant would refer as a
+\emph{machine-like situation}) or a deeper cognitive context (refered as a
+\emph{human-like situation}).
+
+Besides eye-tracking, the participants' perception of robots is assessed through a
+pre- and a post-questionnaire, described below.
 
@@
 
-The study follows a 2x2 design, summarized in table~\ref{table:design}. Our two
+The study follows a 2$\times$2 design, summarized in table~\ref{table:design}. Our two
 independent variables are the level of socio-cognitive context (\emph{shallow
-cognitive context} vs \emph{deep cognitive context}) and the nature of the
+cognitive context} \vs \emph{deep cognitive context}) and the nature of the
 agent appearing in the stimulus (a \emph{robot}, eliciting a \emph{human-robot} interaction
@@
         \emph{human} condition is within subject, while the \emph{shallow
-        cognitive context} vs \emph{deep cognitive context} is between subject.
+        cognitive context} \vs \emph{deep cognitive context} is between subject.
         Two stimuli (\emph{Picking} task, {\bf A}, and \emph{Sound} task,
         {\bf B}) were shown to the participants, introduced by brief verbal
-        commands, reproduced in the table. While visually identical (see
-        screenshots on figure~\ref{fig:stimuli}), the stimuli were introduced
-        with different commands in the two conditions \emph{shallow} and
-        \emph{deep cognitive
-        context}.}
+        commands, reproduced in the table. Figure~\ref{fig:stimuli} shows
+        pictures of the four stimuli.}
 
@@
 
-The audio (and audio only) of these four videos was edited to create two sets of
-stimuli: one for the \emph{shallow cognitive context} condition, one for the
-\emph{deep cognitive context} condition. The audio editing consisted in
-inserting \emph{different commands} to initiate the tasks (reported in
-table~\ref{table:design}), and, in the \emph{Sound} task, to use as sound source
-either a repetitive bip (\emph{shallow cognitive context}) or the sound of a
-crying baby (\emph{deep cognitive context}).
+The audio (and audio only) of these four videos was then edited to create two
+sets of stimuli: one for the \emph{shallow cognitive context} condition, one for
+the \emph{deep cognitive context} condition. The audio editing consisted in
+inserting different commands to initiate the tasks (reported in
+table~\ref{table:design}): in the \emph{Picking} task for instance, the object
+that the agent had to pick was described either as a \emph{``brown toy''} or as
+\emph{``your favorite toy''}. In the former case, the object was refered through
+visible, objective features which do not suppose as deep cognitive capabilities
+as in the latter case where the agent is implicitly supposed to have
+tastes and preferences such as it can choose a toy as its favorite.
+
+This simple verbal priming (\emph{``brown toy''} \vs \emph{``your favorite
+toy''}) set the cognitive context (\emph{shallow} \vs \emph{deep}) and was
+expected to lead to different perceptions of the interaction
+(\emph{machine-like} \vs \emph{human-like}). We reinforced this effect in the
+\emph{Sound} task: not only the verbal priming but also the sound played by the
+speakers during the task was altered: either a repetitive bip (\emph{shallow
+cognitive context}) or the sound of a crying baby (\emph{deeper cognitive
+context}).
 
@@
 
-    \caption{\small Screenshots of the 2x2 stimuli. Note that the images above have been
+    \caption{\small Screenshots of the 2$\times$2 stimuli. Note that the images above have been
     slightly cropped: the original video are framed so that the agent (robot or
@@
 
+Section~\ref{stimuli_design}, at the end of the article, specifically discusses
+the design constraints that were accounted for while creating the above stimuli.
+
 \subsection{Questionnaires}
@@
 Before starting the experiment, the participants were asked to fill a
-questionnaire which had 49 questions. The responses to the questions were scaled
-in the 5-point Likert scale, numerically ranging from -2 to 2. The questionnaire
-had ten questions from the 10 item big-five personality questionnaire. And then
-there were questions taken from Godspeed questionnaire and other
-questionnaires. In this report, we refer to this questionnaire as the
-pre-questionnaire \ie before the experiment, and it typically took 5 minutes for
-participants to fill it.
+pre-questionnaire which had 49 questions (5-point Likert scale). The
+questionnaire comprised of questions assessing their familiarity for robots, 10
+items from \emph{big-five} personality questionnaire, 15 questions taken from
+Godspeed questionnaire (questions related to \emph{anthropomorphism},
+\emph{likeability} and \emph{perceived intelligence}), 20 questions rating
+human-likeness (from~\cite{ruijten_introducing_2014})\footnote{The
+the pre- and post-questionnaires are available online:
+\url{https://github.com/chili-epfl/anthropomorphism-eyetracking}.}. The pre-questionnaire
+typically took 5 minutes for participants to fill. The results were turned into
+a score noted \anti (\emph{initial tendency to anthropomorphize}) following a
+method presented below (section~\ref{questionnaires_processing}).
 
-A second questionnaire was administered at the end of the experiment, that was
-almost identical to the pre-questionnaire.  This questionnaire typically took 3
-to 4 minutes to fill and we refer to this as the post-questionnaire.
+The post-questionnaire was administered at the end of the experiment, and was
+close to the pre-questionnaire: the personality questions were omitted, and a
+manipulation check question was added (\emph{``In your opinion, the tasks that
+you watched were more: A robot kind of task ... A human kind of task''}).
+This questionnaire typically took 3 to 4 minutes to fill. The resulting score is
+noted \antf (\emph{final tendency to anthropomorphism}).
 
-The difference (noted \deltaant, computation detailed below) observed for
-each participant between the pre- and post-questionnaires form the dependent
-variable of our experiment. It reflects the impact of the video stimuli on the
-anthropomorphic perception that they have of robots \emph{in general}: the
-Godspeed questions used in the questionnaires are not specific to the Nao robot,
-and assess in a broader way how humans perceive robots.
+The difference \deltaant measured for each participant between the pre-
+and post-questionnaires forms the dependent variable of our experiment. It
+reflects the impact of the video stimuli on the anthropomorphic perception that
+they have of robots \emph{in general}: the Godspeed questions used in the
+questionnaires are not specific to the Nao robot used in this particular
+experiment, and indeed assess how humans perceive robots in a broad sense.
 
@@
 
-\subsubsection{Participants}
+\paragraph{Participants}
 
@@
 57 subjects (mean age: 20.9, $SD=3.9$, 32 females and 25 males).
-
 The participants were recruited amongst students of our university. To avoid
@@
 Computer Science and Electronics curriculum were excluded. This was \textit{a
-posteriori} comforted as per the questionnaire responses: no participants
+posteriori} comforted by the questionnaire responses: no participants
 reported itself as being very familiar with robots, 8 reported some familiarity
-and 7 out of 57 own a domestic robot (vacuum cleaner).
+and 7 out of 57 owned a domestic robot (vacuum cleaner).
 
 The study lasted about 15 minutes per participant; each participant was invited
-for one session only. Before leaving, each participant was given a reward
-equivalent to EUR 10.
+for one session only.
 
-The study follows a 2$\times$2 design (table~\ref{table:design}): the
-\emph{deep} vs {shallow cognitive context} condition was between-subject ( 31
-subjects performed the \emph{deep cognitive} tasks while 26 were in the
-\emph{shallow cognitive} condition); the \emph{robot} vs \emph{human} condition
-was within-subject (the order of stimuli presentation was counter-balanced over
-the 57 participants).
+As stated previously, the study follows a 2$\times$2 design
+(table~\ref{table:design}): the \emph{deep} \vs {shallow cognitive context}
+condition was between-subject ( 31 subjects performed the \emph{deep cognitive}
+tasks while 26 were in the \emph{shallow cognitive} condition); the \emph{robot}
+\vs \emph{human} condition was within-subject (the order of stimuli presentation
+was counter-balanced over the 57 participants).
 
-\subsubsection{Pre-questionnaire and familiarization}
+\paragraph{Pre-questionnaire and familiarization}
 
@@
 Before the experiment, participants were made to read, understand and sign a
-standard consent form. Participants were then asked to fill the 49 questions of
+consent form. Participants were then asked to fill the 49 questions of
 the pre-questionnaire, without time constraint\fxwarning{right?}.
 
-After the pre questionnaire, we invited the participants to an initial
+After the pre-questionnaire, we invited the participants to an initial
 free interaction with a \textbf{powered-off} Nao robot (we did not constraint
-the time, and participants played between 2 and 3 minutes ith the robot).
+the time, and participants played between 2 and 3 minutes with the robot).
 
@@
 
-\subsubsection{Videos}
+\paragraph{Videos}
 
@@
 
-\subsubsection{Post-questionnaire}
+\paragraph{Post-questionnaire}
 
 Finally, the participants were asked to fill the post-questionnaire.
+Before leaving, each participant was given a reward
+equivalent to EUR 10.
 
@@
 
-Among the two scenarios, the first was one was about the robot/human picking up
-a toy and the second one about pointing to the noise. As seen in
-figure~\ref{fig:aoi}, we defined 10 areas of interest (AOIs): one on the head of
-the agent (robot or human), two on the arms (left and right), two on the hands,
-two on the legs and one on the torso. Besides, we defined one area of interest
-per toy or speaker (depending on the stimulus).
+As seen in figure~\ref{fig:aoi}, we defined 10 areas of interest (AOIs): one on
+the head of the agent (robot or human), two on the arms (left and right), two on
+the hands, two on the legs and one on the torso. Besides, we defined one area of
+interest per toy or speaker (depending on the stimulus).
 
@@
 
-We collected the gazes falling into one of these 10 zones and analyzed
-their distribution (producing what we call \emph{gaze patterns}).
+We collected the gazes falling into one of these 10 zones and normalized them to
+account for different total video duration and surface of AOIs between the robot
+and human conditions\fxfatal{do we?}. We finally analyzed their distribution,
+producing what we call \emph{gaze patterns}.
 
@@
 
-An important data to be obtained here is $\delta_{\mathcal{H},\mathcal{R}}$. This is calculated by
-taking the difference between the ratio of net dwell time on an AOI and the AOI
-fixation coverage summed over all the AOIs in the scene. Hence,
-$\delta_{\mathcal{H},\mathcal{R}}$ is expressed as a ratio in the range of 0 to
-1. Similarly, the differences between gaze patterns of two participants, where
-one watches the LC task, given by $\delta_{shallow}^{\mathcal{H},\mathcal{R}}$ and
-the other watches the HC task, given by
-$\delta_{deep}^{\mathcal{H},\mathcal{R}}$ are important gaze variables.
+\fxfatal{To be rewritten} An important data to be obtained here is
+$\delta_{\mathcal{H},\mathcal{R}}$. This is calculated by taking the difference
+between the ratio of net dwell time on an AOI and the AOI fixation coverage
+summed over all the AOIs in the scene. Hence, $\delta_{\mathcal{H},\mathcal{R}}$
+is expressed as a ratio in the range of 0 to 1. Similarly, the differences
+between gaze patterns of two participants, where one watches the LC task, given
+by $\delta_{shallow}^{\mathcal{H},\mathcal{R}}$ and the other watches the HC
+task, given by $\delta_{deep}^{\mathcal{H},\mathcal{R}}$ are important gaze
+variables.
 
 \subsubsection{Questionnaires processing}
-
+\label{questionnaires_processing}
 \fxnote{TDB}
@@
 ($\mathcal{H}$) and robot ($\mathcal{R}$) interactions across \emph{shallow} and
-\emph{deep cognitive context} conditions, we have the following results. (the
+\emph{deep cognitive context} conditions, we have the following
+results.\footnote{The
 detailed statistics and code used for obtaining the results are available here :
-\url{https://github.com/chili-epfl/anthropomorphism-eyetracking})
+\url{https://github.com/chili-epfl/anthropomorphism-eyetracking}.}
 
@@
 \begin{figure}
-    {\includegraphics[width=3.3in]{ManipulationCheck}}
-    \caption{Manipulation check}
+    \centering
+    \includegraphics[width=10cm]{ManipulationCheck}
+    \caption{\fxfatal{Incorrect nb of particpants! Label should be shallow/deep
+    instead of low/high}Manipulation check}
     \label{fig:ManipulationCheck}
@@
 
-In our post-questionnaire, we had a question asking the participants about
-whether the video has a robot kind of task or a human kind of task on a scale of
--2 to 2 where -2 refers to robot kind of task. As can be seen in figure 2, we
-got a significant correlation in this manipulation check ($F[1,36] = 20.42, p <
-.01$) which means that the participants that were shown the \emph{shallow
-cognitive context} videos identified the task as more robot-like and
-participants watching \emph{deep cognitive context} videos perceived the tasks
-as more human-like.
+Participants were asked in the post-questionnaire whether the video presented a
+\emph{``robot kind of task''} or a \emph{``human kind of task''} on a 5-points
+scale (numerical values ranging from -2 to 2, where -2 refers to robot kind of
+task). As can be seen in figure 2, we got a significant correlation in this
+manipulation check ($F[1,36] = 20.42, p < .01$) which validates our manipulation
+and supports \h{0}: the participants that were shown the \emph{shallow cognitive
+context} videos identified the task as more robot-like and participants watching
+\emph{deep cognitive context} videos perceived the tasks as more human-like.
 
-\subsection{H1: Gaze differences between human and robot conditions}
+\subsection{Gaze differences between human and robot conditions}
 
 We grouped the 8 areas of interest located on the agent into 4 categories : {\sf
-head}, {\sf arm} (containing both arms and hands), {\sf torso}, {\sf leg}
-(including both legs). And this is the result that we obtained from the ANOVA
-between gaze patterns on the AOIs versus the human and robot videos :
+head}, {\sf arms} (containing both arms and hands), {\sf torso}, {\sf legs}
+(including both legs). Running an ANOVA against gaze fixations on the areas of
+interest and the robot \vs human conditions, we obtain the following results:
 
@@
 
-{\sf arm}: the fixations on the arms for the $\mathcal{H}$ video
+{\sf arms}: the fixations on the arms for the $\mathcal{H}$ video
 were also greater than that for the robot video ($F[1,36] = 18.65, p < .01$)
 
-{\sf leg}: the fixations on the legs were much lower
+{\sf legs}: the fixations on the legs were much lower
 for the human video as compared to the robot video ($F[1,36] = 2.89, p < .1$)
 
-{\sf torso}: the fixations on the torso was more for the
+{\sf torso}: the fixations on the torso were higher for the
 human video than for the robot video ($F[1,36] = 3.54, p < .1$)
 
-\subsection{H2: Interaction between \anti and gaze patterns}
+In summary, and over the duration of these shorts videos, the gaze behaviours
+were significantly different between the robot and human conditions, supporting
+\h{1}.
+
+\subsection{Impact of the tendency to anthropomorphize on the robot \vs human
+gazing behaviours}
 
 We got a significant correlation between $\delta_{\mathcal{H},\mathcal{R}}$ and
-the \anti. As can be seen in figure 3(a), there is a significant negative
+the \anti. As can be seen in figure~\ref{h2}, there is a significant negative
 correlation between the two quantities (Pearson Correlation Coefficient = -0.42,
-p < .01).
+$p < .01$).
 
 \begin{figure}
-    \subfigure[Difference in gaze patterns vs \anti]
-    {\includegraphics[width=3.3in]{H2}\label{GazeDifference-vs-ICA}}
-    \subfigure[Gaze patterns for high vs low condition]
-    {\includegraphics[width=3.3in]{GazeHighLow}\label{GazeHighLow}}
-    \subfigure[Difference between \anti and \antf versus High/Low]
-    {\includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}}
-    \caption{Hypotheses H2, H3, H4}
+    \centering
+    \includegraphics[width=3.3in]{H2}\label{GazeDifference-vs-ICA}
+    \caption{Difference in gaze patterns \vs \anti}
+    \label{h2}
 \end{figure}
 
-\subsection{H3: Gaze patterns for high vs low cognitive condition}
+\subsection{Gaze behaviours in shallow \vs deep cognitive contexts}
 
-This test was done only for robot scenario as the human case is
-by default a source of HC condition, hence, would not make a big impact in
-changing the patterns across the LC and HC conditions. Based on ANOVA results,
-taking just the 5 AOI groups (head, arms, hands, torso, legs) for the robot in
-both LC and HC conditions, the fixations on the head in the HC condition was
-found to be significantly higher than that in the LC condition (F[1,36] = 4.55,
-p < .05). For all other AOI groups, the fixations across LC and HC were almost
-the same. Figure 3(b) shows the distribution of proportion of time spent gazing
-on the 5 AOIs for LC and HC conditions.
+We analysed these possible correlations for robot condition only: the human case is
+inherently a source of deep cognitive context, hiding the effects of our
+manipulation on a shallow \vs deep cognitive context.
 
-\subsection{H4: Difference between \anti and \antf versus High/Low}
+Based on ANOVA results, taking the 5 groups of AOIs {\sf head}, {\sf arms}, {\sf
+hands}, {\sf torso}, {\sf legs} for the robot in both the shallow and deep
+cognitive context conditions, the fixations on the head in the deep condition
+were found to be significantly higher than that in the shallow condition
+($F[1,36] = 4.55, p < .05$). For all other AOIs groups, the fixations across
+shallow and deep conditions were almost the same. Figure~\ref{h3} shows the
+distribution of proportion of time spent gazing on the 5 AOIs for the two
+conditions.
 
-ANOVA between \deltaant and the category of cognitive task
-\ie HC or LC tells us that \deltaant is greater for HC tasks
-than that for the LC tasks (F[1,36] = 6.54, p < .05). The results are shown in
-figure 3(c).
+\begin{figure}
+    \centering
+    \includegraphics[width=3.3in]{GazeHighLow}\label{GazeHighLow}
+    \caption{Gaze fixations on the different areas on interest, for shallow \vs
+    deep cognitive context conditions.}
+    \label{h3}
+\end{figure}
 
-\section{Discussion}
+This constitutes the main result of this study: inducing a deeper cognitive
+context for the same interaction suffices to lead to significantly longer
+fixations on the agent's head.
+
+\subsection{Correlation between cognitive context and changes in anthropomorphic
+attributions}
+
+Running an ANOVA against the evolution of anthropomorphic attributions
+(\deltaant) over the duration of the experiment, in the two cognitive
+conditions, shows that \deltaant is greater for tasks with a deeper cognitive
+context than that for the shallow cognitive tasks ($F[1,36] = 6.54, p < .05$,
+figure~\ref{h4}). In other words, after being exposed to short videos of a robot
+performing simple tasks, subjects primed with a deeper cognitive context report
+a significantly higher tendency to anthropomorphize robots \emph{in general} (as
+the questionnaires on anthropomorphic attributions explicitely refered to
+\emph{robots in general}).
+
+\begin{figure}
+    \centering
+    \includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}
+    \caption{Difference between \anti and \antf in the shallow and deep
+    cognitive contexts.}
+    \label{h4}
+\end{figure}
+
+This result supports \h{4} and validate that the cognitive context impacts the
+attribution of anthropomorphic features to robots. This, in turn, supports
+the \emph{proxy} hypothesis of \h{3}: \emph{head fixations are a proxy for
+higher levels of human-likeness attributions}.
+
+%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Discussion and Conclusion}
+
+\subsection{Discussion}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Summary and Contributions}
 
-\section{Conclusion}
+The study and results presented in this article lead to two main contributions:
+new insights on the impact of the cognitive context of the interaction on the
+perception of a robot by humans; a novel unbiased methodology based on
+eye-tracking to measure anthropomorphic attributions during a running
+human-robot interaction.
 
-In our experiment, we created two kinds of scenarios each for human and
-robot interaction and just by changing the audio commands (priming
-effect), we replicated these videos to create a HC and a LC scene. We recorded
-the gaze patterns of the 57 participants who were made to watch these videos and
-also the participants were asked to fill two questionnaires before and after the
-experiment. These data were analyzed and compared to our four hypotheses. We
-hypothesized that one who anthropomorphizes more would have a similar reaction
-to human and robot conditions, and also that in the HC case, a
-participant's fixations would be more on the head of the actor as compared to
-that in the LC case. We also hypothesized that the HC scene would induce more
-anthropomorphic attitude than the LC scene. We found that the results were
-successful and supported our hypotheses. We also had another scenario where the
-robot/human was asked to move/dance, but this scenario had only one object
-(\ie the actor) showing movements, and hence participants would focus
-more on seeing the movements leaving behind the cognition aspect, which made it
-difficult to differentiate between the LC and HC cases and, therefore, we
-discarded this scenario from our analysis.
+Our first contribution extends our understanding of the attribution of
+human-like characteristics to robot by exploring the role of the interaction
+context. As we show in the article, it appears that \textbf{even relatively
+subtle context priming may lead to significantly different anthropomorphic
+perceptions of the exact same robot, performing the exact same task}, as
+confirmed both by distinct gaze patterns, and different reported perceptions in
+questionnaires. As far as we know, this effect had not been previously
+evidenced.
 
-\subsection{Context and Interaction Design}
+This leads to a second-order effect that we also evidence here: depending on the
+cognitive context, the tendency to attribute human-like characteristics to robot
+\textbf{evolves} in significantly different ways: after observing a robot in a
+context that pre-suppose deeper cognitive capabilities, \textbf{people increase
+their general tendency to anthropomorphize robots} compared to a shallow
+cognitive context, even though the robot appearance and behaviour is the exact
+same.
 
-\fxwarning{discuss here how context can be used to shape the interaction}
+The second contribution is a methodological one: we present in this article
+\textbf{a novel technique to assess anthropomorphic projections that relies on a
+biometric measurement (eye-tracking) to compare gaze fixation durations on
+the face of the robot}. We cross-validate this new metric with existing,
+established, questionnaires. Compared to current techniques (post-hoc
+annotations of videos and questionnaires), this new approach is objective,
+is less impacted by experimental biases (like the \emph{observer effect},
+where the subject's behaviour is impacted by the fact he/she knows that
+he/she is observed) and take place during the interaction itself
+(\emph{in-the-moment} measurement).
 
-Anthropomorphism as a proxy for cognitive/affective bonds that are esthablishing
-between humans and robots.
+Besides, we also introduce a new kind of visual stimuli, specifically designed
+to study the impact of non-appearance, non-behavioural related effects on the
+human-like perception of robots. We make these video stimuli available to the
+community, and therefore invite our colleagues to reproduce our experimental
+results. The next section describe the specificities of these stimuli, and also
+discuss how such a methodology can apply to real-world scenarios.
 
-\fxnote{discuss extensions towards mobile eyetrackers}
+As a whole, the article attempts to contribute to our understanding of an
+intricate psychological effects that come to play when humans and robots
+interact, both in terms of methodology and experimental evidence.
 
+\subsection{Design of the stimuli and applicability of the method to real world
+scenarios}
+\label{stimuli_design}
+
+The video stimuli had to obey to several constraints: they had to depict
+plausible and legible situations, yet simple enough to be suitable for an
+eye-tracking study (simple mechanics, easily distinguishable elements at
+predictable locations). The body parts of the robot or human would need remain
+visible most of the time. The actions had to be meaningful for both a robot and
+a human, and both should be able to perform them in similar ways (similar pace,
+similar movements) without looking ackward.
+
+Finally, the situations needed to support two possible cognitive contexts
+(shallow \vs deeper cognitive context), and triggering one or the other of these
+contexts needed to be done \emph{without changing} the visual part of the
+stimulus.
+
+We initially prepared three different stimuli: the \emph{Picking} task, the
+\emph{Sound} task and a \emph{Dance} task.  During the \emph{Dance} task, the
+agent was either asked to \emph{``Show some movements''} (\emph{shallow
+cognitive context} condition) or to \emph{``Dance with the music''}
+(\emph{deeper cognitive context} condition). While all the participants were
+shown this stimuli as well, we decided to exclude it from the results as the
+nature of the task (participants had to watch body movements) defeated our
+gaze-based investigation method: the subjects expectedly paid attention to the
+whole body of the robot or human (even distribution of the gazes on the body),
+thus making specific gaze patterns on the head difficult to evidence.
+
+This underlines the difficulty of designing appropriate stimuli and raises the
+question of the applicability of our method to real-world, ``in the wild''
+human-robot interaction.
+
+Two main comments can be made: first, we had to carefully design those stimuli
+to \emph{evidence} the link between the (anthropomorphic) perception of a robot
+and actual gaze fixations on the face of the robot. This being granted,
+researchers will not have to design their scenarios in such a constraint way to
+rely on our result, \ie the link between perception and gaze behaviour.
+
+Besides, one may point that, in real-world experiments, the robot does not
+always remain in the field of view of the subject, and, at the very least, the
+body of the robot may be partially occluded at time.  This is certainly true,
+and while new experiments would be welcome to validate it, we believe that our
+method remains effective in these situations. First it relies on the
+\emph{ratio} of the gaze fixations on the head \vs gaze fixations on other parts
+of the body, thus compensating for out-of-sight robots; second, our method
+\emph{does not} provide an \emph{absolute} measurement of the level
+anthropomorphic perception, but rather a \emph{relative} measurement: within a
+group of subject, it enables to classify subjects in term of their level of
+projected anthropomorphism onto the robot.  This means that, while this method
+can not be used to assess the perception of robots between different interaction
+situations (\ie different experiments), it can be employed within a group a
+subjects taking part to the same experiment.
+
+Lastly, the stationary eye-tracker would also have to be replaced by a mobile
+eye-tracker. This would however not impact the interpretation of the results.
+
+%\subsection{Context and Interaction Design}
+%
+%\fxwarning{discuss here how context can be used to shape the interaction}
+%
+%
+%Anthropomorphism as a proxy for cognitive/affective bonds that are esthablishing
+%between humans and robots.
+%
+%\fxnote{discuss extensions towards mobile eyetrackers}
+%
 \bibliographystyle{apacite}

### 2015-07-01 main.tex
Implemented Kshitij changes + rewritten discussion of results

@@
 \usepackage{tikz}
-\usetikzlibrary{decorations.pathreplacing}
+\usetikzlibrary{calc,decorations.pathreplacing}
 \newcommand{\tikzmark}[1]{\tikz[overlay,remember picture] \node (#1) {};}
@@
 appearance of the robot and the design of its behaviours do obviously play a key
-role. This paper however evidences another mechanism at play, more subtle and partially
-unconscious: the context of the interaction, and more precisely, the cognitive
-prerequisites that the interaction presupposes.
+role. This paper however reveals another mechanism at play, which is more subtle
+and partially unconscious: the context of the interaction, and more precisely,
+the cognitive prerequisites that the interaction presupposes.
 
 To study this effect, we propose an original methodology based on eye-tracking
-and a set of stimuli that are visually identical and yet elicit different
+and a set of stimuli that are visually identical and yet induce different
 assumptions regarding the cognitive capabilities of the robot. We then correlate
@@
 that human users build with artificial agents such as
-robots~\citep{lemaignan2014dynamics}, and we propose therefore that
+robots~\citep{lemaignan2014dynamics}. Therefore we propose therefore that
 anthropomorphism can be a useful \emph{proxy} to these intricate psychological
-bonds. This article aims at advancing our understanding of this phenomenon
+bonds. This article aims at improving our understanding of this phenomenon
 \textbf{by evidencing the impact of the cognitive presuppositions implied by the
@@
 the ISO as \textit{``users, tasks, equipment (hardware, software and materials),
-and the physical and social environments in which a product is used''}, and
-accordingly, there are various aspects that can impact how a robot is
+and the physical and social environments in which a product is used''}.
+Accordingly, there are various aspects that can impact how a robot is
 experienced. The real or imagined \textit{purpose} of a robot, including the
@@
 account. Generally, when the context of use of a robot is social, entertaining
-or playful, it will enhance anthropomorphism, compared to when the context is a
+or playful, it will enhance anthropomorphism compared to when the context is a
 routine or focused serious task (security, rescue, \etc).
@@
 \emph{in-the-moment} perspective would refer to one's most immediate
-response/sense in a given situation, while a \emph{reflective} perspective would
+response/sense in a given situation whereas a \emph{reflective} perspective would
 indicate one's reaction/sense of a situation based on a more in-depth
@@
 eye-tracking.  By looking at the eyes fixation on the head of the robot, we have
-been able to evidence significantly different patterns in two experimental
+been able to demonstrate significantly different patterns in two experimental
 conditions subtly different in terms of human-likeness. This eye-tracking based
@@
 
-Our first hypothesis \h{1} is then that gaze behaviour only is sufficient to
+Our first hypothesis \h{1} is that gaze behaviour alone is sufficient to
 know if a subject is looking at a robot or at a human.  More precisely, we
@@
 pre-questionnaire: we expect that people with high tendency to anthropomorphize
-will tend to have similar gaze behaviours while watching either a robot or a
-human performing the same task.
+will tend to have smaller differences in their gaze behaviours while watching
+either a robot or a human performing the same task.
 
@@
 robot acting in an \emph{human-like} context leads to an increased level of
-anthropomorphic attributions to robots (and vice versa).
+anthropomorphic attributions to robots (and vice versa). This also provides us
+with a way to triangulate the behavioural measures with the subjective
+attribution of anthropomorphism.
 
@@
 As hinted, this study is build as an eye-tracking experiment (using a stationary
-eye-tracker) where participants watch short videos of an agent -- either a robot
-(Aldebaran Robotics' Nao) or a human -- performing very simple task (picking an
-object or pointing toward a sound source), in two different socio-cognitive
-contexts.  These contexts, created by priming and/or audio cues, are designed to
-elicit either a shallow cognitive context (that participant would refer as a
-\emph{machine-like situation}) or a deeper cognitive context (refered as a
-\emph{human-like situation}).
+eye-tracker SMI RED 250) where participants watch short videos of an agent --
+either a robot (Aldebaran Robotics' Nao) or a human -- performing very simple
+task (picking an object or pointing toward a sound source), in two different
+socio-cognitive contexts.  These contexts, created by priming and/or audio cues,
+are designed to elicit either a shallow cognitive context (that participant
+would refer as a \emph{machine-like situation}) or a deeper cognitive context
+(refered as a \emph{human-like situation}).
 
 Besides eye-tracking, the participants' perception of robots is assessed through a
-pre- and a post-questionnaire, described below.
+pre- and a post-questionnaire interaction, described below.
 
@@
     \tikzmark{left}
-    \begin{tabular}{l|p{2.5cm}|p{2.5cm}}
-        & \tikzmark{top1} Shallow cognitive context & Deep cognitive \tikzmark{top2} context  \\
+    \begin{tabular}{l|p{4cm}|p{4cm}}
+        & \tikzmark{top1} Shallow cognitive context & Deep cognitive context \tikzmark{top2}  \\
         \hline
@@
         \draw [decoration={brace,amplitude=0.5em},decorate,thick]
-            (top -| top1.west) --  (top -| top2.east) node[midway, above=0.5em] {\scriptsize between subjects};
+        (top -| top1.west) --  (top -| bottom.east) node[midway, above=0.5em] {\scriptsize between subjects};
 
         \draw [decoration={brace,amplitude=0.5em},decorate,thick]
-            (left |- bottom) --  (left |- left1.north) node[midway,above=3em,left=1em,rotate=90] {\scriptsize within subject};
+        ($(left |- bottom)+(1.8,-0.3)$) --  ($(left |- left1.north)+(1.8,0.2)$) node[midway,above=3em,left=1em,rotate=90] {\scriptsize within subject};
     \end{tikzpicture}
@@
     \subfigure[\emph{Picking} task, human condition]{
-        \includegraphics[height=5cm]{stimulus-human-toys}
+        \includegraphics[height=5cm]{stimulus-human-toys-anon}
     }
@@
     \subfigure[\emph{Sound} task, human condition]{
-        \includegraphics[height=5cm]{stimulus-human-noise}
+        \includegraphics[height=5cm]{stimulus-human-noise-anon}
     }
@@
 pre-questionnaire which had 49 questions (5-point Likert scale). The
-questionnaire comprised of questions assessing their familiarity for robots, 10
-items from \emph{big-five} personality questionnaire, 15 questions taken from
+questionnaire comprised of questions assessing their familiarity with robots, 10
+items from \emph{Big-Five} personality questionnaire, 15 questions taken from
 Godspeed questionnaire (questions related to \emph{anthropomorphism},
-\emph{likeability} and \emph{perceived intelligence}), 20 questions rating
+\emph{likeability} and \emph{perceived intelligence}) and 20 questions rating
 human-likeness (from~\cite{ruijten_introducing_2014})\footnote{The
@@
 
-\fxwarning{Was it first the pre-questionnaire or the familiarization?}
 Before the experiment, participants were made to read, understand and sign a
 consent form. Participants were then asked to fill the 49 questions of
-the pre-questionnaire, without time constraint\fxwarning{right?}.
+the pre-questionnaire, with a 10 minutes time limit that none of the participants
+reached.
 
@@
 
-\paragraph{Areas Of interest}
+\paragraph{Areas of interest}
 
@@
 account for different total video duration and surface of AOIs between the robot
-and human conditions\fxfatal{do we?}. We finally analyzed their distribution,
-producing what we call \emph{gaze patterns}.
+and human conditions. We finally analyzed their distribution, producing what we
+call \emph{gaze patterns}.
 
-\paragraph{Difference in gaze patterns}
+\paragraph{Differences between gaze behaviours}
 
-\fxfatal{To be rewritten} An important data to be obtained here is
-$\delta_{\mathcal{H},\mathcal{R}}$. This is calculated by taking the difference
-between the ratio of net dwell time on an AOI and the AOI fixation coverage
-summed over all the AOIs in the scene. Hence, $\delta_{\mathcal{H},\mathcal{R}}$
-is expressed as a ratio in the range of 0 to 1. Similarly, the differences
-between gaze patterns of two participants, where one watches the LC task, given
-by $\delta_{shallow}^{\mathcal{H},\mathcal{R}}$ and the other watches the HC
-task, given by $\delta_{deep}^{\mathcal{H},\mathcal{R}}$ are important gaze
-variables.
+To compare gazing behaviours across conditions, we compute a \emph{difference of
+of gaze pattern} as...
+
+\fxfatal{put here the formula + explanations}
 
@@
 \label{questionnaires_processing}
-\fxnote{TDB}
 
@@
 These values were computed by a direct sum of the rating provided by the
-participants for the Godspeed's questions in the category
-\emph{Anthropomorphism} and \emph{\fxwarning{?}...}. These ten questions were
-rated between -2 and 2, hence \anti and \antf vary between -20 and 20.
-
-The other questions (including the Big-Five personality test) were not used for
-this study.
+participants for the Godspeed's questions in the categories
+\emph{anthropomorphism} and \emph{likeability}. These ten questions were rated
+between -2 and 2, hence \anti and \antf vary between -20 and 20.  The other
+questions (including the Big-Five personality test) were not used for this
+study.
 
@@
     \includegraphics[width=10cm]{ManipulationCheck}
-    \caption{\fxfatal{Incorrect nb of particpants! Label should be shallow/deep
-    instead of low/high}Manipulation check}
+    \caption{Average ratings for the manipulation check question}
     \label{fig:ManipulationCheck}
@@
 This result supports \h{4} and validate that the cognitive context impacts the
-attribution of anthropomorphic features to robots. This, in turn, supports
-the \emph{proxy} hypothesis of \h{3}: \emph{head fixations are a proxy for
-higher levels of human-likeness attributions}.
+attribution of anthropomorphic features to robots. This, in turn, supports the
+\emph{proxy} hypothesis of \h{3}: \emph{head fixations are a proxy for higher
+levels of human-likeness attributions}.
 
@@
 
-\subsection{Discussion}
+\subsection{Discussion of the results}
 
-Based on the results that we obtained, we can now verify our four hypotheses.
-For the first hypothesis where we state that the gaze patterns can distinguish
-between human and robot interaction scenarios, we get greater
-amount of fixation on the head, arms and torso for the human scenario as
-compared to the robot scenario. This can be explained by the fact that
-human is by default perceived as a high cognitive agent compared to a robot.
-Hence, the proportion of time spent on looking at the head is more in case of
-human videos as compared to robot videos. But the trend is opposite for legs.
-This might be explained by the fact that the participants are fascinated by the
-joints on the robot's legs \ie the novelty effect. Overall, this
-result weakly validates our hypothesis.
+The presented results bring some light on our initial hypotheses.
 
-In the second hypothesis, where we claim that $\delta_{\mathcal{H},\mathcal{R}}$
-should correlate with the participants' \anti, we obtain in our results, a
-significant negative correlation between the two quantities. From the negative
-correlation, we can understand that if \anti is high, it means that the
-\textit{human likeliness ascription} (HLA) is high (which means that there is a
-greater tendency to anthropomorphize) which indicates that
-$\delta_{\mathcal{H},\mathcal{R}}$ should be low. This supports our hypothesis
-and can be explained by the fact that if HLA is high for a participant, then
-even the robot videos are quite human-like for such participant.
+The clearly significant correlation between deep \vs shallow conditions and the
+answers to the question \emph{Were the task more robot-like or human-like?}
+proves that our manipulation was successful, and that a shallow cognitive
+context was indeed associated to a robot-like situation, while a deeper
+cognitive context was associated to a human-like situation (\h{0}).
 
-The third hypothesis where we state that the gaze patterns can distinguish
-between HC and LC tasks, can also be supported by our results. As can be seen in
-figure 3(b), the proportion of time spent by participants on looking at the head
-is significantly higher in HC task as compared to LC task. When participants
-ascribe more anthropomorphic features to robot, they look more at the head than
-when they ascribe less anthropomorphic features.
+The hypothesis \h{1} postulated that the gaze behaviours alone could tell if the
+subjects was observing a robot or a human. Indeed, our results show
+significantly different (normalized) fixations: the gaze distribution of a human
+observer are different for humans and robots.
 
-Finally for the fourth hypothesis where we state that the cognitive priming will
-have an effect on \deltaant, as seen in the results, \deltaant
-for participants that watched the HC task is greater than that for the
-participants who watched LC task. This proves the fact that HLA was induced by
-the videos and in fact, the HC tasks impose a greater HLA on the minds of
-participants than the LC tasks. This shows the typical priming effect of the
-audio command given in the beginning of the video and highlights the variation
-in HLA based on the interaction scenario (LC versus HC) thereby supporting our
+Hypothesis \h{2} looked at a possible interaction between our potential to
+anthropomorphize (as measured in the pre-questionnaire) and our actual gaze
+behaviour, the hypothesis being that high anthropomorphizers would show smaller
+differences between the way they look at robots and humans (since they would
+consider robots closer to humans than low anthropomorphizers). Our data supports
+this hypothesis: participants reporting an higher tendency to anthropomorphize
+tend to have similar gazing behaviours whether they look at humans or at robots.
+
+To rephrase it: statistically speaking, your tendency to anthropomorphize things
+is reflected in the way you look at these things: you will also look at them
+\emph{as if they were humans}.
+
+The third hypothesis \h{3} proposes that head fixations are related to the
+cognitive context, which is clearly supported by our data: in deeper cognitive
+context, one tends to spend more time looking at the head of the interacting
+agent than in a shallow cognitive context. We also hypothesized that, in turn,
+head fixations could act as a \emph{proxy to anthropomorphic projections}: as
+underlined in the previous section, our data also support this second
 hypothesis.
 
-We analyze the gaze distribution in this study only based on the AOI net dwell
-times . Apart from this, the gaze transition among AOIs can be another way of
-fetching gaze patterns which is not used in this study.
-
-%%%%%%%%%%%%%%%%%%%%%%
-
-No correlation between delta opinion and gaze fixation on head: are we measuring
-two different things? or hidden variable?
-
-If different things, then, gaze is possibly a better metric: in-the-moment, does
-not suffer post-hoc reconstruction.
+Finally, the hypothesis \h{4} looks at the dynamic of anthropomorphic
+projections, with the hypothesis that watching an interaction with a particular
+robot in a deeper cognitive context may impact \emph{globally} the
+anthropomorphic perceptions of robots. This is supported by our study.
 
@@
 confirmed both by distinct gaze patterns, and different reported perceptions in
-questionnaires. As far as we know, this effect had not been previously
+questionnaires. To the best of our knowledge, this effect had not been previously
 evidenced.
@@
 their general tendency to anthropomorphize robots} compared to a shallow
-cognitive context, even though the robot appearance and behaviour is the exact
-same.
+cognitive context, even though the robot appearance and visual behaviour is the
+exact same.
 

### 2015-07-02 main.tex
Fixed spacing of macros

@@
 
-\newcommand{\anti}{{$\mathcal{A}_0$ }}
-\newcommand{\antf}{{$\mathcal{A}_1$ }}
-\newcommand{\deltaant}{{ $\Delta_{\mathcal{A}_0,\mathcal{A}_1}$ }}
+\newcommand{\anti}{{$\mathcal{A}_0$\xspace}}
+\newcommand{\antf}{{$\mathcal{A}_1$\xspace}}
+\newcommand{\deltaant}{{ $\Delta_{\mathcal{A}_0,\mathcal{A}_1}$\xspace}}
 
@@
 We ran first a pilot study with 10 participants, followed by an experiment with
-57 subjects (mean age: 20.9, $SD=3.9$, 32 females and 25 males).
+56 subjects (mean age: 20.9, $SD=3.9$, 31 females and 25 males).
 The participants were recruited amongst students of our university. To avoid
@@
 reported itself as being very familiar with robots, 8 reported some familiarity
-and 7 out of 57 owned a domestic robot (vacuum cleaner).
+and 7 out of 56 owned a domestic robot (vacuum cleaner).
 
@@
 (table~\ref{table:design}): the \emph{deep} \vs {shallow cognitive context}
-condition was between-subject ( 31 subjects performed the \emph{deep cognitive}
+condition was between-subject ( 30 subjects performed the \emph{deep cognitive}
 tasks while 26 were in the \emph{shallow cognitive} condition); the \emph{robot}
 \vs \emph{human} condition was within-subject (the order of stimuli presentation
-was counter-balanced over the 57 participants).
+was counter-balanced over the 56 participants).
 
@@
 
-We collected the gazes falling into one of these 10 zones and normalized them to
-account for different total video duration and surface of AOIs between the robot
-and human conditions. We finally analyzed their distribution, producing what we
-call \emph{gaze patterns}.
+We recorded the fixations on one of these 10 zones and normalized by different total video duration and surface of AOIs between the robot and human conditions.
+We finally analyzed their distribution, producing what we
+call \emph{gaze patterns}. The difference in the gaze patterns over ``N'' AOis can be calculated as follows:\\
+
+$ \frac{\sum_{AOI=1}^{N}\left | \frac{Time_{Human}^{i}}{Area_{Human}^{i}} - \frac{Time_{Robot}^{i}}{Area_{Robot}^{i}} \right |}{N}$
 
@@
 
-Based on the experiments conducted on 57 participants in the human
+Based on the experiments conducted on 55 participants in the human
 ($\mathcal{H}$) and robot ($\mathcal{R}$) interactions across \emph{shallow} and
@@
 task). As can be seen in figure 2, we got a significant correlation in this
-manipulation check ($F[1,36] = 20.42, p < .01$) which validates our manipulation
+manipulation check ($F[1,54] = 29.0, p < .001$) which validates our manipulation
 and supports \h{0}: the participants that were shown the \emph{shallow cognitive
@@
 {\sf head}: the fixations on the head for the human video
-were observed to more than that for the robot video ($F[1,36] = 6.60, p < .05$)
+were observed to more than that for the robot video ($F[1,54] = 12.7, p < .001$)
 
 {\sf arms}: the fixations on the arms for the $\mathcal{H}$ video
-were also greater than that for the robot video ($F[1,36] = 18.65, p < .01$)
+were also greater than that for the robot video ($F[1,54] = 16.5, p < .01$)
 
 {\sf legs}: the fixations on the legs were much lower
-for the human video as compared to the robot video ($F[1,36] = 2.89, p < .1$)
+for the human video as compared to the robot video ($F[1,54] = 1.9, p < .1$)
 
 {\sf torso}: the fixations on the torso were higher for the
-human video than for the robot video ($F[1,36] = 3.54, p < .1$)
+human video than for the robot video ($F[1,54] = 2.65, p < .1$)
 
@@
 the \anti. As can be seen in figure~\ref{h2}, there is a significant negative
-correlation between the two quantities (Pearson Correlation Coefficient = -0.42,
-$p < .01$).
+correlation between the two quantities (Pearson Correlation Coefficient = -0.43,
+$p < .001$).
 
@@
 were found to be significantly higher than that in the shallow condition
-($F[1,36] = 4.55, p < .05$). For all other AOIs groups, the fixations across
+($F[1,54] = 4.2, p < .05$). For all other AOIs groups, the fixations across
 shallow and deep conditions were almost the same. Figure~\ref{h3} shows the
@@
 conditions, shows that \deltaant is greater for tasks with a deeper cognitive
-context than that for the shallow cognitive tasks ($F[1,36] = 6.54, p < .05$,
+context than that for the shallow cognitive tasks ($F[1,54] = 6.54, p < .05$,
 figure~\ref{h4}). In other words, after being exposed to short videos of a robot

### 2015-07-02 main.tex
Minor fix to one subtitle
Modified Figures
and Stats

@@
 
-\newcommand{\anti}{{$\mathcal{A}_0$\xspace}}
-\newcommand{\antf}{{$\mathcal{A}_1$\xspace}}
-\newcommand{\deltaant}{{ $\Delta_{\mathcal{A}_0,\mathcal{A}_1}$\xspace}}
+\newcommand{\anti}{{$\mathcal{A}_0$ }}
+\newcommand{\antf}{{$\mathcal{A}_1$ }}
+\newcommand{\deltaant}{{ $\Delta_{\mathcal{A}_0,\mathcal{A}_1}$ }}
 
@@
 
-We recorded the fixations on one of these 10 zones and normalized by different total video duration and surface of AOIs between the robot and human conditions.
-We finally analyzed their distribution, producing what we
-call \emph{gaze patterns}. The difference in the gaze patterns over ``N'' AOis can be calculated as follows:\\
-
-$ \frac{\sum_{AOI=1}^{N}\left | \frac{Time_{Human}^{i}}{Area_{Human}^{i}} - \frac{Time_{Robot}^{i}}{Area_{Robot}^{i}} \right |}{N}$
+We collected the gazes falling into one of these 10 zones and normalized them to
+account for different total video duration and surface of AOIs between the robot
+and human conditions. We finally analyzed their distribution, producing what we
+call \emph{gaze patterns}.
 

### 2015-07-02 main.tex
Formula for gaze difference
Updated title

--- 2015-07-02 main.tex
@@
 
-\rightheader{Impact of Cognitive Context in the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
+\rightheader{Cognitive Context: Impace on the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
 \leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
-\title{Impact of Context in the Perception of a Robot}
+\title{Cognitive Context: Impact on the Perception of a Robot}
 
@@
 
-\subsection{Impact of the tendency to anthropomorphize on the robot \vs human
+\subsection{Impact of the tendency to anthropomorphize on human
 gazing behaviours}

### 2015-07-02 main.tex
Minor tuning

@@
 
-\rightheader{Cognitive Context: Impace on the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
+\rightheader{Cognitive Context: Impact on the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
 \leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
@@
 
+Figure~\ref{course_of_study} gives an overview of the protocol, detailed
+hereafter.
+
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.3\linewidth]{experimentFlow}
+    \caption{Overview of the course of the study}
+    \label{course_of_study}
+\end{figure}
 \paragraph{Participants}
@@
 
-$ \frac{\sum_{AOI=1}^{N}\left | \frac{Time_{Human}^{i}}{Area_{Human}^{i}} - \frac{Time_{Robot}^{i}}{Area_{Robot}^{i}} \right |}{N}$
-
 \paragraph{Differences between gaze behaviours}
 
-To compare gazing behaviours across conditions, we compute a \emph{difference of
-of gaze pattern} as...
+To compare gazing behaviours across conditions, we compute a \emph{difference in
+gaze patterns} over the $N(=10)$ AOIs:
 
-\fxfatal{put here the formula + explanations}
+{\large
+\[
+    \delta_{\mathcal{H}, \mathcal{R}}^{\text{gaze}} =
+    \frac{\sum\limits_{{\text{{\sc aoi}s}}}\left |
+    \frac{\text{Time}_{\text{Human}}^{\text{\sc
+aoi}}}{\text{Area}_{\text{Human}}^{\text{\sc aoi}}} -
+\frac{\text{Time}_{\text{Robot}}^{\text{\sc
+aoi}}}{\text{Area}_{\text{Robot}}^{\text{\sc aoi}}} \right |}{N}
+\]
+}
+
+\emph{Time} and \emph{Area} are normalized, respectively for the total
+video length and the total area of the AOIs.
 
@@
     \centering
-    \includegraphics[width=10cm]{ManipulationCheck}
+    \includegraphics[width=7cm]{ManipulationCheck}
     \caption{Average ratings for the manipulation check question}
@@
     \includegraphics[width=3.3in]{H2}\label{GazeDifference-vs-ICA}
-    \caption{Difference in gaze patterns \vs \anti}
+    \caption{Difference in gaze patterns $\delta_{\mathcal{H},
+    \mathcal{R}}^{\text{gaze}}$ \vs \anti}
     \label{h2}

### 2015-07-03 main.tex
Completely removed H1 which does not bring much to the paper

@@
 
-Several hypotheses ensued, our baseline hypothesis \h{0} being that \emph{shallow
+We actually build several hypotheses: our baseline hypothesis \h{1} being that \emph{shallow
 cognitive contexts} and \emph{deep cognitive contexts} are recognized
@@
 \emph{human-like} (higher level of anthropomorphic attributions).
-
-Our first hypothesis \h{1} is that gaze behaviour alone is sufficient to
-know if a subject is looking at a robot or at a human.  More precisely, we
-hypothesize that the distribution of gaze fixations on the different body parts
-is significantly different when watching a robot or a human performing the same
-task.
 
@@
 manipulation check ($F[1,54] = 29.0, p < .001$) which validates our manipulation
-and supports \h{0}: the participants that were shown the \emph{shallow cognitive
+and supports \h{1}: the participants that were shown the \emph{shallow cognitive
 context} videos identified the task as more robot-like and participants watching
 \emph{deep cognitive context} videos perceived the tasks as more human-like.
-
-\subsection{Gaze differences between human and robot conditions}
-
-We grouped the 8 areas of interest located on the agent into 4 categories : {\sf
-head}, {\sf arms} (containing both arms and hands), {\sf torso}, {\sf legs}
-(including both legs). Running an ANOVA against gaze fixations on the areas of
-interest and the robot \vs human conditions, we obtain the following results:
-
-{\sf head}: the fixations on the head for the human video
-were observed to more than that for the robot video ($F[1,54] = 12.7, p < .001$)
-
-{\sf arms}: the fixations on the arms for the $\mathcal{H}$ video
-were also greater than that for the robot video ($F[1,54] = 16.5, p < .01$)
-
-{\sf legs}: the fixations on the legs were much lower
-for the human video as compared to the robot video ($F[1,54] = 1.9, p < .1$)
-
-{\sf torso}: the fixations on the torso were higher for the
-human video than for the robot video ($F[1,54] = 2.65, p < .1$)
-
-In summary, and over the duration of these shorts videos, the gaze behaviours
-were significantly different between the robot and human conditions, supporting
-\h{1}.
 
@@
 context was indeed associated to a robot-like situation, while a deeper
-cognitive context was associated to a human-like situation (\h{0}).
-
-The hypothesis \h{1} postulated that the gaze behaviours alone could tell if the
-subjects was observing a robot or a human. Indeed, our results show
-significantly different (normalized) fixations: the gaze distribution of a human
-observer are different for humans and robots.
+cognitive context was associated to a human-like situation (\h{1}).
 

### 2015-07-03 main.tex
Proof-reading pass

@@
 \usepackage{tikz}
-\usetikzlibrary{calc,decorations.pathreplacing}
+\usetikzlibrary{shapes,positioning,calc,decorations.pathreplacing}
 \newcommand{\tikzmark}[1]{\tikz[overlay,remember picture] \node (#1) {};}
@@
 that human users build with artificial agents such as
-robots~\citep{lemaignan2014dynamics}. Therefore we propose therefore that
-anthropomorphism can be a useful \emph{proxy} to these intricate psychological
-bonds. This article aims at improving our understanding of this phenomenon
-\textbf{by evidencing the impact of the cognitive presuppositions implied by the
-context of the interaction}.
+robots~\citep{lemaignan2014dynamics}. Therefore anthropomorphism appears to be a
+useful \emph{proxy} to study these intricate psychological
+bonds. Going in that direction, this article introduces \textbf{new ways to assess
+anthropomorphic attributions} and provides in particular \textbf{new insights on
+the impact of the cognitive context of the interaction on anthropomorphic
+attributions}.
 
-The study of context in HRI is not new. \textit{Context of use} is defined by
-the ISO as \textit{``users, tasks, equipment (hardware, software and materials),
-and the physical and social environments in which a product is used''}.
-Accordingly, there are various aspects that can impact how a robot is
-experienced. The real or imagined \textit{purpose} of a robot, including the
-application context in which it is typically used (\eg office environment, home,
-rehabilitation center, public space, \etc) as well as the task context (\eg
-serious or playful task; composition of human-robot team; number of users) and
-the (social) role in which the robot is used / experienced are taken into
-account. Generally, when the context of use of a robot is social, entertaining
-or playful, it will enhance anthropomorphism compared to when the context is a
-routine or focused serious task (security, rescue, \etc).
-\citet{joosse_what_2013} showed, for instance, that when the same robot ({\sc
-nao}) was used in a different task context (cleaning task \vs tour guide), users
-ascribed different personalities to the robot. \citet{goetz_cooperation_2002}
-revealed a link between a robot's context of use and people's perception of the
-robot: the authors found that people prefer a serious robot for serious tasks
-and a less serious robot for more playful tasks. \citet{kaplan_free_2000}
-discussed the role of uselessness in the design of robots. The author argues
-that artificial pets like AIBO have no real purpose, in a sense that they do not
-provide any kind of service or, in other words, \textit{``they are not doing
-what you tell them to do''} and \textit{``they might refuse the order of its
-owner''}. It may be this very aspect that increases people's tendency to
-anthropomorphize the robot. According to Kaplan, it is in our daily use language
-that we tend to attribute intentions to devices that are not doing their job
-well.
+\subsection{Role of context in human-robot interaction}
+
+The study of context in human-robot interaction (HRI) is not new.
+\textit{Context of use} is defined by the ISO as \textit{``users, tasks,
+equipment (hardware, software and materials), and the physical and social
+environments in which a product is used''}.  Accordingly, there are various
+aspects that can impact how a robot is experienced. The real or imagined
+\textit{purpose} of a robot, including the application context in which it is
+typically used (\eg office environment, home, rehabilitation center, public
+space, \etc) as well as the task context (\eg serious or playful task;
+composition of human-robot team; number of users) and the (social) role in which
+the robot is used / experienced are to be taken into account.
+
+Notably, when the context of use of a robot is social, entertaining or playful,
+it will enhance anthropomorphism compared to when the context is a routine or
+focused serious task (security, rescue, \etc).  \citet{joosse_what_2013} showed,
+for instance, that when the same robot ({\sc nao}) was used in a different task
+context (cleaning task \vs tour guide), users ascribed different personalities
+to the robot. \citet{goetz_cooperation_2002} revealed a link between a robot's
+context of use and people's perception of the robot: the authors found that
+people prefer a serious robot for serious tasks and a less serious robot for
+more playful tasks. \citet{kaplan_free_2000} discussed the role of uselessness
+in the design of robots. The author argues that artificial pets like AIBO have
+no real purpose, in a sense that they do not provide any kind of service or, in
+other words, \textit{``they are not doing what you tell them to do''} and
+\textit{``they might refuse the order of its owner''}. It may be this very
+aspect that increases people's tendency to anthropomorphize the robot. According
+to Kaplan, it is in our daily use language that we tend to attribute intentions
+to devices that are not doing their job well.
 
@@
 instance that subjects interacting with technologies in ways close to how they
-would behave towards people, would deny any human-like interaction in a post-hoc
+would behave towards people, would still deny any human-like interaction in a post-hoc
 questionnaire, illustrating this reflective perspective.
@@
 
-\subsection*{Hypotheses}
+\subsection{Hypotheses}
 
@@
 ascribe cognitive capabilities to an agent, the more we focus on its head when
-interacting with it}.  Eye-tracking was a natural methodology to investigate
-this intuition, and we crafted audio-visual stimuli that would elicit different
+interacting with it}. Eye-tracking would be a natural methodology to investigate
+this intuition, and we would then design audio-visual stimuli that would elicit different
 levels of cognitive ascription onto the robot while being identical in every
@@
 
-We actually build several hypotheses: our baseline hypothesis \h{1} being that \emph{shallow
-cognitive contexts} and \emph{deep cognitive contexts} are recognized
-(manipulation check) and interpreted by the participants as being respectively
-\emph{machine-like} (low level of anthropomorphic attributions) or
+We actually build several hypotheses: our baseline hypothesis \h{1} is that we
+can actually create such stimuli that induce recognisable \emph{shallow
+cognitive contexts} and \emph{deep cognitive contexts} (manipulation check); and
+further that these contexts are interpreted by the participants as being
+respectively \emph{machine-like} (low level of anthropomorphic attributions) or
 \emph{human-like} (higher level of anthropomorphic attributions).
@@
 will tend to have smaller differences in their gaze behaviours while watching
-either a robot or a human performing the same task.
+either a robot or a human performing the same task: if this can be observed, it
+would also show that anthropomorphic attributions are related to gaze patterns.
 
-Then, we hypothesize (\h{3}) that the gaze fixations on the head are significantly
-different depending on the cognitive context, and that a deeper cognitive
-context corresponds to longer gaze fixations on the head. This would in turn
-interpreted at \emph{gaze fixations on the head is a proxy for an higher
-level of human-likeness attribution}, the core hypothesis of this article.
+Then, we hypothesize (\h{3}) that the gaze fixations on the head are
+significantly different depending on the cognitive context, and that a deeper
+cognitive context corresponds to longer gaze fixations on the head. This would
+in turn interpreted at \emph{gaze fixations on the head is a proxy for the level
+of human-likeness attribution}, and constitutes the core hypothesis of this
+article.
 
 Finally, the hypothesis \h{4} examines whether the cognitive context affects the
-general tendency to anthropomorphize, \ie whether observing a
+general tendency to anthropomorphize, \ie whether observing \emph{one}
 robot acting in an \emph{human-like} context leads to an increased level of
-anthropomorphic attributions to robots (and vice versa). This also provides us
+anthropomorphic attributions to robots \emph{in general}. This also provides us
 with a way to triangulate the behavioural measures with the subjective
-attribution of anthropomorphism.
+attribution of anthropomorphism: if such an effect is evidences, we can also
+conclude that the cognitive context impacts the attribution of human-likeness,
+and this, in turns, supports the hypothesis \h{3} that head fixations would
+reflect not only the cognitive context but also the level of anthropomorphic
+attributions.
+
+Figure~\ref{hyps} illustrate how these four hypotheses relate to \emph{a)}
+cognitive context, \emph{b)} anthropomorphic attributions, and \emph{c)} gaze
+patterns.
+
+\begin{figure}[ht]
+\centering
+
+\resizebox{0.5\linewidth}{!}{%
+
+\begin{tikzpicture}[
+    >=latex,
+    every edge/.style={->,draw, very thick},
+    every node/.style={draw, circle, text centered, text width=2.7cm}]
+
+    \node at (0,0) (ctxt) {Cognitive context};
+    \node at (-3,-3) (anthro) {Anthropomorphic attributions};
+    \node at (3,-3)[circle split, text width=2.5cm] (gaze) {\textit{\small Fixations \\on head} \nodepart{lower} \textit{\small Gaze
+distribution \\differences}};
+    \node [draw=none,anchor=east,left=-0.5cm of gaze.west] (gazecap) {\large Gaze:};
+
+    \path[every node/.style={draw=none}]
+            (ctxt) edge [bend right] node[left] {\h{1}, \h{4}} (anthro)
+            (ctxt) edge [bend left] node[right] {\h{3}} (gaze.north)
+            (anthro) edge [bend right] node[above] {\h{2}} (gaze.south);
+\end{tikzpicture}
+}
+
+\caption{Hypotheses of interactions between the three main concepts studied in
+the article. Arrows mean ``A impacts B''.}
+
+    \label{hyps}
+\end{figure}
 
@@
 socio-cognitive contexts.  These contexts, created by priming and/or audio cues,
-are designed to elicit either a shallow cognitive context (that participant
-would refer as a \emph{machine-like situation}) or a deeper cognitive context
-(refered as a \emph{human-like situation}).
+are designed to elicit either a shallow cognitive context (that participants
+would \textit{a posteriori} rate as a \emph{machine-like situation}) or a deeper
+cognitive context (rated as a \emph{human-like situation}).
 
 Besides eye-tracking, the participants' perception of robots is assessed through a
-pre- and a post-questionnaire interaction, described below.
+pre- and a post-questionnaire, described below.
 
@@
 cognitive context} \vs \emph{deep cognitive context}) and the nature of the
-agent appearing in the stimulus (a \emph{robot}, eliciting a \emph{human-robot} interaction
-situation, or a \emph{human}, eliciting a \emph{human-human} interaction
+agent appearing in the stimulus (a robot, eliciting a \emph{human-robot} interaction
+situation, or a human, eliciting a \emph{human-human} interaction
 situation).
 
-\begin{table}
+\begin{table}[ht!]
+    \vspace{2em}
     \centering
@@
 The human actor was instructed to follow as closely as possible the actions and
-attitudes of the robot (left/right glances, hesitations\ldots), while keeping a
+attitudes of the robot (left/right glances, hesitations, gestures), while keeping a
 natural, \emph{human-like} general behaviour.  Hence, the length of human videos
@@
 questionnaire comprised of questions assessing their familiarity with robots, 10
-items from \emph{Big-Five} personality questionnaire, 15 questions taken from
+items from the \emph{Big-Five} personality questionnaire, 15 questions taken from
 Godspeed questionnaire (questions related to \emph{anthropomorphism},
@@
 human-likeness (from~\cite{ruijten_introducing_2014})\footnote{The
-the pre- and post-questionnaires are available online:
+pre- and post-questionnaires are available online:
 \url{https://github.com/chili-epfl/anthropomorphism-eyetracking}.}. The pre-questionnaire
@@
 The post-questionnaire was administered at the end of the experiment, and was
-close to the pre-questionnaire: the personality questions were omitted, and a
+identical to the pre-questionnaire, except that the personality questions were omitted and a
 manipulation check question was added (\emph{``In your opinion, the tasks that
-you watched were more: A robot kind of task ... A human kind of task''}).
+you watched were more: A robot kind of task ... A human kind of task''}, on a 5
+points scale).
 This questionnaire typically took 3 to 4 minutes to fill. The resulting score is
@@
 
-The difference \deltaant measured for each participant between the pre-
-and post-questionnaires forms the dependent variable of our experiment. It
-reflects the impact of the video stimuli on the anthropomorphic perception that
-they have of robots \emph{in general}: the Godspeed questions used in the
-questionnaires are not specific to the Nao robot used in this particular
-experiment, and indeed assess how humans perceive robots in a broad sense.
+\anti, \antf and the difference \deltaant measured for each participant between
+the pre- and post-questionnaires form the dependent variables of our experiment.
+\deltaant, in particular, reflects the impact of the video stimuli on the
+anthropomorphic perception that they have of robots \emph{in general}: the
+Godspeed questions used in the questionnaires are not specific to the Nao robot
+used in this particular experiment, and indeed assess how humans perceive robots
+in a broad sense.
 
@@
 
-\begin{figure}[ht!]
+\begin{figure}[ht]
 \centering
-    \includegraphics[width=0.3\linewidth]{experimentFlow}
+
+\begin{tikzpicture}[
+    >=latex,
+    every edge/.style={<-,draw, very thick},
+    every node/.style={draw, text centered, text width=5cm}]
+
+    \node (n1) at (0,0) {Consent form};
+    \node (n2) [below=of n1] {Familiarization}
+        edge (n1);
+    \node (n3) [below=of n2] {Pre-questionnaire}
+        edge (n2);
+    \node (n4) [below=of n3] {Videos}
+        edge (n3);
+    \node (n5) [below=of n4] {Post-questionnaire}
+        edge (n4);
+
+\end{tikzpicture}
     \caption{Overview of the course of the study}
@@
 
-\paragraph{Pre-questionnaire and familiarization}
+\paragraph{Familiarization and pre-questionnaire}
 
@@
 consent form. Participants were then asked to fill the 49 questions of
-the pre-questionnaire, with a 10 minutes time limit that none of the participants
-reached.
+the pre-questionnaire, with a 10 minutes time limit (that none of the participants
+reached).
 
@@
 the time, and participants played between 2 and 3 minutes with the robot).
-
 The purpose of this pre-interaction was to get the participants acquainted with the
@@
 
-\paragraph{Areas of interest}
-
 As seen in figure~\ref{fig:aoi}, we defined 10 areas of interest (AOIs): one on
@@
 
-We recorded the fixations on one of these 10 zones and normalized by different total video duration and surface of AOIs between the robot and human conditions.
-We finally analyzed their distribution, producing what we
-call \emph{gaze patterns}. The difference in the gaze patterns over ``N'' AOis can be calculated as follows:\\
+We recorded the fixations on each of these 10 zones and normalized by different
+total video duration and surface of AOIs between the robot and human conditions.
+We finally analyzed their distribution, producing what we call \emph{gaze
+patterns}.
 
-\paragraph{Differences between gaze behaviours}
-
-To compare gazing behaviours across conditions, we compute a \emph{difference in
-gaze patterns} over the $N(=10)$ AOIs:
+To compare gazing behaviours across the robot and human conditions, we then
+computed a \emph{difference in gaze patterns} over the $N(=10)$ AOIs:
 
@@
 
-Based on the experiments conducted on 55 participants in the human
-($\mathcal{H}$) and robot ($\mathcal{R}$) interactions across \emph{shallow} and
-\emph{deep cognitive context} conditions, we have the following
-results.\footnote{The
-detailed statistics and code used for obtaining the results are available here :
+Based on the experiments conducted on 56 participants in the human and robot
+interactions across \emph{shallow} and \emph{deep cognitive context} conditions,
+we have the following results.\footnote{The detailed statistics and code used
+    for obtaining the results are available here :
 \url{https://github.com/chili-epfl/anthropomorphism-eyetracking}.}
@@
 While testing for all the 4 hypotheses, we observed no significant bias with
-respect to age, gender, EPFL status, familiarity with robot and robot ownership
-of the participants, \ie there was no correlation found between these factors
-and the gaze patterns in the videos.
+respect to age, gender, familiarity with robot and robot ownership
+of the participants, \ie there was no effects to be found between these factors
+and the other variables of the experiment.
 
@@
 
-We got a significant correlation between $\delta_{\mathcal{H},\mathcal{R}}$ and
-the \anti. As can be seen in figure~\ref{h2}, there is a significant negative
+We found a significant correlation between
+$\delta_{\mathcal{H},\mathcal{R}}^{\text{gaze}}$ and
+the \anti. As seen in figure~\ref{h2}, there is a significant negative
 correlation between the two quantities (Pearson Correlation Coefficient = -0.43,
-$p < .001$).
+$p < .001$). The higher the (initial) tendency to anthropomorphize, the smaller
+the difference in gazing behaviours between the robot and human conditions. This
+supports hypothesis \h{2}.
 
@@
     \centering
-    \includegraphics[width=3.3in]{H2}\label{GazeDifference-vs-ICA}
+    \includegraphics[width=0.5\columnwidth]{H2}\label{GazeDifference-vs-ICA}
     \caption{Difference in gaze patterns $\delta_{\mathcal{H},
@@
 
-We analysed these possible correlations for robot condition only: the human case is
-inherently a source of deep cognitive context, hiding the effects of our
-manipulation on a shallow \vs deep cognitive context.
-
 Based on ANOVA results, taking the 5 groups of AOIs {\sf head}, {\sf arms}, {\sf
-hands}, {\sf torso}, {\sf legs} for the robot in both the shallow and deep
+hands}, {\sf torso} and {\sf legs} for the robot in both the shallow and deep
 cognitive context conditions, the fixations on the head in the deep condition
@@
 shallow and deep conditions were almost the same. Figure~\ref{h3} shows the
-distribution of proportion of time spent gazing on the 5 AOIs for the two
+distribution of proportion of time spent gazing on the 5 AOI groups for the two
 conditions.
 
-\begin{figure}
+\begin{figure}[ht!]
     \centering
-    \includegraphics[width=3.3in]{GazeHighLow}\label{GazeHighLow}
+    \includegraphics[width=0.6\columnwidth]{GazeHighLow}\label{GazeHighLow}
     \caption{Gaze fixations on the different areas on interest, for shallow \vs
@@
 context for the same interaction suffices to lead to significantly longer
-fixations on the agent's head.
+fixations on the agent's head (hypothesis \h{3}).
+
+Note that we only analysed these possible correlations for robot condition: in
+the human condition, the presence of the human is intrinsically a source of deep
+cognitive context, hiding the effects of our manipulation on a shallow \vs deep
+cognitive context.
 
@@
 
-Running an ANOVA against the evolution of anthropomorphic attributions
-(\deltaant) over the duration of the experiment, in the two cognitive
+Running an ANOVA against the change of anthropomorphic attributions
+(\deltaant) over the duration of the experiment in the two cognitive
 conditions, shows that \deltaant is greater for tasks with a deeper cognitive
@@
 a significantly higher tendency to anthropomorphize robots \emph{in general} (as
-the questionnaires on anthropomorphic attributions explicitely refered to
+the questionnaire on anthropomorphic attributions explicitly referred to
 \emph{robots in general}).
@@
 
-The clearly significant correlation between deep \vs shallow conditions and the
+The significant correlation between deep \vs shallow conditions and the
 answers to the question \emph{Were the task more robot-like or human-like?}
-proves that our manipulation was successful, and that a shallow cognitive
+shows that our manipulation was successful, and that a shallow cognitive
 context was indeed associated to a robot-like situation, while a deeper
-cognitive context was associated to a human-like situation (\h{1}).
+cognitive context was associated to a human-like situation (\h{1}). This is
+already an interesting result: subtle changes in the cognitive contexts are
+recognized and clearly interpreted in terms of human-likeness.
 
-Hypothesis \h{2} looked at a possible interaction between our potential to
+Hypothesis \h{2} looked at a possible interaction between our tendency to
 anthropomorphize (as measured in the pre-questionnaire) and our actual gaze
@@
 this hypothesis: participants reporting an higher tendency to anthropomorphize
-tend to have similar gazing behaviours whether they look at humans or at robots.
-
-To rephrase it: statistically speaking, your tendency to anthropomorphize things
-is reflected in the way you look at these things: you will also look at them
-\emph{as if they were humans}.
+tend to have closer gazing behaviours when they look at humans or at robots:
+statistically speaking, the tendency to anthropomorphize robots
+is reflected in the way one looks at them: you look at them
+like you would look at humans.
 
@@
 head fixations could act as a \emph{proxy to anthropomorphic projections}: as
-underlined in the previous section, our data also support this second
-hypothesis.
+underlined in the previous section, our data also support this.
 
@@
 The study and results presented in this article lead to two main contributions:
-new insights on the impact of the cognitive context of the interaction on the
-perception of a robot by humans; a novel unbiased methodology based on
-eye-tracking to measure anthropomorphic attributions during a running
-human-robot interaction.
+new insights on the impact of the cognitive context on the perception of a robot
+by humans; a novel unbiased methodology based on eye-tracking to assess
+anthropomorphic attributions during a running human-robot interaction.
 
@@
 human-like characteristics to robot by exploring the role of the interaction
-context. As we show in the article, it appears that \textbf{even relatively
+context. As we show, it appears that \textbf{even relatively
 subtle context priming may lead to significantly different anthropomorphic
@@
 confirmed both by distinct gaze patterns, and different reported perceptions in
-questionnaires. To the best of our knowledge, this effect had not been previously
-evidenced.
+questionnaires.
 
@@
 cognitive context, the tendency to attribute human-like characteristics to robot
-\textbf{evolves} in significantly different ways: after observing a robot in a
-context that pre-suppose deeper cognitive capabilities, \textbf{people increase
+\textbf{evolves} in significantly different ways. \textbf{After observing a robot in a
+context that pre-suppose deeper cognitive capabilities, people increase
 their general tendency to anthropomorphize robots} compared to a shallow
@@
 nature of the task (participants had to watch body movements) defeated our
-gaze-based investigation method: the subjects expectedly paid attention to the
-whole body of the robot or human (even distribution of the gazes on the body),
-thus making specific gaze patterns on the head difficult to evidence.
+gaze-based investigation method: the subjects expectedly paid attention to each
+and every part of the body of the robot or human (even distribution of the gazes
+on the body), thus making specific gaze patterns on the head difficult to
+evidence.
 
@@
 
-%\subsection{Context and Interaction Design}
-%
-%\fxwarning{discuss here how context can be used to shape the interaction}
-%
-%
-%Anthropomorphism as a proxy for cognitive/affective bonds that are esthablishing
-%between humans and robots.
-%
-%\fxnote{discuss extensions towards mobile eyetrackers}
-%
+\section*{Acknowledgments}
+
+We would like here to acknowledge the contribution of Julia Fink to a better
+understanding of anthropomorphism as a psychological phenomenon.
+
 \bibliographystyle{apacite}

### 2015-07-08 main.tex
Implemented Pierre's comments

@@
 
-We take here a different approach to measure anthropomorphism, based on
+We explore here a different approach to measure anthropomorphism, based on
 eye-tracking.  By looking at the eyes fixation on the head of the robot, we have
@@
 ascribe cognitive capabilities to an agent, the more we focus on its head when
-interacting with it}. Eye-tracking would be a natural methodology to investigate
-this intuition, and we would then design audio-visual stimuli that would elicit different
+interacting with it}. Eye-tracking is a natural methodology to investigate
+this intuition. We hence design audio-visual stimuli that elicit different
 levels of cognitive ascription onto the robot while being identical in every
@@
 with a way to triangulate the behavioural measures with the subjective
-attribution of anthropomorphism: if such an effect is evidences, we can also
-conclude that the cognitive context impacts the attribution of human-likeness,
+attribution of anthropomorphism: if such an effect is found, we can also
+conclude that the cognitive context impacts on the attribution of human-likeness,
 and this, in turns, supports the hypothesis \h{3} that head fixations would
@@
         cognitive context} \vs \emph{deep cognitive context} is between subject.
-        Two stimuli (\emph{Picking} task, {\bf A}, and \emph{Sound} task,
+        Two stimuli (\emph{Picking} task, {\bf A}, and \emph{Pointing} task,
         {\bf B}) were shown to the participants, introduced by brief verbal
@@
 \emph{Picking} task, and pointing towards a source of sound, refered as the
-\emph{Sound} task) acted either by a human or a robot. Video stimuli were
+\emph{Pointing} task) acted either by a human or a robot. Video stimuli were
 realised in studio conditions. All videos followed the same simple structure: an
@@
 attitudes of the robot (left/right glances, hesitations, gestures), while keeping a
-natural, \emph{human-like} general behaviour.  Hence, the length of human videos
+natural, \emph{human-like} general behaviour. As a result, the length of human videos
 (57 seconds in total for the two tasks) was shorter than robot videos (110
@@
 (\emph{machine-like} \vs \emph{human-like}). We reinforced this effect in the
-\emph{Sound} task: not only the verbal priming but also the sound played by the
+\emph{Pointing} task: not only the verbal priming but also the sound played by the
 speakers during the task was altered: either a repetitive bip (\emph{shallow
@@
 
-    \subfigure[\emph{Sound} task, robot condition]{
+    \subfigure[\emph{Pointing} task, robot condition]{
         \includegraphics[height=5cm]{stimulus-robot-noise}
     }
-    \subfigure[\emph{Sound} task, human condition]{
+    \subfigure[\emph{Pointing} task, human condition]{
         \includegraphics[height=5cm]{stimulus-human-noise-anon}
@@
     {\includegraphics[height=5cm]{aoi-robot}\label{fig:aoi-toys}}
-    \subfigure[\emph{Sound} task, human condition]
+    \subfigure[\emph{Pointing} task, human condition]
     {\includegraphics[height=5cm]{aoi-human}\label{fig:aoi-noise}}
@@
 
-Based on ANOVA results, taking the 5 groups of AOIs {\sf head}, {\sf arms}, {\sf
-hands}, {\sf torso} and {\sf legs} for the robot in both the shallow and deep
+We consider the 5 groups of AOIs {\sf head}, {\sf arms}, {\sf hands}, {\sf
+torso} and {\sf legs} (the left and right arms, hands and legs are grouped
+together). Based on ANOVA results for the robot in both the shallow and deep
 cognitive context conditions, the fixations on the head in the deep condition
@@
 human-like characteristics to robot by exploring the role of the interaction
-context. As we show, it appears that \textbf{even relatively
-subtle context priming may lead to significantly different anthropomorphic
-perceptions of the exact same robot, performing the exact same task}, as
-confirmed both by distinct gaze patterns, and different reported perceptions in
-questionnaires.
+context. As we show, it appears that \textbf{even relatively subtle context
+priming may lead to significantly different anthropomorphic perceptions of
+the exact same robot, performing the exact same task}, as confirmed both by
+distinct gaze patterns, and different reported perceptions in questionnaires.
+Interestingly, this effects can already be evidenced after \textbf{very short,
+one-way, interactions} (less than 2 minutes).
 
@@
 We initially prepared three different stimuli: the \emph{Picking} task, the
-\emph{Sound} task and a \emph{Dance} task.  During the \emph{Dance} task, the
+\emph{Pointing} task and a \emph{Dance} task.  During the \emph{Dance} task, the
 agent was either asked to \emph{``Show some movements''} (\emph{shallow
@@
 (\emph{deeper cognitive context} condition). While all the participants were
-shown this stimuli as well, we decided to exclude it from the results as the
-nature of the task (participants had to watch body movements) defeated our
-gaze-based investigation method: the subjects expectedly paid attention to each
-and every part of the body of the robot or human (even distribution of the gazes
-on the body), thus making specific gaze patterns on the head difficult to
-evidence.
+shown this stimuli as well, we decided to exclude it from the results as we
+found out that the nature of the task (participants had to watch body movements)
+introduced an experimental bias: because dance is a form of whole-body
+expression, gazes where evenly distributed on the body of the agents, masking
+possible cognition-related gaze patterns.
 
@@
 We would like here to acknowledge the contribution of Julia Fink to a better
-understanding of anthropomorphism as a psychological phenomenon.
+understanding of anthropomorphism as a psychological phenomenon. We also thank
+all the students for their participation.
+
+This research was supported by the Swiss National Science Foundation through the
+National Centre of Competence in Research Robotics.
 

### 2015-07-08 cover.tex
Added JHRI cover page

\documentclass{article}

\usepackage[utf8]{inputenc}

\begin{document}

\section{Authors List}

\begin{itemize}
    \item Séverin Lemaignan, CHILI Lab, École Polytechnique Fédérale de
    Lausanne, \texttt{severin.lemaignan@epfl.ch} 
    \item Kshitij Sharma, CHILI Lab, École Polytechnique Fédérale de Lausanne,
    \texttt{kshitij.sharma@epfl.ch}
    \item Ashish Ranjan Jha, CHILI Lab, École Polytechnique Fédérale de
    Lausanne, \texttt{ashish.jha@epfl.ch}
    \item Pierre Dillenbourg, CHILI Lab, École Polytechnique Fédérale de
    Lausanne, \texttt{pierre.dillenbourg@epfl.ch}
\end{itemize}

\section{Title}

\begin{center}
{\sc Cognitive Context: Impact on the Perception of a Robot}
\end{center}

\section{Contribution type}

Research article

\section{Keywords}

human-robot interaction, anthropomorphism, cognitive context, eye-tracking, gaze patterns

\section{Relationship with prior papers}

\begin{itemize}
\item Lemaignan, S., Fink, J., \& Dillenbourg, P. (2014). The dynamics of
anthropomorphism in robotics. In \emph{Proceedings of the 2014 human-robot
interaction conference}: this paper discusses the dynamics of anthropomorphic
attributions, in a completely different setting and with a completely
different methodology than the one used in the present publication.
\item Fink, J. (2012). Anthropomorphism and human likeness in the design of
robots and human-robot interaction. In \emph{S. S. Ge, O. Khatib, J.-J.
Cabibihan, R. Simmons, \& M.-A. Williams (Eds.), Social robotics}: this paper
introduce theoretical background on the concept of anthropomorphism which is
re-used in the introduction of the present publication.
\end{itemize}

\section{Implication of authors}

\begin{itemize}
\item Séverin Lemaignan: experiment design
\item Kshitij Sharma: data analysis
\item Ashish Jha: data collection
\item Pierre Dillenbourg: project supervision
\end{itemize}

\section{JHRI Sections}

\textbf{Preferred section}: \emph{Behavioral and Social Science}

\textbf{Possible Editors}: Vanessa Evers, Wendy Ju

\section{Presentation at HRI}

We will gladly present this work during a future HRI Conference.

\end{document}

### 2015-07-08 main.tex
Minor fixes
Added a note on gaze distributions over the duration of the robot video stimuli

@@
 seconds) due to the robot being usually slower in performing actions (in
-particular walks) compared to human.
+particular walks) compared to human.\footnote{To make sure the difference of
+video lenght does not bias gaze distributions, we ran a $\chi^2$ test between
+the gaze distributions of the first half and the second half of the robot
+videos: no significant difference was found ($\chi^2[DF=4]=.0066, p=1$).}
 
@@
     \subfigure[\emph{Picking} task, human condition]{
-        \includegraphics[height=5cm]{stimulus-human-toys-anon}
+        \includegraphics[height=5cm]{stimulus-human-toys}
     }
@@
     \subfigure[\emph{Pointing} task, human condition]{
-        \includegraphics[height=5cm]{stimulus-human-noise-anon}
+        \includegraphics[height=5cm]{stimulus-human-noise}
     }

### 2015-10-29 main.tex
Removed emphasises with bold face

@@
 useful \emph{proxy} to study these intricate psychological
-bonds. Going in that direction, this article introduces \textbf{new ways to assess
-anthropomorphic attributions} and provides in particular \textbf{new insights on
+bonds. Going in that direction, this article introduces new ways to assess
+anthropomorphic attributions and provides in particular new insights on
 the impact of the cognitive context of the interaction on anthropomorphic
-attributions}.
+attributions.
 
@@
 After the pre-questionnaire, we invited the participants to an initial
-free interaction with a \textbf{powered-off} Nao robot (we did not constraint
+free interaction with a powered-off Nao robot (we did not constraint
 the time, and participants played between 2 and 3 minutes with the robot).
@@
 human-like characteristics to robot by exploring the role of the interaction
-context. As we show, it appears that \textbf{even relatively subtle context
+context. As we show, it appears that even relatively subtle context
 priming may lead to significantly different anthropomorphic perceptions of
-the exact same robot, performing the exact same task}, as confirmed both by
+the exact same robot, performing the exact same task, as confirmed both by
 distinct gaze patterns, and different reported perceptions in questionnaires.
-Interestingly, this effects can already be evidenced after \textbf{very short,
-one-way, interactions} (less than 2 minutes).
+Interestingly, this effects can already be evidenced after very short,
+one-way, interactions (less than 2 minutes).
 
@@
 cognitive context, the tendency to attribute human-like characteristics to robot
-\textbf{evolves} in significantly different ways. \textbf{After observing a robot in a
+evolves in significantly different ways. After observing a robot in a
 context that pre-suppose deeper cognitive capabilities, people increase
-their general tendency to anthropomorphize robots} compared to a shallow
+their general tendency to anthropomorphize robots compared to a shallow
 cognitive context, even though the robot appearance and visual behaviour is the
@@
 The second contribution is a methodological one: we present in this article
-\textbf{a novel technique to assess anthropomorphic projections that relies on a
+a novel technique to assess anthropomorphic projections that relies on a
 biometric measurement (eye-tracking) to compare gaze fixation durations on
-the face of the robot}. We cross-validate this new metric with existing,
+the face of the robot. We cross-validate this new metric with existing,
 established, questionnaires. Compared to current techniques (post-hoc

### 2015-10-29 main.tex
Removed overview of experimental procedure
Do not mention the pilot study

@@
 
-Figure~\ref{course_of_study} gives an overview of the protocol, detailed
-hereafter.
-
-\begin{figure}[ht]
-\centering
-
-\begin{tikzpicture}[
-    >=latex,
-    every edge/.style={<-,draw, very thick},
-    every node/.style={draw, text centered, text width=5cm}]
-
-    \node (n1) at (0,0) {Consent form};
-    \node (n2) [below=of n1] {Familiarization}
-        edge (n1);
-    \node (n3) [below=of n2] {Pre-questionnaire}
-        edge (n2);
-    \node (n4) [below=of n3] {Videos}
-        edge (n3);
-    \node (n5) [below=of n4] {Post-questionnaire}
-        edge (n4);
-
-\end{tikzpicture}
-    \caption{Overview of the course of the study}
-    \label{course_of_study}
-\end{figure}
+%Figure~\ref{course_of_study} gives an overview of the protocol, detailed
+%hereafter.
+%
+%\begin{figure}[ht]
+%\centering
+%
+%\begin{tikzpicture}[
+%    >=latex,
+%    every edge/.style={<-,draw, very thick},
+%    every node/.style={draw, text centered, text width=5cm}]
+%
+%    \node (n1) at (0,0) {Consent form};
+%    \node (n2) [below=of n1] {Familiarization}
+%        edge (n1);
+%    \node (n3) [below=of n2] {Pre-questionnaire}
+%        edge (n2);
+%    \node (n4) [below=of n3] {Videos}
+%        edge (n3);
+%    \node (n5) [below=of n4] {Post-questionnaire}
+%        edge (n4);
+%
+%\end{tikzpicture}
+%    \caption{Overview of the course of the study}
+%    \label{course_of_study}
+%\end{figure}
 \paragraph{Participants}
 
-We ran first a pilot study with 10 participants, followed by an experiment with
-56 subjects (mean age: 20.9, $SD=3.9$, 31 females and 25 males).
-The participants were recruited amongst students of our university. To avoid
-students with a high familiarity with robots and artificial intelligent systems,
-Computer Science and Electronics curriculum were excluded. This was \textit{a
-posteriori} comforted by the questionnaire responses: no participants
+We ran the experiment with 56 subjects (mean age: 20.9, $SD=3.9$, 31 females and
+25 males).  The participants were recruited amongst students of our university.
+To avoid students with a high familiarity with robots and artificial intelligent
+systems, Computer Science and Electronics curriculum were excluded. This was
+\textit{a posteriori} comforted by the questionnaire responses: no participants
 reported itself as being very familiar with robots, 8 reported some familiarity

### 2015-10-29 main.tex
Do not mention participants came only once

@@
 
-The study lasted about 15 minutes per participant; each participant was invited
-for one session only.
-
 As stated previously, the study follows a 2$\times$2 design
-(table~\ref{table:design}): the \emph{deep} \vs {shallow cognitive context}
-condition was between-subject ( 30 subjects performed the \emph{deep cognitive}
+(table~\ref{table:design}): the \emph{deep} \vs \emph{shallow cognitive context}
+condition was between-subject (30 subjects performed the \emph{deep cognitive}
 tasks while 26 were in the \emph{shallow cognitive} condition); the \emph{robot}
 \vs \emph{human} condition was within-subject (the order of stimuli presentation
-was counter-balanced over the 56 participants).
+was counter-balanced over the 56 participants). The study lasted in average 15
+minutes per participant.
 

### 2015-10-29 main.tex
Clarify a little the procedure

@@
 
-\subsection{Course of the study}
-
 %Figure~\ref{course_of_study} gives an overview of the protocol, detailed
@@
 %\end{figure}
-\paragraph{Participants}
 
-We ran the experiment with 56 subjects (mean age: 20.9, $SD=3.9$, 31 females and
+\subsection{Participants}
+
+We ran the study with 56 subjects (mean age: 20.9, $SD=3.9$, 31 females and
 25 males).  The participants were recruited amongst students of our university.
@@
 
+\subsection{Procedure}
+
 \paragraph{Familiarization and pre-questionnaire}
 
-Before the experiment, participants were made to read, understand and sign a
+Before starting the experiment, participants were made to read, understand and sign a
 consent form. Participants were then asked to fill the 49 questions of
@@
 The purpose of this pre-interaction was to get the participants acquainted with the
-robot shape and kind of motions it could possibly perform, and therefore
-mitigate the (visual) novelty effect (so that they do not get surprised seeing
-a robot for the first time in the videos).
+robot appearance, shape and range of motions it could possibly perform, so as to
+mitigate the (visual) novelty of the robot that would lead to hard-to-measure gaze artifacts.
 
-\paragraph{Videos}
+\paragraph{Stimuli screening}
 
@@
 calibration procedure, and the participants' gaze was recorded while they
-watched the \emph{robot} and \emph{human} interaction videos.
+watched the \emph{robot} and \emph{human} interaction stimuli.
 
-\paragraph{Post-questionnaire}
+\paragraph{Post-questionnaire and conclusion}
 
-Finally, the participants were asked to fill the post-questionnaire.
-Before leaving, each participant was given a reward
-equivalent to EUR 10.
+Finally, the participants were asked to fill a post-questionnaire.
+
+Before leaving, possible questions on the purpose of the study were
+answered and each participant was given a reward equivalent to EUR 10.
 

### 2015-10-29 main.tex
APA: {subject->participant}

@@
 instead of an in-the-moment reaction: \citet{reeves_media_1996} showed for
-instance that subjects interacting with technologies in ways close to how they
+instance that participants interacting with technologies in ways close to how they
 would behave towards people, would still deny any human-like interaction in a post-hoc
@@
 metric is behavioural and hence does not suffer post-hoc reconstruction by the
-subjects, possibly providing a better, ``noise-less'', access to the human
+participants, possibly providing a better, ``noise-less'', access to the human
 attitude towards the machine, and, as such, a better proxy to the cognitive and
@@
         \emph{human} condition is within subject, while the \emph{shallow
-        cognitive context} \vs \emph{deep cognitive context} is between subject.
+        cognitive context} \vs \emph{deep cognitive context} is between subjects.
         Two stimuli (\emph{Picking} task, {\bf A}, and \emph{Pointing} task,
@@
 
-We ran the study with 56 subjects (mean age: 20.9, $SD=3.9$, 31 females and
+We ran the study with 56 participants (mean age: 20.9, $SD=3.9$, 31 females and
 25 males).  The participants were recruited amongst students of our university.
@@
 (table~\ref{table:design}): the \emph{deep} \vs \emph{shallow cognitive context}
-condition was between-subject (30 subjects performed the \emph{deep cognitive}
+condition was between-subjects (30 participants performed the \emph{deep cognitive}
 tasks while 26 were in the \emph{shallow cognitive} condition); the \emph{robot}
@@
 figure~\ref{h4}). In other words, after being exposed to short videos of a robot
-performing simple tasks, subjects primed with a deeper cognitive context report
+performing simple tasks, participants primed with a deeper cognitive context report
 a significantly higher tendency to anthropomorphize robots \emph{in general} (as
@@
 is less impacted by experimental biases (like the \emph{observer effect},
-where the subject's behaviour is impacted by the fact he/she knows that
+where the behaviour of the participant is impacted by the fact he/she knows that
 he/she is observed) and take place during the interaction itself
@@
 Besides, one may point that, in real-world experiments, the robot does not
-always remain in the field of view of the subject, and, at the very least, the
+always remain in the field of view of the participant, and, at the very least, the
 body of the robot may be partially occluded at time.  This is certainly true,
@@
 anthropomorphic perception, but rather a \emph{relative} measurement: within a
-group of subject, it enables to classify subjects in term of their level of
+group of participants, it enables to classify participants in term of their level of
 projected anthropomorphism onto the robot.  This means that, while this method
@@
 situations (\ie different experiments), it can be employed within a group a
-subjects taking part to the same experiment.
+participants taking part to the same experiment.
 

### 2015-10-29 main.tex
Fixed spacing after A0 and A1

@@
 typically took 5 minutes for participants to fill. The results were turned into
-a score noted \anti (\emph{initial tendency to anthropomorphize}) following a
+a score noted \anti{} (\emph{initial tendency to anthropomorphize}) following a
 method presented below (section~\ref{questionnaires_processing}).
@@
 This questionnaire typically took 3 to 4 minutes to fill. The resulting score is
-noted \antf (\emph{final tendency to anthropomorphism}).
+noted \antf{} (\emph{final tendency to anthropomorphism}).
 
-\anti, \antf and the difference \deltaant measured for each participant between
+\anti{}, \antf{} and the difference \deltaant measured for each participant between
 the pre- and post-questionnaires form the dependent variables of our experiment.
@@
 Questionnaires were coded and two values, the \emph{initial tendency to
-anthropomorphize} \anti and the \emph{final tendency to anthropomorphize} \antf
+anthropomorphize} \anti{} and the \emph{final tendency to anthropomorphize} \antf{}
 were computed, respectively from the pre- and post-questionnaires.
@@
 \emph{anthropomorphism} and \emph{likeability}. These ten questions were rated
-between -2 and 2, hence \anti and \antf vary between -20 and 20.  The other
-questions (including the Big-Five personality test) were not used for this
-study.
+between -2 and 2, hence \anti{} and \antf{} vary between -20 and 20. The other
+questions were not used for this study.
 
@@
 $\delta_{\mathcal{H},\mathcal{R}}^{\text{gaze}}$ and
-the \anti. As seen in figure~\ref{h2}, there is a significant negative
+the \anti{}. As seen in figure~\ref{h2}, there is a significant negative
 correlation between the two quantities (Pearson Correlation Coefficient = -0.43,
@@
     \caption{Difference in gaze patterns $\delta_{\mathcal{H},
-    \mathcal{R}}^{\text{gaze}}$ \vs \anti}
+    \mathcal{R}}^{\text{gaze}}$ \vs \anti{}}
     \label{h2}
@@
     \includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}
-    \caption{Difference between \anti and \antf in the shallow and deep
+    \caption{Difference between \anti{} and \antf{} in the shallow and deep
     cognitive contexts.}

### 2015-10-29 main.tex
Various APA style changes

@@
 
-\subsection{Role of context in human-robot interaction}
+\subsection{Role of Context in Human-Robot Interaction}
 
@@
 
-\subsection*{Measuring anthropomorphism}
+\subsection*{Measuring Anthropomorphism}
 
@@
 
+\pagebreak
 \section{Experimental Design}
@@
 
-\section{Experiment}
+\pagebreak
+\section{Method}
 
@@
 
-We ran the study with 56 participants (mean age: 20.9, $SD=3.9$, 31 females and
+We ran the study with 56 participants ($M = 20.9$ years old, $SD = 3.9$, 31 females and
 25 males).  The participants were recruited amongst students of our university.
@@
 \vs \emph{human} condition was within-subject (the order of stimuli presentation
-was counter-balanced over the 56 participants). The study lasted in average 15
+was counter-balanced over the participants). The study lasted in average 15
 minutes per participant.
@@
 
-\paragraph{Familiarization and pre-questionnaire}
+\subsubsection{Familiarization and Pre-questionnaire}
 
@@
 
-\paragraph{Stimuli screening}
+\subsubsection{Stimuli Screening}
 
@@
 
-\paragraph{Post-questionnaire and conclusion}
+\subsubsection{Post-questionnaire and Conclusion}
 
 Finally, the participants were asked to fill a post-questionnaire.
-
 Before leaving, possible questions on the purpose of the study were
@@
 
-\subsection{Data Collection}
+\subsection{Measures}
 
-\subsubsection{Gaze variables}
+\subsubsection{Gaze Variables}
 
-As seen in figure~\ref{fig:aoi}, we defined 10 areas of interest (AOIs): one on
+As seen in figure~\ref{fig:aoi}, we defined 10 Areas of Interest (AOIs): one on
 the head of the agent (robot or human), two on the arms (left and right), two on
@@
 
-    \caption{Areas of interest used for the gaze analysis}
+    \caption{Areas of Interest (AOIs) used for the gaze analysis}
     \label{fig:aoi}
@@
 
-We recorded the fixations on each of these 10 zones and normalized by different
-total video duration and surface of AOIs between the robot and human conditions.
-We finally analyzed their distribution, producing what we call \emph{gaze
+We recorded the fixations on each of these zones and normalized them by
+the full duration of the video stimulis and the surface of AOIs between the robot
+and human conditions. We finally analyzed their distribution, producing what we call \emph{gaze
 patterns}.
 
-To compare gazing behaviours across the robot and human conditions, we then
-computed a \emph{difference in gaze patterns} over the $N(=10)$ AOIs:
+To compare gazing behaviours across the robot and human conditions, we besides
+computed a \emph{gaze distribution difference} over the 10 AOIs ($N=10$):
 
-{\large
+{\Large
 \[
@@
 
-\subsubsection{Questionnaires processing}
+\subsubsection{Questionnaires Processing}
 \label{questionnaires_processing}
@@
 
+\pagebreak
 \section{Results}
@@
 
-\subsection{Manipulation check}
+\subsection{Manipulation Check}
 
@@
 task). As can be seen in figure 2, we got a significant correlation in this
-manipulation check ($F[1,54] = 29.0, p < .001$) which validates our manipulation
+manipulation check ($F(1,54) = 29.0, p < .001$) which validates our manipulation
 and supports \h{1}: the participants that were shown the \emph{shallow cognitive
@@
 
-\subsection{Impact of the tendency to anthropomorphize on human
-gazing behaviours}
+\subsection{Impact of the Tendency to Anthropomorphize on Human
+Gazing Behaviours}
 
@@
 the \anti{}. As seen in figure~\ref{h2}, there is a significant negative
-correlation between the two quantities (Pearson Correlation Coefficient = -0.43,
-$p < .001$). The higher the (initial) tendency to anthropomorphize, the smaller
+correlation between the two quantities (Pearson Correlation Coefficient $r(54) = -0.43,
+p < .001$). The higher the (initial) tendency to anthropomorphize, the smaller
 the difference in gazing behaviours between the robot and human conditions. This
@@
     \includegraphics[width=0.5\columnwidth]{H2}\label{GazeDifference-vs-ICA}
-    \caption{Difference in gaze patterns $\delta_{\mathcal{H},
-    \mathcal{R}}^{\text{gaze}}$ \vs \anti{}}
+    \caption{Gaze distribution difference $\delta_{\mathcal{H},
+    \mathcal{R}}^{\text{gaze}}$ \vs initial tendency to anthropomorphize \anti{}}
     \label{h2}
@@
 
-\subsection{Gaze behaviours in shallow \vs deep cognitive contexts}
+\subsection{Gaze Behaviours in Shallow \vs Deep Cognitive Contexts}
 
@@
 were found to be significantly higher than that in the shallow condition
-($F[1,54] = 4.2, p < .05$). For all other AOIs groups, the fixations across
+($F(1,54) = 4.2, p < .05$\fixme{put the exact p value here}). For all other AOIs groups, the fixations across
 shallow and deep conditions were almost the same. Figure~\ref{h3} shows the
@@
 
-\subsection{Correlation between cognitive context and changes in anthropomorphic
-attributions}
+\subsection{Correlation Between Cognitive Context and Changes in Anthropomorphic
+Attributions}
 
@@
 conditions, shows that \deltaant is greater for tasks with a deeper cognitive
-context than that for the shallow cognitive tasks ($F[1,54] = 6.54, p < .05$,
+context than that for the shallow cognitive tasks ($F(1,54) = 6.54, p <
+.05$\fixme{put the exact p value here},
 figure~\ref{h4}). In other words, after being exposed to short videos of a robot
@@
 
+\pagebreak
 \section{Discussion and Conclusion}
 
-\subsection{Discussion of the results}
+\subsection{Discussion of the Results}
 
@@
 
-\subsection{Design of the stimuli and applicability of the method to real world
-scenarios}
+\subsection{Design of the Stimuli and Applicability of the Method to Real World
+Scenarios}
 \label{stimuli_design}

### 2015-10-29 main.tex
Cognitive context -> Cognitive priming (may be incomplete)

@@
 
-\rightheader{Cognitive Context: Impact on the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
+\rightheader{Cognitive Priming: Impact on the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
 \leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
-\title{Cognitive Context: Impact on the Perception of a Robot}
+\title{Cognitive Priming: Impact on the Perception of a Robot}
 
@@
 
-\keywords{human-robot interaction, anthropomorphism, cognitive context, eye-tracking, gaze patterns}
+\keywords{human-robot interaction, anthropomorphism, cognitive priming, eye-tracking, gaze patterns}
 
@@
 useful \emph{proxy} to study these intricate psychological
-bonds. Going in that direction, this article introduces new ways to assess
+bonds. Going in that direction, this article introduces a new way to assess
 anthropomorphic attributions and provides in particular new insights on
-the impact of the cognitive context of the interaction on anthropomorphic
+the impact of \emph{cognitive priming} on anthropomorphic
 attributions.
@@
 We actually build several hypotheses: our baseline hypothesis \h{1} is that we
-can actually create such stimuli that induce recognisable \emph{shallow
-cognitive contexts} and \emph{deep cognitive contexts} (manipulation check); and
-further that these contexts are interpreted by the participants as being
-respectively \emph{machine-like} (low level of anthropomorphic attributions) or
-\emph{human-like} (higher level of anthropomorphic attributions).
+can actually create such stimuli that induce recognisable \emph{shallow} or
+\emph{deeper} cognitive ascriptions onto the robot (manipulation check); and
+further that these different levels of cognitive ascriptions are interpreted by
+the participants as being respectively \emph{machine-like} (low level of
+anthropomorphic attributions) or \emph{human-like} (higher level of
+anthropomorphic attributions).
 
@@
 Then, we hypothesize (\h{3}) that the gaze fixations on the head are
-significantly different depending on the cognitive context, and that a deeper
-cognitive context corresponds to longer gaze fixations on the head. This would
+significantly different depending on the cognitive priming, and that a deeper
+cognitive priming corresponds to longer gaze fixations on the head. This would
 in turn interpreted at \emph{gaze fixations on the head is a proxy for the level
@@
 
-Finally, the hypothesis \h{4} examines whether the cognitive context affects the
+Finally, the hypothesis \h{4} examines whether the cognitive priming affects the
 general tendency to anthropomorphize, \ie whether observing \emph{one}
@@
 attribution of anthropomorphism: if such an effect is found, we can also
-conclude that the cognitive context impacts on the attribution of human-likeness,
+conclude that the cognitive priming impacts on the attribution of human-likeness,
 and this, in turns, supports the hypothesis \h{3} that head fixations would
-reflect not only the cognitive context but also the level of anthropomorphic
-attributions.
+reflect not only the cognitive context of the interaction but also the level of
+anthropomorphic attributions.
 
 Figure~\ref{hyps} illustrate how these four hypotheses relate to \emph{a)}
-cognitive context, \emph{b)} anthropomorphic attributions, and \emph{c)} gaze
+cognitive priming, \emph{b)} anthropomorphic attributions, and \emph{c)} gaze
 patterns.
@@
 
-    \node at (0,0) (ctxt) {Cognitive context};
+    \node at (0,0) (ctxt) {cognitive priming};
     \node at (-3,-3) (anthro) {Anthropomorphic attributions};
@@
 
-\pagebreak
 \section{Experimental Design}
 
-As hinted, this study is build as an eye-tracking experiment (using a stationary
+This study is build as an eye-tracking experiment (using a stationary
 eye-tracker SMI RED 250) where participants watch short videos of an agent --
-either a robot (Aldebaran Robotics' Nao) or a human -- performing very simple
-task (picking an object or pointing toward a sound source), in two different
-socio-cognitive contexts.  These contexts, created by priming and/or audio cues,
-are designed to elicit either a shallow cognitive context (that participants
-would \textit{a posteriori} rate as a \emph{machine-like situation}) or a deeper
-cognitive context (rated as a \emph{human-like situation}).
+either a robot (Aldebaran Robotics' Nao) or a human -- performing simple
+task (picking an object or pointing toward a sound source) after being primed.
+The priming is designed to elicit either shallow cognitive ascriptions onto the
+robot (leading to a \emph{machine-like} situation) or deeper cognitive
+ascriptions (leaning toward a \emph{human-like} situation).
 
@@
 
-The study follows a 2$\times$2 design, summarized in table~\ref{table:design}. Our two
-independent variables are the level of socio-cognitive context (\emph{shallow
-cognitive context} \vs \emph{deep cognitive context}) and the nature of the
-agent appearing in the stimulus (a robot, eliciting a \emph{human-robot} interaction
-situation, or a human, eliciting a \emph{human-human} interaction
-situation).
+The study follows a 2$\times$2 design, summarized in table~\ref{table:design}.
+Our two independent variables are the level of cognitive priming (\emph{shallow}
+\vs \emph{deep}) and the nature of the agent appearing in the stimulus (a robot,
+eliciting a \emph{human-robot} interaction situation, or a human, eliciting a
+\emph{human-human} interaction situation).
 
@@
     \begin{tabular}{l|p{4cm}|p{4cm}}
-        & \tikzmark{top1} Shallow cognitive context & Deep cognitive context \tikzmark{top2}  \\
+        & \tikzmark{top1} Shallow cognitive priming & Deep cognitive priming \tikzmark{top2}  \\
         \hline
@@
         \emph{human} condition is within subject, while the \emph{shallow
-        cognitive context} \vs \emph{deep cognitive context} is between subjects.
+        cognitive priming} \vs \emph{deep cognitive priming} is between subjects.
         Two stimuli (\emph{Picking} task, {\bf A}, and \emph{Pointing} task,
@@
 The audio (and audio only) of these four videos was then edited to create two
-sets of stimuli: one for the \emph{shallow cognitive context} condition, one for
-the \emph{deep cognitive context} condition. The audio editing consisted in
+sets of stimuli: one for the \emph{shallow cognitive priming} condition, one for
+the \emph{deep cognitive priming} condition. The audio editing consisted in
 inserting different commands to initiate the tasks (reported in
@@
 This simple verbal priming (\emph{``brown toy''} \vs \emph{``your favorite
-toy''}) set the cognitive context (\emph{shallow} \vs \emph{deep}) and was
-expected to lead to different perceptions of the interaction
-(\emph{machine-like} \vs \emph{human-like}). We reinforced this effect in the
-\emph{Pointing} task: not only the verbal priming but also the sound played by the
-speakers during the task was altered: either a repetitive bip (\emph{shallow
-cognitive context}) or the sound of a crying baby (\emph{deeper cognitive
-context}).
+toy''}) set the expectations regarding the cognitive capabilities of the robot
+(\emph{shallow} \vs \emph{deep}) and was expected to lead to different
+perceptions of the interaction (\emph{machine-like} \vs \emph{human-like}). We
+reinforced this effect in the \emph{Pointing} task: not only the verbal priming
+but also the sound played by the speakers during the task was altered: either a
+repetitive bip (\emph{shallow cognitive priming}) or the sound of a crying baby
+(\emph{deeper cognitive priming}).
 
@@
 
-\pagebreak
 \section{Method}
@@
 As stated previously, the study follows a 2$\times$2 design
-(table~\ref{table:design}): the \emph{deep} \vs \emph{shallow cognitive context}
+(table~\ref{table:design}): the \emph{shallow} \vs \emph{deep cognitive priming}
 condition was between-subjects (30 participants performed the \emph{deep cognitive}
@@
 
-\pagebreak
 \section{Results}
@@
 Based on the experiments conducted on 56 participants in the human and robot
-interactions across \emph{shallow} and \emph{deep cognitive context} conditions,
+interactions across \emph{shallow} and \emph{deep cognitive priming} conditions,
 we have the following results.\footnote{The detailed statistics and code used
@@
 context} videos identified the task as more robot-like and participants watching
-\emph{deep cognitive context} videos perceived the tasks as more human-like.
+the videos with deeper cognitive priming perceived the tasks as more human-like.
 
@@
 
-\subsection{Gaze Behaviours in Shallow \vs Deep Cognitive Contexts}
+\subsection{Gaze Behaviours in Response to Shallow \vs Deep Cognitive Priming}
 
@@
 together). Based on ANOVA results for the robot in both the shallow and deep
-cognitive context conditions, the fixations on the head in the deep condition
+cognitive priming conditions, the fixations on the head in the deep condition
 were found to be significantly higher than that in the shallow condition
@@
     \caption{Gaze fixations on the different areas on interest, for shallow \vs
-    deep cognitive context conditions.}
+    deep cognitive priming conditions.}
     \label{h3}
@@
 the human condition, the presence of the human is intrinsically a source of deep
-cognitive context, hiding the effects of our manipulation on a shallow \vs deep
-cognitive context.
+cognitive expectations, hiding the effects of our manipulation on a shallow \vs deep
+cognitive priming.
 
-\subsection{Correlation Between Cognitive Context and Changes in Anthropomorphic
+\subsection{Correlation Between Cognitive Priming and Changes in Anthropomorphic
 Attributions}
@@
 figure~\ref{h4}). In other words, after being exposed to short videos of a robot
-performing simple tasks, participants primed with a deeper cognitive context report
-a significantly higher tendency to anthropomorphize robots \emph{in general} (as
-the questionnaire on anthropomorphic attributions explicitly referred to
-\emph{robots in general}).
+performing simple tasks, participants primed with a deeper cognitive
+expectations report a significantly higher tendency to anthropomorphize robots
+\emph{in general} (as the questionnaire on anthropomorphic attributions
+explicitly referred to \emph{robots in general}).
 
@@
     \caption{Difference between \anti{} and \antf{} in the shallow and deep
-    cognitive contexts.}
+    cognitive priming conditions.}
     \label{h4}
@@
 
-This result supports \h{4} and validate that the cognitive context impacts the
+This result supports \h{4} and validate that the cognitive priming impacts the
 attribution of anthropomorphic features to robots. This, in turn, supports the
@@
 
-\pagebreak
-\section{Discussion and Conclusion}
+\section{Discussion}
 
@@
 context was indeed associated to a robot-like situation, while a deeper
-cognitive context was associated to a human-like situation (\h{1}). This is
-already an interesting result: subtle changes in the cognitive contexts are
+cognitive priming was associated to a human-like situation (\h{1}). This is
+already an interesting result: subtle changes in the cognitive priming are
 recognized and clearly interpreted in terms of human-likeness.
@@
 The third hypothesis \h{3} proposes that head fixations are related to the
-cognitive context, which is clearly supported by our data: in deeper cognitive
-context, one tends to spend more time looking at the head of the interacting
-agent than in a shallow cognitive context. We also hypothesized that, in turn,
+cognitive expectations, which is clearly supported by our data: after deeper cognitive
+priming, one tends to spend more time looking at the head of the interacting
+agent than after shallow cognitive priming. We also hypothesized that, in turn,
 head fixations could act as a \emph{proxy to anthropomorphic projections}: as
@@
 projections, with the hypothesis that watching an interaction with a particular
-robot in a deeper cognitive context may impact \emph{globally} the
+robot after a deeper cognitive priming may impact \emph{globally} the
 anthropomorphic perceptions of robots. This is supported by our study.
-
-\subsection{Summary and Contributions}
-
-The study and results presented in this article lead to two main contributions:
-new insights on the impact of the cognitive context on the perception of a robot
-by humans; a novel unbiased methodology based on eye-tracking to assess
-anthropomorphic attributions during a running human-robot interaction.
-
-Our first contribution extends our understanding of the attribution of
-human-like characteristics to robot by exploring the role of the interaction
-context. As we show, it appears that even relatively subtle context
-priming may lead to significantly different anthropomorphic perceptions of
-the exact same robot, performing the exact same task, as confirmed both by
-distinct gaze patterns, and different reported perceptions in questionnaires.
-Interestingly, this effects can already be evidenced after very short,
-one-way, interactions (less than 2 minutes).
-
-This leads to a second-order effect that we also evidence here: depending on the
-cognitive context, the tendency to attribute human-like characteristics to robot
-evolves in significantly different ways. After observing a robot in a
-context that pre-suppose deeper cognitive capabilities, people increase
-their general tendency to anthropomorphize robots compared to a shallow
-cognitive context, even though the robot appearance and visual behaviour is the
-exact same.
-
-The second contribution is a methodological one: we present in this article
-a novel technique to assess anthropomorphic projections that relies on a
-biometric measurement (eye-tracking) to compare gaze fixation durations on
-the face of the robot. We cross-validate this new metric with existing,
-established, questionnaires. Compared to current techniques (post-hoc
-annotations of videos and questionnaires), this new approach is objective,
-is less impacted by experimental biases (like the \emph{observer effect},
-where the behaviour of the participant is impacted by the fact he/she knows that
-he/she is observed) and take place during the interaction itself
-(\emph{in-the-moment} measurement).
-
-Besides, we also introduce a new kind of visual stimuli, specifically designed
-to study the impact of non-appearance, non-behavioural related effects on the
-human-like perception of robots. We make these video stimuli available to the
-community, and therefore invite our colleagues to reproduce our experimental
-results. The next section describe the specificities of these stimuli, and also
-discuss how such a methodology can apply to real-world scenarios.
-
-As a whole, the article attempts to contribute to our understanding of an
-intricate psychological effects that come to play when humans and robots
-interact, both in terms of methodology and experimental evidence.
 
@@
 
-Finally, the situations needed to support two possible cognitive contexts
-(shallow \vs deeper cognitive context), and triggering one or the other of these
+Finally, the situations needed to support two possible kind of cognitive priming
+(shallow \vs deeper cognitive priming), and triggering one or the other of these
 contexts needed to be done \emph{without changing} the visual part of the
@@
 agent was either asked to \emph{``Show some movements''} (\emph{shallow
-cognitive context} condition) or to \emph{``Dance with the music''}
-(\emph{deeper cognitive context} condition). While all the participants were
+cognitive priming} condition) or to \emph{``Dance with the music''}
+(\emph{deeper cognitive priming} condition). While all the participants were
 shown this stimuli as well, we decided to exclude it from the results as we
@@
 
+\section{Conclusion}
+
+The study and results presented in this article lead to two main contributions:
+new insights on the impact of the cognitive priming on the perception of a robot
+by humans; a novel unbiased methodology based on eye-tracking to assess
+anthropomorphic attributions during a running human-robot interaction.
+
+Our first contribution extends our understanding of the attribution of
+human-like characteristics to robot by exploring the role of the interaction
+context. As we show, it appears that even relatively subtle context
+priming may lead to significantly different anthropomorphic perceptions of
+the exact same robot, performing the exact same task, as confirmed both by
+distinct gaze patterns, and different reported perceptions in questionnaires.
+Interestingly, this effects can already be evidenced after very short,
+one-way, interactions (less than 2 minutes).
+
+This leads to a second-order effect that we also evidence here: depending on the
+cognitive priming, the tendency to attribute human-like characteristics to robot
+evolves in significantly different ways. After observing a robot in a
+context that pre-suppose deeper cognitive capabilities, people increase
+their general tendency to anthropomorphize robots compared to a shallow
+cognitive priming, even though the robot appearance and visual behaviour is the
+exact same.
+
+The second contribution is a methodological one: we present in this article
+a novel technique to assess anthropomorphic projections that relies on a
+biometric measurement (eye-tracking) to compare gaze fixation durations on
+the face of the robot. We cross-validate this new metric with existing,
+established, questionnaires. Compared to current techniques (post-hoc
+annotations of videos and questionnaires), this new approach is objective,
+is less impacted by experimental biases (like the \emph{observer effect},
+where the behaviour of the participant is impacted by the fact he/she knows that
+he/she is observed) and take place during the interaction itself
+(\emph{in-the-moment} measurement).
+
+Besides, we also introduce a new kind of visual stimuli, specifically designed
+to study the impact of non-appearance, non-behavioural related effects on the
+human-like perception of robots. We make these video stimuli available to the
+community, and therefore invite our colleagues to reproduce our experimental
+results. The next section describe the specificities of these stimuli, and also
+discuss how such a methodology can apply to real-world scenarios.
+
+As a whole, the article attempts to contribute to our understanding of an
+intricate psychological effects that come to play when humans and robots
+interact, both in terms of methodology and experimental evidence.
+
+\fixme{Properly conclude the paper: what does our research reveals?}
+
 \section*{Acknowledgments}

### 2015-11-02 main.tex
New tentative title

@@
 
-\rightheader{Cognitive Priming: Impact on the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
+\rightheader{Shaping the Perception of a Robot by Cognitive Priming}   % This should be the title, or a shortened version of the title if your title is long.
 \leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
-\title{Cognitive Priming: Impact on the Perception of a Robot}
+\title{Shaping the Perception of a Robot as a Human-Like Agent by Cognitive
+Priming}
 

### 2015-11-03 main.tex
Rewritten abstract

@@
 \abstract{
-What leads us to attribute human-like characteristics to robots? The physical
-appearance of the robot and the design of its behaviours do obviously play a key
-role. This paper however reveals another mechanism at play, which is more subtle
-and partially unconscious: the context of the interaction, and more precisely,
-the cognitive prerequisites that the interaction presupposes.
+What leads us to perceive robots as human-like agents? The physical appearance
+of the robot and the design of its behaviours (the anthropomorphic \emph{design}
+of the robot) do certainly play an important role. This paper sheds light on
+another mechanism at play, less obvious because partially unconscious: the
+cognitive skills that the interaction situation presupposes.
 
-To study this effect, we propose an original methodology based on eye-tracking
+We evidence this effect with a novel methodology based on eye-tracking
 and a set of stimuli that are visually identical and yet induce different
-assumptions regarding the cognitive capabilities of the robot. We then correlate
-the gaze patterns with established questionnaires that assess anthropomorphic
-attributions.
+assumptions regarding the cognitive capabilities of the robot. By correlating
+the resulting gaze patterns with answers to established questionnaires on
+anthropomorphic attributions, we show that fixations on the head of the robot
+indeed reflect how we perceive the machine.
 
-\begin{inparaenum}[\itshape a\upshape)]
-As a result, we show that \item specific gaze patterns (fixations on the head of
-the robot) correlate with post-hoc anthropomorphic
-attributions, and hence, eye-tracking can be used as a novel \emph{in-the-moment}
-metric of anthropomorphism, and \item simple context priming is sufficient
-to elicit significantly different anthropomorphic attributions.
-\end{inparaenum}
+Interestingly, we also show that humans appear quite sensitive to this effect:
+even subtle context priming is sufficient to elicit significantly different
+anthropomorphic attributions, and as such, this article provides new insights on
+how our expectations of the robot's cognitive competency shape the bonds that we
+build with the machine.
 

### 2015-11-03 main.tex
Re-organized and mostly rewritten intro

@@
 
-Robotics researchers often tend to consider that anthropomorphism only describes
-a static set of human-like features of a robot (like its shape, its speech
-capabilities, facial expressions, etc.).
-Following~\citet{fink_anthropomorphism_2012}, we refer to these characteristics
-as the \emph{anthropomorphic design} of the robot, and we call
-\emph{anthropomorphism} the general \emph{social phenomenon} that emerges from
-the (real or imagined) interaction between a non-human agent (a robot in our
-case) and a human~\citep{persson_anthropomorphism_2000}.  According
-to~\citet{epley_when_2008}, anthropomorphism includes the human perception of
-emotional states, motivations, intentions in the non-human agent, and tends to
-ascribe those qualities to it. As such, the dynamic and socio-cognitive
-dimensions of anthropomorphism are essential to understand the complex bonds
-that human users build with artificial agents such as
-robots~\citep{lemaignan2014dynamics}. Therefore anthropomorphism appears to be a
-useful \emph{proxy} to study these intricate psychological
-bonds. Going in that direction, this article introduces a new way to assess
-anthropomorphic attributions and provides in particular new insights on
-the impact of \emph{cognitive priming} on anthropomorphic
-attributions.
+Researchers in robotics often tend to see anthropomorphism as the static set of
+human-like features of a robot (like its shape, its speech capabilities, facial
+expressions, etc.). Following~\citet{fink_anthropomorphism_2012}, we refer to
+these characteristics as the \emph{anthropomorphic design} of the robot, and we
+call instead \emph{anthropomorphism} the \emph{social phenomenon} that arises
+from the (real or imagined) interaction between a non-human agent (a robot in
+our case) and a human~\citep{persson_anthropomorphism_2000}. As such,
+anthropomorphism includes the perception of emotional states, motivations,
+intentions in the non-human agent, and, conversely, the ascriptions of those
+qualities to them~\citep{epley_when_2008}.
 
-\subsection{Role of Context in Human-Robot Interaction}
+Being such a central ingredient of the psychological ``sauce'' that binds humans to
+robots, the field of human-robot interaction (HRI) has long~\fixme{ref?}
+attempted to manipulate the anthropomorphic attributes we ascribe to robots.
+While modifying the anthropomorphic \emph{design} of robots is conceptually
+easy, influencing the underlying psychological phenomenon is less
+obvious, although likely more effective.
 
-The study of context in human-robot interaction (HRI) is not new.
-\textit{Context of use} is defined by the ISO as \textit{``users, tasks,
-equipment (hardware, software and materials), and the physical and social
-environments in which a product is used''}.  Accordingly, there are various
-aspects that can impact how a robot is experienced. The real or imagined
-\textit{purpose} of a robot, including the application context in which it is
-typically used (\eg office environment, home, rehabilitation center, public
-space, \etc) as well as the task context (\eg serious or playful task;
-composition of human-robot team; number of users) and the (social) role in which
-the robot is used / experienced are to be taken into account.
+One way consists in manipulating the context of use of the robot: when social,
+entertaining or playful, it elicits more anthropomorphic attributions compared
+routine or focused, serious situations (security, rescue, \etc).
+\citet{joosse_what_2013} showed, for instance, that when the same robot (a {\sc
+nao} humanoid) was used in a different task context (cleaning task \vs tour
+guide), users would ascribe different personalities to the robot. Along the same
+line, \citet{goetz_cooperation_2002} found that people prefer a serious robot
+for serious tasks and a less serious robot for more playful tasks. Also related,
+\citet{kaplan_free_2000} discussed how the uselessness of the robot impacts our
+tendency to anthropomorphize it: artificial pets like AIBO have no real purpose,
+in a sense that they do not provide any kind of service, and this very aspect
+may increase people's tendency to anthropomorphize them.
 
-Notably, when the context of use of a robot is social, entertaining or playful,
-it will enhance anthropomorphism compared to when the context is a routine or
-focused serious task (security, rescue, \etc).  \citet{joosse_what_2013} showed,
-for instance, that when the same robot ({\sc nao}) was used in a different task
-context (cleaning task \vs tour guide), users ascribed different personalities
-to the robot. \citet{goetz_cooperation_2002} revealed a link between a robot's
-context of use and people's perception of the robot: the authors found that
-people prefer a serious robot for serious tasks and a less serious robot for
-more playful tasks. \citet{kaplan_free_2000} discussed the role of uselessness
-in the design of robots. The author argues that artificial pets like AIBO have
-no real purpose, in a sense that they do not provide any kind of service or, in
-other words, \textit{``they are not doing what you tell them to do''} and
-\textit{``they might refuse the order of its owner''}. It may be this very
-aspect that increases people's tendency to anthropomorphize the robot. According
-to Kaplan, it is in our daily use language that we tend to attribute intentions
-to devices that are not doing their job well.
+We may hypothesize that these results are a consequence of different
+expectations we form about the robot depending on the context: when a machine is
+embedded in a social situation, for instance, we expect it to exhibit certain
+social skills. However, the experiments conducted so far explore prototypical
+opposite situations (routine \vs playful, typically boring \vs typically
+intellectual): while they do confirm that the interaction context impacts our
+perception of the robot, the stark contrast of the conditions makes it difficult
+to finely analyse the psychological determinants that explain the different
+perception of the robot.\fixme{references are needed} In particular, existing
+techniques to measure anthropomorphism traditionally rely on questionnaires that
+may suffer post-hoc reconstruction (we come back on this hereafter).
 
-These previous studies investigated users' perception of robots in
-prototypical situations (routine \vs playful, typically boring \vs typically
-intellectual) and their results nicely supports our general intuition.
-In this article, we show that much more subtle variations in the task context do
-lead to very noticeable effects as well.
+This article attempts to address this issue with a different experimental design
+and a novel methodology to measure \emph{in-the-moment} anthropomorphic attributions.
+Our approach is built on a combination of cognitive priming and eye-tracking,
+and evidences specific gaze fixations on the head of the robot when the
+participants are primed with higher expectations regarding the cognitive skills
+of the robot.
 
-\subsection*{Measuring Anthropomorphism}
+\subsection{Cognitive Priming and Interaction Situation}
 
-Measuring anthropomorphism raises
-interesting methodological challenges, if only because people's perception of
-robots change over the duration of their interaction with the
-robots~\citep{lemaignan2014dynamics}. \citet{takayama_perspectives_2012}
-discusses the effects of these changes and differentiates between what she calls
-an \emph{in-the-moment} and a \emph{reflective} perspective on agency: an
-\emph{in-the-moment} perspective would refer to one's most immediate
-response/sense in a given situation whereas a \emph{reflective} perspective would
-indicate one's reaction/sense of a situation based on a more in-depth
-consideration and contemplation.  In the first phase of interaction with a
-robot, people might respond ``mindlessly'' instead of responding
-consciously~\citep{nass_machines_2000}, and only after what is called the
-\emph{familiarization} period, one might respond in a more reflective manner
-instead of an in-the-moment reaction: \citet{reeves_media_1996} showed for
-instance that participants interacting with technologies in ways close to how they
-would behave towards people, would still deny any human-like interaction in a post-hoc
-questionnaire, illustrating this reflective perspective.
+\textbf{TBD: Kshitij} at the end of this section, the reader must be convinced
+that:
+\begin{itemize}
+    \item cognitive priming is a well established technique, grounded in the
+        litterature,
+    \item our terminology ('shallow' vs 'deep') is meaningful, and grounded
+    \item our cognitive priming would impact the perception of the interaction
+        situation as machine-like vs human-like (to support our manipulation
+        check!)
+\end{itemize}
 
-Yet, most of the experiments that investigate anthropomorphism in HRI are based
-on post-interaction, closed questionnaires or rating scales.  The Godspeed
+\subsection{Measuring Anthropomorphism}
+
+Assessing anthropomorphic attributions during a human-robot interaction is an
+indirect mean to explore the intricate -- and dynamic -- bonds that build up
+between the robot and its human partner. As such, a lot of literature in HRI has
+investigated means of measuring anthropomorphism. This indeed raises interesting
+methodological challenges, if only because of high inter-personal variations in
+one's tendency to anthropomorphize~\fixme{ref?}, and the dynamic nature of
+anthropomorphic attributions~\citep{lemaignan2014dynamics}.
+
+One phenomenon requires particular attention: well established in the
+psychological literature in terms of \emph{impulsive} or \emph{automatic} \vs
+\emph{reflective} behaviours~\citep{strack2004reflective}, the way we behave and
+perceive \emph{in-the-moment} is significantly different from what results from
+a thoughtful (and slower) reflection on the situation. As noted by
+\citet{takayama_perspectives_2012} for instance, this also impacts our
+perspective on agency, and in fact, as shown by~\citet{nass_machines_2000}, in
+the first phase of interaction with a robot, people might respond mindlessly,
+and only after the so-called \emph{familiarization} period, one might respond in
+a more conscious, reflective manner. The typical illustration of this mechanism
+is found in~\citet{reeves_media_1996} who showed that participants who would
+interact with technologies in ways similar to how they interact with people,
+would however {\it a posteriori} typically deny having performed an human-like
+interaction.
+
+Yet, most of the methodologies available to assess anthropomorphic ascriptions
+in HRI are limited to post-interaction measurement, mainly in the form of closed
+questionnaires or rating scales. The Godspeed
 questionnaire~\citep{bartneck_measurement_2008}, and in particular, its subpart
@@
 two-dimensional scale measuring \emph{Human Nature} and \emph{Uniquely Human}
-traits of robots, based on an original proposal by \citet{haslam2008attributing}.
+traits of robots, based on an original proposal by
+\citet{haslam2008attributing}.
 
-We explore here a different approach to measure anthropomorphism, based on
-eye-tracking.  By looking at the eyes fixation on the head of the robot, we have
-been able to demonstrate significantly different patterns in two experimental
-conditions subtly different in terms of human-likeness. This eye-tracking based
-metric is behavioural and hence does not suffer post-hoc reconstruction by the
-participants, possibly providing a better, ``noise-less'', access to the human
-attitude towards the machine, and, as such, a better proxy to the cognitive and
-affective bonds that the human establishes with the robot.
+We explore hereafter a different approach to measure anthropomorphism, based on
+eye-tracking. By looking at the eyes fixation on the head of the robot, we show
+significantly different gazing behaviours in two experimental conditions that
+differ in terms of the (projected) robot's human-likeness. This eye-tracking
+based metric is behavioural -- hence not prone to post-hoc reconstruction by the
+participants -- and \emph{in-the-moment} -- mitigating the impact of a reflective
+elaboration on the nature of the human-robot interaction. We believe that these
+two improvements over existing techniques provide a solid ground for the study
+of the socio-cognitive bonds that establish between humans and robots when they
+interact.
 
@@
 evolves in significantly different ways. After observing a robot in a
-context that pre-suppose deeper cognitive capabilities, people increase
+context that presupposes deeper cognitive capabilities, people increase
 their general tendency to anthropomorphize robots compared to a shallow

### 2015-11-03 main.tex
WIP on the hypotheses

@@
 
-The study has been designed out of the following intuition: \emph{the more we
-ascribe cognitive capabilities to an agent, the more we focus on its head when
-interacting with it}. Eye-tracking is a natural methodology to investigate
-this intuition. We hence design audio-visual stimuli that elicit different
-levels of cognitive ascription onto the robot while being identical in every
-other way.
+\begin{inparaenum}[\itshape a\upshape)]
+Two nested research questions have been presented so far: \item can we
+characterize the link between expectations regarding the cognitive
+skills of a robot and the effective ascription of anthropomorphic features to
+this robot; and \item to this end, can we develop and validate a behavioural and
+\emph{in-the-moment} metric of anthropomorphism?  \end{inparaenum}
 
-We actually build several hypotheses: our baseline hypothesis \h{1} is that we
-can actually create such stimuli that induce recognisable \emph{shallow} or
-\emph{deeper} cognitive ascriptions onto the robot (manipulation check); and
-further that these different levels of cognitive ascriptions are interpreted by
-the participants as being respectively \emph{machine-like} (low level of
-anthropomorphic attributions) or \emph{human-like} (higher level of
-anthropomorphic attributions).
+These two questions translate into several experimental hypotheses, whose design
+was guided by the following intuition: \emph{the more we ascribe cognitive
+capabilities to an agent, the more likely we are to focus on its head when
+interacting with it}, which suggests an eye-tracking-based investigation.
 
-Secondly, we hypothesize (\h{2}) that the \emph{difference} of gaze
-behaviours between the human and robot conditions correlates with the
-participants' initial tendency to anthropomorphize, measured from a standard
-pre-questionnaire: we expect that people with high tendency to anthropomorphize
-will tend to have smaller differences in their gaze behaviours while watching
-either a robot or a human performing the same task: if this can be observed, it
-would also show that anthropomorphic attributions are related to gaze patterns.
+%Eye-tracking-based technique logically follows as an investigation mean, is a natural
+%methodology to investigate this intuition. We hence design audio-visual stimuli
+%that elicit different levels of cognitive ascription onto the robot while being
+%identical in every other way.
 
-Then, we hypothesize (\h{3}) that the gaze fixations on the head are
-significantly different depending on the cognitive priming, and that a deeper
-cognitive priming corresponds to longer gaze fixations on the head. This would
-in turn interpreted at \emph{gaze fixations on the head is a proxy for the level
-of human-likeness attribution}, and constitutes the core hypothesis of this
-article.
+Our baseline hypothesis \h{1} is that cognitive priming allows us to effectively create
+stimuli that induce \emph{shallow} or \emph{higher} expectations regarding the
+cognitive skills of the robot. This hypothesis is to be tested by asking
+participants to rate the interactions depicted by the stimuli as being more
+\emph{machine-like} (low ascription of cognitive skills) or \emph{human-like}
+(higher expectation of cognitive competency).
 
-Finally, the hypothesis \h{4} examines whether the cognitive priming affects the
-general tendency to anthropomorphize, \ie whether observing \emph{one}
+Secondly, we hypothesize that people with a higher tendency to anthropomorphize
+robots will tend to look at robots and humans in similar ways, contrary to
+people with a lower tendency to anthropomorphize (\h{2}). If this is verified,
+it supports the idea that anthropomorphic attributions affect gaze patterns. The
+hypothesis can be tested by correlating the participants' tendency to
+anthropomorphize, measured from a standard questionnaire, with the comparative
+gazing behaviour in two conditions (human task \vs robot task).
+
+Third, we hypothesize that in the \emph{human-like} condition (higher ascription
+of cognitive skills to the robot), the participants' gaze will be directed
+significantly more towards the head of the robot than in the \emph{machine-like}
+condition (low ascription of cognitive skills) (\h{3}). If verified, it
+effectively means that the expectations held by the participants regarding the
+cognitive capabilities of the robot are reflected by the eye fixations on the
+head of the robot.  The hypothesis can be tested by comparing gaze fixations in
+the two conditions (\emph{human-like} \vs \emph{machine-like}).
+
+Finally, the hypothesis \h{4} proposes that manipulating cognitive expectations
+affects the broader tendency to anthropomorphize robots, \ie whether observing one
 robot acting in an \emph{human-like} context leads to an increased level of
-anthropomorphic attributions to robots \emph{in general}. This also provides us
-with a way to triangulate the behavioural measures with the subjective
-attribution of anthropomorphism: if such an effect is found, we can also
-conclude that the cognitive priming impacts on the attribution of human-likeness,
-and this, in turns, supports the hypothesis \h{3} that head fixations would
-reflect not only the cognitive context of the interaction but also the level of
-anthropomorphic attributions.
+anthropomorphic attributions to robots in general. The hypothesis can be
+tested by looking at pre- and post-experiment self-reports on the tendency to
+anthropomorphize.
 
-Figure~\ref{hyps} illustrate how these four hypotheses relate to \emph{a)}
-cognitive priming, \emph{b)} anthropomorphic attributions, and \emph{c)} gaze
-patterns.
+If all these hypotheses are verified, the findings can be summarized as follow:
+\h{1} shows that our manipulation (based on cognitive priming) does effectively
+elicit lower or higher expectations in terms of the cognitive capabilities of
+the robot; \h{4} shows that these expectations influence our tendency to
+anthropomorphize robots; in parallel, \h{3} shows that these same expectations
+shape the way we look at the robot by eliciting specific eye fixations on the
+head of the robot; finally, \h{2} suggests that the fixation on the head
+reflects human-likeliness and supports the thesis that head fixation can be used
+as a behavioural measure of anthropomorphism.
 
-\begin{figure}[ht]
-\centering
-
-\resizebox{0.5\linewidth}{!}{%
-
-\begin{tikzpicture}[
-    >=latex,
-    every edge/.style={->,draw, very thick},
-    every node/.style={draw, circle, text centered, text width=2.7cm}]
-
-    \node at (0,0) (ctxt) {cognitive priming};
-    \node at (-3,-3) (anthro) {Anthropomorphic attributions};
-    \node at (3,-3)[circle split, text width=2.5cm] (gaze) {\textit{\small Fixations \\on head} \nodepart{lower} \textit{\small Gaze
-distribution \\differences}};
-    \node [draw=none,anchor=east,left=-0.5cm of gaze.west] (gazecap) {\large Gaze:};
-
-    \path[every node/.style={draw=none}]
-            (ctxt) edge [bend right] node[left] {\h{1}, \h{4}} (anthro)
-            (ctxt) edge [bend left] node[right] {\h{3}} (gaze.north)
-            (anthro) edge [bend right] node[above] {\h{2}} (gaze.south);
-\end{tikzpicture}
-}
-
-\caption{Hypotheses of interactions between the three main concepts studied in
-the article. Arrows mean ``A impacts B''.}
-
-    \label{hyps}
-\end{figure}
+%Figure~\ref{hyps} illustrate how these four hypotheses relate to \emph{a)}
+%cognitive priming, \emph{b)} anthropomorphic attributions, and \emph{c)} gaze
+%patterns.
+%
+%\begin{figure}[ht]
+%\centering
+%
+%\resizebox{0.5\linewidth}{!}{%
+%
+%\begin{tikzpicture}[
+%    >=latex,
+%    every edge/.style={->,draw, very thick},
+%    every node/.style={draw, circle, text centered, text width=2.7cm}]
+%
+%    \node at (0,0) (ctxt) {cognitive priming};
+%    \node at (-3,-3) (anthro) {Anthropomorphic attributions};
+%    \node at (3,-3)[circle split, text width=2.5cm] (gaze) {\textit{\small Fixations \\on head} \nodepart{lower} \textit{\small Gaze
+%distribution \\differences}};
+%    \node [draw=none,anchor=east,left=-0.5cm of gaze.west] (gazecap) {\large Gaze:};
+%
+%    \path[every node/.style={draw=none}]
+%            (ctxt) edge [bend right] node[left] {\h{1}, \h{4}} (anthro)
+%            (ctxt) edge [bend left] node[right] {\h{3}} (gaze.north)
+%            (anthro) edge [bend right] node[above] {\h{2}} (gaze.south);
+%\end{tikzpicture}
+%}
+%
+%\caption{Hypotheses of interactions between the three main concepts studied in
+%the article. Arrows mean ``A impacts B''.}
+%
+%    \label{hyps}
+%\end{figure}
 

### 2016-01-26 main.tex
Shorten the title
new results
New results for some more statistical power and answers to a few
comments in the reviews

@@
 \leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
-\title{Shaping the Perception of a Robot as a Human-Like Agent by Cognitive
-Priming}
+\title{Shaping the Perception of a Robot by Cognitive Priming}
 
@@
 
-We evidence this effect with a novel methodology based on eye-tracking
+We show that humans appear quite sensitive to this effect:
+even subtle context priming is sufficient to elicit significantly different
+anthropomorphic attributions, and as such, this article provides new insights on
+how our expectations of the robot's cognitive competency shape the bonds that we
+build with the machine.
+
+We evidence the effect with a novel methodology based on eye-tracking
 and a set of stimuli that are visually identical and yet induce different
@@
 anthropomorphic attributions, we show that fixations on the head of the robot
-indeed reflect how we perceive the machine.
-
-Interestingly, we also show that humans appear quite sensitive to this effect:
-even subtle context priming is sufficient to elicit significantly different
-anthropomorphic attributions, and as such, this article provides new insights on
-how our expectations of the robot's cognitive competency shape the bonds that we
-build with the machine.
+indeed reflect how we anthropomorphize the machine.
 
@@
 Being such a central ingredient of the psychological ``sauce'' that binds humans to
-robots, the field of human-robot interaction (HRI) has long~\fixme{ref?}
+robots, the field of human-robot interaction (HRI) has long
 attempted to manipulate the anthropomorphic attributes we ascribe to robots.
@@
 easy, influencing the underlying psychological phenomenon is less
-obvious, although likely more effective.
+obvious, although possibly as effective.
 
@@
 routine or focused, serious situations (security, rescue, \etc).
-\citet{joosse_what_2013} showed, for instance, that when the same robot (a {\sc
-nao} humanoid) was used in a different task context (cleaning task \vs tour
-guide), users would ascribe different personalities to the robot. Along the same
+\citet{joosse_what_2013} showed, for instance, that users would ascribe
+different personalities to the same robot (a {\sc nao} humanoid) when it was
+used in a different task context (cleaning task \vs tour guide). Along the same
 line, \citet{goetz_cooperation_2002} found that people prefer a serious robot
@@
 \citet{kaplan_free_2000} discussed how the uselessness of the robot impacts our
-tendency to anthropomorphize it: artificial pets like AIBO have no real purpose,
+tendency to anthropomorphise it: artificial pets like AIBO have no real purpose,
 in a sense that they do not provide any kind of service, and this very aspect
-may increase people's tendency to anthropomorphize them.
+may increase people's tendency to anthropomorphise them.
 
-We may hypothesize that these results are a consequence of different
+We may hypothesise that these results are a consequence of different
 expectations we form about the robot depending on the context: when a machine is
-embedded in a social situation, for instance, we expect it to exhibit certain
-social skills. However, the experiments conducted so far explore prototypical
-opposite situations (routine \vs playful, typically boring \vs typically
+embedded in a social situation, we expect it to exhibit certain
+social skills. The experiments conducted so far only contrast prototypical
+\emph{opposite} interaction situations (routine \vs playful, typically boring \vs typically
 intellectual): while they do confirm that the interaction context impacts our
@@
 to finely analyse the psychological determinants that explain the different
-perception of the robot.\fixme{references are needed} In particular, existing
+perception of the robot. In particular, existing
 techniques to measure anthropomorphism traditionally rely on questionnaires that
-may suffer post-hoc reconstruction (we come back on this hereafter).
+may suffer post-hoc reconstruction (we further discuss this point hereafter).
 
@@
 participants are primed with higher expectations regarding the cognitive skills
-of the robot.
+of the robot. This methodology leads us next to uncover and evidence the significant
+impact of even subtle contextual cues on humans' tendency to ascribe human
+traits to machines.
 
@@
     \item cognitive priming is a well established technique, grounded in the
-        litterature,
+        literature,
     \item our terminology ('shallow' vs 'deep') is meaningful, and grounded
@@
 methodological challenges, if only because of high inter-personal variations in
-one's tendency to anthropomorphize~\fixme{ref?}, and the dynamic nature of
+one's tendency to anthropomorphise~\fixme{ref?}, and the dynamic nature of
 anthropomorphic attributions~\citep{lemaignan2014dynamics}.
@@
 the first phase of interaction with a robot, people might respond mindlessly,
-and only after the so-called \emph{familiarization} period, one might respond in
+and only after the so-called \emph{familiarisation} period, one might respond in
 a more conscious, reflective manner. The typical illustration of this mechanism
@@
 Two nested research questions have been presented so far: \item can we
-characterize the link between expectations regarding the cognitive
+characterise the link between expectations regarding the cognitive
 skills of a robot and the effective ascription of anthropomorphic features to
@@
 
-Secondly, we hypothesize that people with a higher tendency to anthropomorphize
+Secondly, we hypothesise that people with a higher tendency to anthropomorphise
 robots will tend to look at robots and humans in similar ways, contrary to
-people with a lower tendency to anthropomorphize (\h{2}). If this is verified,
+people with a lower tendency to anthropomorphise (\h{2}). If this is verified,
 it supports the idea that anthropomorphic attributions affect gaze patterns. The
 hypothesis can be tested by correlating the participants' tendency to
-anthropomorphize, measured from a standard questionnaire, with the comparative
+anthropomorphise, measured from a standard questionnaire, with the comparative
 gazing behaviour in two conditions (human task \vs robot task).
 
-Third, we hypothesize that in the \emph{human-like} condition (higher ascription
+Third, we hypothesise that in the \emph{human-like} condition (higher ascription
 of cognitive skills to the robot), the participants' gaze will be directed
@@
 Finally, the hypothesis \h{4} proposes that manipulating cognitive expectations
-affects the broader tendency to anthropomorphize robots, \ie whether observing one
+affects the broader tendency to anthropomorphise robots, \ie whether observing one
 robot acting in an \emph{human-like} context leads to an increased level of
@@
 tested by looking at pre- and post-experiment self-reports on the tendency to
-anthropomorphize.
+anthropomorphise.
 
-If all these hypotheses are verified, the findings can be summarized as follow:
+If all these hypotheses are verified, the findings can be summarised as follow:
 \h{1} shows that our manipulation (based on cognitive priming) does effectively
@@
 the robot; \h{4} shows that these expectations influence our tendency to
-anthropomorphize robots; in parallel, \h{3} shows that these same expectations
+anthropomorphise robots; in parallel, \h{3} shows that these same expectations
 shape the way we look at the robot by eliciting specific eye fixations on the
@@
 
-The study follows a 2$\times$2 design, summarized in table~\ref{table:design}.
+The study follows a 2$\times$2 design, summarised in table~\ref{table:design}.
 Our two independent variables are the level of cognitive priming (\emph{shallow}
@@
         \hline
-        \tikzmark{left1} Robot & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favorite toy''} \\
+        \tikzmark{left1} Robot & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favourite toy''} \\
                                & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''} \\
         \hline
-        \tikzmark{left2} Human & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favorite toy''} \\ 
+        \tikzmark{left2} Human & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favourite toy''} \\ 
                                & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''}\tikzmark{bottom} \\
@@
 Four different video stimuli where filmed (figure~\ref{fig:stimuli}): two
-different tasks (picking a stuffed animal, refered hereafter as the
-\emph{Picking} task, and pointing towards a source of sound, refered as the
+different tasks (picking a stuffed animal, referred hereafter as the
+\emph{Picking} task, and pointing towards a source of sound, referred as the
 \emph{Pointing} task) acted either by a human or a robot. Video stimuli were
@@
 particular walks) compared to human.\footnote{To make sure the difference of
-video lenght does not bias gaze distributions, we ran a $\chi^2$ test between
+video length does not bias gaze distributions, we ran a $\chi^2$ test between
 the gaze distributions of the first half and the second half of the robot
@@
 that the agent had to pick was described either as a \emph{``brown toy''} or as
-\emph{``your favorite toy''}. In the former case, the object was refered through
+\emph{``your favourite toy''}. In the former case, the object was referred through
 visible, objective features which do not suppose as deep cognitive capabilities
 as in the latter case where the agent is implicitly supposed to have
-tastes and preferences such as it can choose a toy as its favorite.
+tastes and preferences such as it can choose a toy as its favourite.
 
-This simple verbal priming (\emph{``brown toy''} \vs \emph{``your favorite
+This simple verbal priming (\emph{``brown toy''} \vs \emph{``your favourite
 toy''}) set the expectations regarding the cognitive capabilities of the robot
@@
 typically took 5 minutes for participants to fill. The results were turned into
-a score noted \anti{} (\emph{initial tendency to anthropomorphize}) following a
+a score noted \anti{} (\emph{initial tendency to anthropomorphise}) following a
 method presented below (section~\ref{questionnaires_processing}).
@@
 
-\subsubsection{Familiarization and Pre-questionnaire}
+\subsubsection{Familiarisation and Pre-questionnaire}
 
@@
 
-We recorded the fixations on each of these zones and normalized them by
-the full duration of the video stimulis and the surface of AOIs between the robot
-and human conditions. We finally analyzed their distribution, producing what we call \emph{gaze
+We recorded the fixations on each of these zones and normalised them by
+the full duration of the video stimuli and the surface of AOIs between the robot
+and human conditions. We finally analysed their distribution, producing what we call \emph{gaze
 patterns}.
@@
 
-\emph{Time} and \emph{Area} are normalized, respectively for the total
+\emph{Time} and \emph{Area} are normalised, respectively for the total
 video length and the total area of the AOIs.
@@
 Questionnaires were coded and two values, the \emph{initial tendency to
-anthropomorphize} \anti{} and the \emph{final tendency to anthropomorphize} \antf{}
+anthropomorphise} \anti{} and the \emph{final tendency to anthropomorphise} \antf{}
 were computed, respectively from the pre- and post-questionnaires.
@@
 
-\subsection{General Biases}
+%\subsection{General Biases}
+First of all, we checked if there were any direct effects of the age, gender, familiarity with robot and robot ownership of the participants on the different aforementioned variables.
+We did not observe any such significant effects.
 
-While testing for all the 4 hypotheses, we observed no significant bias with
-respect to age, gender, familiarity with robot and robot ownership
-of the participants, \ie there was no effects to be found between these factors
-and the other variables of the experiment.
+%While testing for all the 4 hypotheses, we observed no significant bias with
+%respect to age, gender, familiarity with robot and robot ownership
+%of the participants, \ie there was no effects to be found between these factors
+%and the other variables of the experiment.
 
@@
 
-\subsection{Impact of the Tendency to Anthropomorphize on Human
+\subsection{Impact of the Tendency to Anthropomorphise on Human
 Gazing Behaviours}
@@
 correlation between the two quantities (Pearson Correlation Coefficient $r(54) = -0.43,
-p < .001$). The higher the (initial) tendency to anthropomorphize, the smaller
+p < .001$). The higher the (initial) tendency to anthropomorphise, the smaller
 the difference in gazing behaviours between the robot and human conditions. This
@@
     \caption{Gaze distribution difference $\delta_{\mathcal{H},
-    \mathcal{R}}^{\text{gaze}}$ \vs initial tendency to anthropomorphize \anti{}}
+    \mathcal{R}}^{\text{gaze}}$ \vs initial tendency to anthropomorphise \anti{}}
     \label{h2}
@@
 performing simple tasks, participants primed with a deeper cognitive
-expectations report a significantly higher tendency to anthropomorphize robots
+expectations report a significantly higher tendency to anthropomorphise robots
 \emph{in general} (as the questionnaire on anthropomorphic attributions
@@
 already an interesting result: subtle changes in the cognitive priming are
-recognized and clearly interpreted in terms of human-likeness.
+recognised and clearly interpreted in terms of human-likeness.
 
 Hypothesis \h{2} looked at a possible interaction between our tendency to
-anthropomorphize (as measured in the pre-questionnaire) and our actual gaze
-behaviour, the hypothesis being that high anthropomorphizers would show smaller
+anthropomorphise (as measured in the pre-questionnaire) and our actual gaze
+behaviour, the hypothesis being that high anthropomorphisers would show smaller
 differences between the way they look at robots and humans (since they would
-consider robots closer to humans than low anthropomorphizers). Our data supports
-this hypothesis: participants reporting an higher tendency to anthropomorphize
+consider robots closer to humans than low anthropomorphisers). Our data supports
+this hypothesis: participants reporting an higher tendency to anthropomorphise
 tend to have closer gazing behaviours when they look at humans or at robots:
-statistically speaking, the tendency to anthropomorphize robots
+statistically speaking, the tendency to anthropomorphise robots
 is reflected in the way one looks at them: you look at them
@@
 priming, one tends to spend more time looking at the head of the interacting
-agent than after shallow cognitive priming. We also hypothesized that, in turn,
+agent than after shallow cognitive priming. We also hypothesised that, in turn,
 head fixations could act as a \emph{proxy to anthropomorphic projections}: as
@@
 a human, and both should be able to perform them in similar ways (similar pace,
-similar movements) without looking ackward.
+similar movements) without looking awkward.
 
@@
 context that presupposes deeper cognitive capabilities, people increase
-their general tendency to anthropomorphize robots compared to a shallow
+their general tendency to anthropomorphise robots compared to a shallow
 cognitive priming, even though the robot appearance and visual behaviour is the
@@
 
+\newpage
+
+\section {To be discussed}
+
+% new results up for discussion on Skype
+\subsection{Manipulation check - H1}
+
+\begin{table}[ht]
+\caption{Ordinal linear regression table for the manipulation check vs. cognitive context.}
+\centering
+\begin{tabular}{rrrrr}
+  \hline
+ & Value & Std. Error & t value & p value \\ 
+  \hline
+cond low & -2.52 & 0.57 & -4.39 & 0.00 \\ 
+  -2$|$-1 & -4.06 & 0.66 & -6.19 & 0.00 \\ 
+  -1$|$0 & -2.17 & 0.48 & -4.57 & 0.00 \\ 
+  0$|$1 & -1.24 & 0.40 & -3.08 & 0.00 \\ 
+  1$|$2 & 0.05 & 0.35 & 0.15 & 0.88 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+\subsection{Gaze difference vs. \anti levels- H2}
+
+\begin{table}[ht]
+\caption{\anti levels - high, low, neutral}
+\centering
+\begin{tabular}{rrrrr}
+  \hline
+ & diff & lwr & upr & p adj \\ 
+  \hline
+l-h & 0.10 & 0.02 & 0.18 & 0.01 \\ 
+  n-h & 0.03 & -0.10 & 0.17 & 0.80 \\ 
+  n-l & -0.06 & -0.18 & 0.06 & 0.44 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+\subsection{H3- the results remain the same}
+
+One more result in deep (high) cognitive condition the participant stay on the head for longer periods,
+
+We had a comment from the reviewers: 
+`` In addition, you need to address that head fixations to the robot could increase because people are curious whether the robot really has the implied capacities, not because they assume it has them.
+Can you rule out this alternative interpretation?''
+
+they leave other parts of body earlier and leave the head later this might reflect a hypothesis verification by the participants
+
+\begin{table}[ht]
+\caption{transition to and from ``head'' and Duration of looking at head}
+\centering
+\begin{tabular}{rrr}
+  \hline
+ & to & from \\ 
+  \hline
+high & 1441.075(-3.31) & 2646.870(2.62) \\ 
+  low & 1882.956(3.14) & 2670.569(-2.48) \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+MORE TO APPEAR``reported eye tracking results are far too cursory'' - I will put a nice factor analysis of the eye-tracking data with the questionnaire responses and then we can answer many questions in the results section.
+
 \bibliographystyle{apacite}

### 2016-05-04 main.tex
Proof reading intro

@@
 expectations we form about the robot depending on the context: when a machine is
-embedded in a social situation, for instance, we expect it to exhibit certain
-social skills. However, the experiments conducted so far explore prototypical
-opposite situations (routine \vs playful, typically boring \vs typically
+embedded in a social situation, we expect it to exhibit certain
+social skills. The experiments conducted so far only contrast prototypical
+\emph{opposite} interaction situations (routine \vs playful, typically boring \vs typically
 intellectual): while they do confirm that the interaction context impacts our

### 2016-05-09 main.tex
Minor changes

--- 2016-01-26 main.tex
@@
 between the robot and its human partner. As such, a lot of literature in HRI has
-investigated means of measuring anthropomorphism. This indeed raises interesting
-methodological challenges, if only because of high inter-personal variations in
-one's tendency to anthropomorphise~\fixme{ref?}, and the dynamic nature of
+investigated means of measuring anthropomorphism. This indeed raises 
+methodological challenges, due to high inter-personal variations in
+one's tendency to anthropomorphise, and the dynamic nature of
 anthropomorphic attributions~\citep{lemaignan2014dynamics}.
@@
 constructs that are typical or unique of the concept of ``human-likeness'', and
-\citet{ruijten_introducing_2014} propose for instance a 25-item questionnaire to
+\citet{ruijten_introducing_2014} propose for instance a 25-items questionnaire to
 measure various concrete aspects of human-likeness. Other
@@
 skills of a robot and the effective ascription of anthropomorphic features to
-this robot; and \item to this end, can we develop and validate a behavioural and
+this robot; and \item to this end, can we develop and validate a robust behavioural and
 \emph{in-the-moment} metric of anthropomorphism?  \end{inparaenum}
@@
 was guided by the following intuition: \emph{the more we ascribe cognitive
-capabilities to an agent, the more likely we are to focus on its head when
+capabilities to an agent, the more likely we are to focus on its head (\ie the
+brain) when
 interacting with it}, which suggests an eye-tracking-based investigation.

### 2016-05-17 main.tex
Added pre/post questionnaires as appendices
Many changes requested by the editor

@@
 focused on anthropomorphism, is the main validated questionnaire to assess
-anthropomorphism. On 5-points semantic differential scales, people are asked to
+anthropomorphism. On 5-point semantic differential scales, people are asked to
 rate the following constructs: fake \vs natural, machinelike \vs humanlike,
@@
 Secondly, we hypothesise that people with a higher tendency to anthropomorphise
-robots will tend to look at robots and humans in similar ways, contrary to
+robots will tend to physically look at robots and humans in similar ways, contrary to
 people with a lower tendency to anthropomorphise (\h{2}). If this is verified,
@@
 the robot; \h{4} shows that these expectations influence our tendency to
-anthropomorphise robots; in parallel, \h{3} shows that these same expectations
+anthropomorphise robots in general; in parallel, \h{3} shows that these same expectations
 shape the way we look at the robot by eliciting specific eye fixations on the
@@
 
-This study is build as an eye-tracking experiment (using a stationary
+This study is built as an eye-tracking experiment (using a stationary
 eye-tracker SMI RED 250) where participants watch short videos of an agent --
 either a robot (Aldebaran Robotics' Nao) or a human -- performing simple
-task (picking an object or pointing toward a sound source) after being primed.
+tasks (picking an object or pointing toward a sound source) after being primed.
 The priming is designed to elicit either shallow cognitive ascriptions onto the
@@
 
-The study follows a 2$\times$2 design, summarised in table~\ref{table:design}.
+The study follows a 2$\times$2 design, summarised in figure~\ref{table:design}.
 Our two independent variables are the level of cognitive priming (\emph{shallow}
-\vs \emph{deep}) and the nature of the agent appearing in the stimulus (a robot,
-eliciting a \emph{human-robot} interaction situation, or a human, eliciting a
-\emph{human-human} interaction situation).
+\vs \emph{deep}) and the nature of the agent appearing in the stimulus (a robot
+or a human).
 
-\begin{table}[ht!]
+The cognitive priming manipulation is established by having a speaker imply
+different cognitive capacities in the robot.
+
+\begin{figure}[ht!]
     \vspace{2em}
@@
         \draw [decoration={brace,amplitude=0.5em},decorate,thick]
-        ($(left |- bottom)+(1.8,-0.3)$) --  ($(left |- left1.north)+(1.8,0.2)$) node[midway,above=3em,left=1em,rotate=90] {\scriptsize within subject};
+        ($(left |- bottom)+(1.8,-0.3)$) --  ($(left |- left1.north)+(1.8,0.2)$) node[midway,left=1em,rotate=90,anchor=south] {\scriptsize within subject};
     \end{tikzpicture}
@@
     \label{table:design}
-\end{table}
+\end{figure}
 
@@
 
-Four different video stimuli where filmed (figure~\ref{fig:stimuli}): two
+Four different video stimuli were filmed (figure~\ref{fig:stimuli}, see appendix
+for download link): two
 different tasks (picking a stuffed animal, referred hereafter as the
@@
 sets of stimuli: one for the \emph{shallow cognitive priming} condition, one for
-the \emph{deep cognitive priming} condition. The audio editing consisted in
+the \emph{deep cognitive priming} condition. The audio editing consisted of 
 inserting different commands to initiate the tasks (reported in
@@
 \emph{``your favourite toy''}. In the former case, the object was referred through
-visible, objective features which do not suppose as deep cognitive capabilities
-as in the latter case where the agent is implicitly supposed to have
-tastes and preferences such as it can choose a toy as its favourite.
+visible, objective features. They do not presuppose as deep cognitive capabilities
+as in the latter case where the priming is expected to elicit the assumption
+that the robot has tastes and preferences such as it can choose a toy as its favourite.
 
-This simple verbal priming (\emph{``brown toy''} \vs \emph{``your favourite
+This simple verbal prompt (\emph{``brown toy''} \vs \emph{``your favourite
 toy''}) set the expectations regarding the cognitive capabilities of the robot
-(\emph{shallow} \vs \emph{deep}) and was expected to lead to different
-perceptions of the interaction (\emph{machine-like} \vs \emph{human-like}). We
-reinforced this effect in the \emph{Pointing} task: not only the verbal priming
-but also the sound played by the speakers during the task was altered: either a
-repetitive bip (\emph{shallow cognitive priming}) or the sound of a crying baby
-(\emph{deeper cognitive priming}).
+(\emph{shallow} \vs \emph{deep}) and is expected to lead to different
+perceptions of the robot behaviour (\emph{machine-like} \vs \emph{human-like}). We
+reinforced this effect in the \emph{Pointing} task: not only the verbal prompt
+(\emph{``point at the noise''} \vs \emph{``point at the crying baby''}) but also
+the background sound played by the speakers during the task was altered: either a
+repetitive beep (\emph{machine-like} context) or the sound of a crying baby
+(\emph{human-like} context).
 
@@
 Before starting the experiment, the participants were asked to fill a
-pre-questionnaire which had 49 questions (5-point Likert scale). The
-questionnaire comprised of questions assessing their familiarity with robots, 10
+pre-questionnaire (available in appendix) which had 49 questions (5-point Likert scale). The
+questionnaire included questions assessing their familiarity with robots, 10
 items from the \emph{Big-Five} personality questionnaire, 15 questions taken from
@@
 \emph{likeability} and \emph{perceived intelligence}) and 20 questions rating
-human-likeness (from~\cite{ruijten_introducing_2014})\footnote{The
-pre- and post-questionnaires are available online:
-\url{https://github.com/chili-epfl/anthropomorphism-eyetracking}.}. The pre-questionnaire
-typically took 5 minutes for participants to fill. The results were turned into
+human-likeness of robots (from~\cite{ruijten_introducing_2014}). The pre-questionnaire
+typically took 5 minutes for participants to complete. A subset of the results was turned into
 a score noted \anti{} (\emph{initial tendency to anthropomorphise}) following a
@@
 
-The post-questionnaire was administered at the end of the experiment, and was
+The post-questionnaire (available in appendix) was administered at the end of the experiment, and was
 identical to the pre-questionnaire, except that the personality questions were omitted and a
@@
 you watched were more: A robot kind of task ... A human kind of task''}, on a 5
-points scale).
-This questionnaire typically took 3 to 4 minutes to fill. The resulting score is
+point scale -- the phrasing was chosen over more the direct ``Machine-like'' \vs
+``Human-like'' to mitigate the impact of a possible reflective moral judgement
+on human-likeness).
+This questionnaire typically took 3 to 4 minutes to complete. The resulting score is
 noted \antf{} (\emph{final tendency to anthropomorphism}).
@@
 To avoid students with a high familiarity with robots and artificial intelligent
-systems, Computer Science and Electronics curriculum were excluded. This was
-\textit{a posteriori} comforted by the questionnaire responses: no participants
-reported itself as being very familiar with robots, 8 reported some familiarity
+systems, Computer Science and Electronics students were excluded. This was
+\textit{a posteriori} confirmed by the questionnaire responses: no participants
+reported as being very familiar with robots, 8 reported some familiarity
 and 7 out of 56 owned a domestic robot (vacuum cleaner).
 
-As stated previously, the study follows a 2$\times$2 design
+As stated previously, the study followed a 2$\times$2 design
 (table~\ref{table:design}): the \emph{shallow} \vs \emph{deep cognitive priming}
@@
 tasks while 26 were in the \emph{shallow cognitive} condition); the \emph{robot}
-\vs \emph{human} condition was within-subject (the order of stimuli presentation
+\vs \emph{human} condition was within-subject (the order of stimulus presentation
 was counter-balanced over the participants). The study lasted in average 15
@@
 robot appearance, shape and range of motions it could possibly perform, so as to
-mitigate the (visual) novelty of the robot that would lead to hard-to-measure gaze artifacts.
+mitigate the (visual) novelty of the robot that would lead to possible
+gaze artifacts (for instance, gaze fixations on salient peculiarities of the
+robot, like the visible gears, or gaze exploration of the robot's body when the robot
+starts to move).
 
@@
 
-After filling the pre-questionnaire, we conducted a brief eye-tracker
-calibration procedure, and the participants' gaze was recorded while they
+We then presented the stationary eye-tracker, conducted a brief eye-tracker
+calibration procedure (all participants could be successfully tracked), and the participants' gaze was recorded while they
 watched the \emph{robot} and \emph{human} interaction stimuli.
@@
 Before leaving, possible questions on the purpose of the study were
-answered and each participant was given a reward equivalent to EUR 10.
+answered and each participant was given a compensation equivalent to EUR 10.
 
@@
 
-\emph{Time} and \emph{Area} are normalised, respectively for the total
-video length and the total area of the AOIs.
+TBD: editor comment here is correct: "a non-difference can come about as a
+result of many counterveiling differences". He suggests instead "head-to-rest"
+(or "head-to-[arm+hand]") difference for robot vs human
+
+%As the lengths of the human's stimuli are different from the robot's ones, and
+%the visual surface of the human body larger than the robot's, both \emph{Time}
+%and \emph{Area} are normalised, respectively for the video length and the total
+%area of the AOIs.
 
@@
 questions were not used for this study.
+
+TBD: why anthropomorphism and likeability scales?
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=7cm]{ManipulationCheck}
-    \caption{Average ratings for the manipulation check question}
-    \label{fig:ManipulationCheck}
-\end{figure}
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=7cm]{ManipulationCheck}
+%    \caption{Average ratings for the manipulation check question}
+%    \label{fig:ManipulationCheck}
+%\end{figure}
 
 Participants were asked in the post-questionnaire whether the video presented a
-\emph{``robot kind of task''} or a \emph{``human kind of task''} on a 5-points
+\emph{``robot kind of task''} or a \emph{``human kind of task''} on a 5-point
 scale (numerical values ranging from -2 to 2, where -2 refers to robot kind of
-task). As can be seen in figure 2, we got a significant correlation in this
+task). We found a significant mean difference ($M_{shallow}=TBD (SD=TBD)$
+\vs $M_{deep}=TBD (SD=TDB)$) in this
 manipulation check ($F(1,54) = 29.0, p < .001$) which validates our manipulation
-and supports \h{1}: the participants that were shown the \emph{shallow cognitive
-context} videos identified the task as more robot-like and participants watching
-the videos with deeper cognitive priming perceived the tasks as more human-like.
+and supports \h{1}: the participants that watched stimuli with a \emph{shallow cognitive
+priming} identified the task as more robot-like and participants watching
+the videos with a deep cognitive priming perceived the tasks as more human-like.
+
+TBD: editor asks about possible ordering effect
 
@@
 
-We found a significant correlation between
+We found a significant negative correlation between
 $\delta_{\mathcal{H},\mathcal{R}}^{\text{gaze}}$ and
-the \anti{}. As seen in figure~\ref{h2}, there is a significant negative
-correlation between the two quantities (Pearson Correlation Coefficient $r(54) = -0.43,
-p < .001$). The higher the (initial) tendency to anthropomorphise, the smaller
+the initial tendency to anthropomorphise \anti{} (Pearson Correlation Coefficient $r(54) = -0.43,
+p < .001$, figure~\ref{h2}). The higher the (initial) tendency to anthropomorphise, the smaller
 the difference in gazing behaviours between the robot and human conditions. This
@@
 torso} and {\sf legs} (the left and right arms, hands and legs are grouped
-together). Based on ANOVA results for the robot in both the shallow and deep
+together, other AOIs not belonging to the robot are left out). Based on ANOVA results for the robot in both the shallow and deep
 cognitive priming conditions, the fixations on the head in the deep condition
@@
     \includegraphics[width=0.6\columnwidth]{GazeHighLow}\label{GazeHighLow}
-    \caption{Gaze fixations on the different areas on interest, for shallow \vs
-    deep cognitive priming conditions.}
+    \caption{Gaze fixations on the different areas on interest of the robot, for shallow \vs
+    deep cognitive priming conditions. TBD: what do the error bar represent?}
     \label{h3}
@@
 
-This constitutes the main result of this study: inducing a deeper cognitive
-context for the same interaction suffices to lead to significantly longer
-fixations on the agent's head (hypothesis \h{3}).
+TBD: add plot human condition
+
+This constitutes the main novel result of this study: priming an observer with a deeper cognitive
+context for the same interaction situation suffices to lead to significantly longer
+fixations on the robot's head (hypothesis \h{3}).
 
@@
 
-\subsection{Correlation Between Cognitive Priming and Changes in Anthropomorphic
+\subsection{Impact of Cognitive Priming on Changes in Anthropomorphic
 Attributions}
@@
 
-%\appendix
+\pagebreak
+\appendix
+
+\section{Appendices}
+
+The video stimuli, questionnaires results, eye-tracking data and R scripts for
+the analysis are all available at
+\url{https://github.com/chili-epfl/anthropomorphism-eyetracking}.
+
+The pre- and post-questionnaires are reproduced hereafter.
+\vfill
+\pagebreak
+\paragraph{Pre-questionnaire} (2 pages)
+
+\begin{center}
+    \includegraphics[width=0.9\linewidth]{pre-questionnaire}
+
+    \includegraphics[width=0.9\linewidth, page=2]{pre-questionnaire}
+\end{center}
+
+\pagebreak
+\paragraph{Post-questionnaire} (2 pages)
+
+\begin{center}
+    \includegraphics[width=0.9\linewidth]{post-questionnaire}
+
+    \includegraphics[width=0.9\linewidth, page=2]{post-questionnaire}
+\end{center}
 %\includepdf[pages={1,2}]{pre-questionnaire.pdf}

### 2016-05-17 rebuttal.tex
First bits of the rebuttal

\documentclass{article}
\usepackage[utf8]{inputenc}

\begin{document}

Dear Editor, Dear Reviewers,

\vspace{2em}

We would like first to thank the editor and the reviewers for their thorough review of our
work. The manuscript underwent significant changes: we have hopefully addressed most of
the reviewers' concerns, and we discuss hereafter the remaining points.

The core points raised by the editors were the following:

\begin{itemize}
    \item \emph{Lack of theoretical background for the concept of "cognitive
        context"}: we take this point, and have reframed our theoretical
        background around "cognitive priming". Section 1.1 accordingly provides
        the literature references and precisely define our shallow vs deep
        conditions.
    \item \emph{Validity of the manipulation check} TBD
    \item \emph{Missing material}: We have appended the pre- and
        post-questionnaires to the manuscript appendices. We have as well added
        a link to the video stimuli, and eye-tracking and questionnaires
        results.
    \item \emph{Cursory eye-tracking results}: we have significantly expanded
        our reporting of eye-tracking results [TBD add details]
    \item \emph{Curiosity about cognitive skills vs actual ascription of cognitive
        skills}: one question raised concerns whether the participants are
        actually ascribing cognitive capacities to the robot, or merely curious
        whether the robot has them or not. While our approach does not
        intrinsically allow to rule out one or the other of these
        interpretations, we argue that this issue is to be observed in virtually
        any short-term human-robot interaction: as we previously
        argued~\cite{lemaignan2014cognitive}, the initial human-robot cognitive
        familiarisation period is basically about restating and iteratively
        shaping a mental model of the robot. During that period of time,
        anthropomorphic \emph{projections} are likely not yet anthropomorphic
        \emph{ascriptions}, and any investigation of anthropomorphism at this
        stage is subject to this double interpretation ``curiosity'' vs
        ``ascription''. In order to rule out one of the interpretation,
        longer-term observations (once the novelty effect has vanished) are
        needed, which could be relatively easily conducted with our method (by
        relying on non-intrusive gaze tracking techniques). [TBD: Kshitij
        argument]
    \item \emph{Use of the concept of proxy}: Using the term ``proxy'' was a
        mistake, rightfully pointed by the editor. This has been removed from
        the text.

\end{itemize}

The introduction of the article has been largely rewritten, to better frame our
work, and to clarify our working hypotheses.

We have as well attempted to address individually each of the other concerns
raised by the reviewers in this document (note that minor typos/style issues
have been fixed directly in the manuscript, and are not discussed here).

\section{Comments from Editor}

We list hereafter the main points raised by the editor (the other ones, omitted
here for brevity, have been directly addressed in the text):

\begin{itemize}
    \item \emph{Computation of the gazing differences between the human and the
        robot conditions}: TBD
    \item \emph{Choice of the questionnaire result subset}: TBD
    \item \emph{Possible ordering effect in the manipulation check}: TBD
    \item \emph{Interpretation of the head fixation in the 'deep cognitive
        priming' condition}: the editor suggests that the interpretation of the
        head focus in terms of higher anthropomorphic ascriptions onto the robot
        depends on the meaningfulness of such a head focus for a human. As noted
        in the paper, we did not observed significant differences in fixations
        on the human head between the shallow and deep cognitive conditions. We
        interpret this absence of difference as the result of the mere presence
        of a human being: because of the human presence, the two conditions
        (deep vs shallow) do not elicit anymore a significantly different perception of
        the situation as being machine-like or human-like. As such
        such a strong intrinsic source of

\end{itemize}

All the other grammar and style errors pointed by the editor have been addressed.

\bibliographystyle{abbrv}
\bibliography{biblio}

\end{document}

### 2016-05-18 main.tex
Cognitive priming
Added some studies about priming and rationale for the deep and shallow
priming.

@@
 
-\textbf{TBD: Kshitij} at the end of this section, the reader must be convinced
-that:
-\begin{itemize}
-    \item cognitive priming is a well established technique, grounded in the
-        literature,
-    \item our terminology ('shallow' vs 'deep') is meaningful, and grounded
-    \item our cognitive priming would impact the perception of the interaction
-        situation as machine-like vs human-like (to support our manipulation
-        check!)
-\end{itemize}
+Previous studies had shown that cognitive and/or affective priming influences human perception of the input stimulus.
+\cite{zajonc1980feeling} advocated the the use of affective priming and proposed that the affective reactions can be elicited with minimal stimulated input.
+As \cite{murphy1993affect} wrote \textit{``The experimental paradigm of priming, involves the presentation of one stimulus, or prime, alters subjects' perceptions of a second target stimulus...''}  \cite{murphy1993affect} found in their series of studies, where the subjects were shown happy and angry faces of people as a priming method, showed that the subjects' perceptions of positive emotions were higher and quicker when the priming was a happy face than for those who were primed with a angry face.
+The gender of the priming faces, however had no effect on the subjects' perception.
+
+\cite{forgas1987mood} showed that priming subjects with positive or negative moods affects their person-perception judgement\footnote{Person-perception judgement is a task where the subjects are asked to read a few characteristics of an unknown person; and once they have read the description the subjects are then asked to provide their perception about the target person}.
+In their study, \cite{forgas1987mood} showed used a bogus test with manipulated positive or negative feedback to prime the mood of the subjects in a positive or negative manner.
+Once the subjects were primed with a particular mood they were shown the descriptions of some unknown persons (with the same positive and negative characteristics).
+The results showed that the mood priming influences their person-perception, i.e, the positively primed subjects gave more positive remarks about the target perception while the negatively primed subjects gave more negative remarks.
+Moreover, the subjects in both the priming conditions spent more time on the priming specific characteristics (positive or negative).
+This shows that not only subjects' perception was altered but also their approach as well using the mood priming.
+
+\cite{yi1990cognitive} used specific attributes of a car to prime subjects' before they watched an advertisement about cars.
+The advertisement focused on explains various characteristics of a few imaginary cars in terms of the safety and the fuel efficiency.
+The priming stimulus had the size of the cars manipulated.
+The results showed that tone (affective priming) and size (cognitive priming) affects the favourability of the cars.
+For example, a big car was perceived to be more ``safe'' and less ``fuel-efficient'' than the small cars.
+
+\cite{tillmann2006cognitive}, in an fMRI study with music notes, showed that different parts of the frontal cortex gets activated when the participants were primed with sung or instrumental music.
+In their experiment, the subjects were asked to listen the first seven notes in either sung or instrumental manner (cognitive priming) and then to identify the relation between the first seven and the eighth note.
+The results showed that the subjects showed a higher activation in the inferior frontal cortex when primed with the sung notes than when they were primed with the instrumental notes.
+\cite{rholes1987emotional} showed that the memory recall is affected by the tone (affective priming) of the self-evaluation statement.
+In an experiment, where the subjects were given a set of positive or negative self-evaluation statements before being asked to recall a few good and bad memories from their past, the subjects were faster in recalling good memories when they were given a positive self-evaluation test; and vice-versa.
+
+All the above studies show that the cognitive and/or affective priming might alter the behaviour and/or the perception of the subjects about a target stimulus.
+Some of the studies found some complex interactions between cognitive and affective priming (\cite{yi1990cognitive} and \cite{storbeck2008affective} ).
+In this contribution, we were only interested in the cognitive priming aspect during a Human Robot Interaction situation, as \cite{baldwin1990priming} advocated that the cognitive priming may activate a relationship schema between the priming stimulus and the target stimulus.
+Moreover, in the context of advertisement, a number of studies suggest that the ad context (cognitive priming) can influence the audience's perception of the ad, and thus, its effectiveness (e.g., \cite{singh1987arousal};\cite{soldow1981response})  Our primary hypothesis was that the way the robot is given commands might alter the way the subjects perceive its actions.
+We propose to use a neutral mood (no affective priming) and two cognitive priming conditions (Deep and Shallow), in order to remove the ``mood'' or  ``affect'' bias of the priming.
+The ``shallow'' priming consisted of giving commands to the robot which are more ``machine-like''.
+On the other hand, the ``deep'' priming had the commands to robot in a more ``human-like'' manner (Manipulation-check hypothesis).
+We also kept the time of priming to be the same in the deep and shallow conditions, in order to remove the time of priming effect on the subjects' perceptions about the robot.
 
@@
 conditions, shows that \deltaant is greater for tasks with a deeper cognitive
-context than that for the shallow cognitive tasks ($F(1,54) = 6.54, p <
-.05$\fixme{put the exact p value here},
-figure~\ref{h4}). In other words, after being exposed to short videos of a robot
+context than that for the shallow cognitive tasks ($\Delta_{shallow}=TBD (SD=TBD)$
+\vs $\Delta_{deep}=TBD (SD=TDB)$, $F(1,54) = 6.54, p < .05$\fixme{put the exact
+p value here}). In other words, after being exposed to short videos of a robot
 performing simple tasks, participants primed with a deeper cognitive
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}
-    \caption{Difference between \anti{} and \antf{} in the shallow and deep
-    cognitive priming conditions.}
-    \label{h4}
-\end{figure}
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}
+%    \caption{Difference between \anti{} and \antf{} in the shallow and deep
+%    cognitive priming conditions.}
+%    \label{h4}
+%\end{figure}
 
-This result supports \h{4} and validate that the cognitive priming impacts the
-attribution of anthropomorphic features to robots. This, in turn, supports the
-\emph{proxy} hypothesis of \h{3}: \emph{head fixations are a proxy for higher
-levels of human-likeness attributions}.
+This result supports \h{4}: cognitive priming impacts the
+attribution of anthropomorphic features to robots \emph{beyond the specific Nao robot
+shown in the stimuli}.  It appears that participants transfer to some extent the
+cognitive capabilities that they ascribe to the Nao robot in the
+\emph{deep} cognitive condition to ``robots'' in general (we can not, however,
+conclude on any possible \emph{lasting} anthropomorphic ascriptions to robots as we
+measure the anthropomorphic perception immediately after the experiment).
 

### 2016-08-30 main.tex
Some old proof-reading

--- 2016-05-18 main.tex
@@
 These two questions translate into several experimental hypotheses, whose design
-was guided by the following intuition: \emph{the more we ascribe cognitive
+was guided by the following high-level hypothesis: \emph{the more we ascribe cognitive
 capabilities to an agent, the more likely we are to focus on its head (\ie the
-brain) when
-interacting with it}, which suggests an eye-tracking-based investigation.
+brain) when interacting with it}. As such, this hypothesis naturally suggests an
+eye-tracking-based investigation.
 
@@
 Our baseline hypothesis \h{1} is that cognitive priming allows us to effectively create
-stimuli that induce \emph{shallow} or \emph{higher} expectations regarding the
-cognitive skills of the robot. This hypothesis is to be tested by asking
+stimuli that induce \emph{lower} or \emph{higher} attribution of human-likeness
+to the robot. This hypothesis can be tested by asking
 participants to rate the interactions depicted by the stimuli as being more
-\emph{machine-like} (low ascription of cognitive skills) or \emph{human-like}
-(higher expectation of cognitive competency).
+\emph{machine-like} or \emph{human-like}.
 
@@
 
-Third, we hypothesise that in the \emph{human-like} condition (higher ascription
-of cognitive skills to the robot), the participants' gaze will be directed
+Third, we hypothesise that in the \emph{human-like} condition (which we
+interpret as well as a higher ascription of cognitive skills to the robot), the participants' gaze will be directed
 significantly more towards the head of the robot than in the \emph{machine-like}
-condition (low ascription of cognitive skills) (\h{3}). If verified, it
+condition (interpreted as a lower ascription of cognitive skills) (\h{3}). If verified, it
 effectively means that the expectations held by the participants regarding the
@@
 
-\subsection{Discussion of the Results}
-
-The presented results bring some light on our initial hypotheses.
-
-The significant correlation between deep \vs shallow conditions and the
-answers to the question \emph{Were the task more robot-like or human-like?}
-shows that our manipulation was successful, and that a shallow cognitive
-context was indeed associated to a robot-like situation, while a deeper
-cognitive priming was associated to a human-like situation (\h{1}). This is
-already an interesting result: subtle changes in the cognitive priming are
-recognised and clearly interpreted in terms of human-likeness.
+The significant impact of the deep \vs shallow commands implication on the
+answers to the question \emph{Were the tasks more robot-like or human-like?}
+shows that our manipulation was well recognized, and that a shallow cognitive
+context was indeed perceived to elicit a ``robot-like'' situation, while a deeper
+cognitive priming was perceived as a ``human-like'' situation. This supports our
+ifirst hypothesis \h{1}: even indirect hints at the cognitive capabilities of a robot are
+sufficient to elicit significantly increased attribution of human-likeness.
 

### 2016-08-30 main.tex
Proof-reading/rephrasing intro

@@
 another mechanism at play, less obvious because partially unconscious: the
-cognitive skills that the interaction situation presupposes.
+cognitive skills that the interaction situation \emph{presupposes}.
 
 We show that humans appear quite sensitive to this effect:
-even subtle context priming is sufficient to elicit significantly different
+even subtle cognitive priming is sufficient to elicit significantly different
 anthropomorphic attributions, and as such, this article provides new insights on
@@
 the resulting gaze patterns with answers to established questionnaires on
-anthropomorphic attributions, we show that fixations on the head of the robot
-indeed reflect how we anthropomorphize the machine.
+anthropomorphic attributions, we further show that fixations on the head of the robot
+reflect how we anthropomorphize the machine.
 
@@
 
-Being such a central ingredient of the psychological ``sauce'' that binds humans to
-robots, the field of human-robot interaction (HRI) has long
-attempted to manipulate the anthropomorphic attributes we ascribe to robots.
+Being a rich, compound trait that characterises the bonds between humans
+and robots, the field of human-robot interaction (HRI) has long
+attempted to assess and manipulate the anthropomorphic attributes we ascribe to robots.
 While modifying the anthropomorphic \emph{design} of robots is conceptually
@@
 routine or focused, serious situations (security, rescue, \etc).
-\citet{joosse_what_2013} showed, for instance, that users would ascribe
+\citet{joosse_what_2013} showed for instance that users would ascribe
 different personalities to the same robot (a {\sc nao} humanoid) when it was
@@
 in a sense that they do not provide any kind of service, and this very aspect
-may increase people's tendency to anthropomorphise them.
+increases people's tendency to anthropomorphise them.
 
@@
 embedded in a social situation, we expect it to exhibit certain
-social skills. The experiments conducted so far only contrast prototypical
+social skills. The experiments found so far in the literature contrast prototypical
 \emph{opposite} interaction situations (routine \vs playful, typically boring \vs typically
@@
 to finely analyse the psychological determinants that explain the different
-perception of the robot. In particular, existing
-techniques to measure anthropomorphism traditionally rely on questionnaires that
-may suffer post-hoc reconstruction (we further discuss this point hereafter).
+perception of the robot. This is made worst by the common reliance on
+questionnaires to measure anthropomorphism, with the associated issue of
+post-hoc reconstruction (we elaborate on this hereafter).
 
-This article attempts to address this issue with a different experimental design
-and a novel methodology to measure \emph{in-the-moment} anthropomorphic attributions.
-Our approach is built on a combination of cognitive priming and eye-tracking,
-and evidences specific gaze fixations on the head of the robot when the
-participants are primed with higher expectations regarding the cognitive skills
-of the robot. This methodology leads us next to uncover and evidence the significant
-impact of even subtle contextual cues on humans' tendency to ascribe human
-traits to machines.
+This article attempts to address the issue with a different experimental design
+and a novel methodology to measure \emph{in-the-moment} anthropomorphic
+attributions.  Our approach is built on a combination of cognitive priming and
+eye-tracking. By doing so, we evidence specific gaze fixations on the head
+of the robot when the participants are primed with higher expectations
+regarding the cognitive skills of the robot. We then establish the link
+between head fixations and anthropomorphic ascriptions, to eventually show how
+subtle interaction manipulations do significantly impact our tendency
+to ascribe human traits to machines.
 

### 2016-09-02 main.tex
{shallow/deep -> machine-like/human-like} + {A0/A1 -> Astart/Aend}

@@
 
-\newcommand{\anti}{{$\mathcal{A}_0$\xspace}}
-\newcommand{\antf}{{$\mathcal{A}_1$\xspace}}
-\newcommand{\deltaant}{{ $\Delta_{\mathcal{A}_0,\mathcal{A}_1}$\xspace}}
+\newcommand{\anti}{{$\mathcal{A}_{start}$\xspace}}
+\newcommand{\antf}{{$\mathcal{A}_{end}$\xspace}}
+\newcommand{\deltaant}{{$\Delta_{\mathcal{A}}$\xspace}}
 
@@
 Moreover, in the context of advertisement, a number of studies suggest that the ad context (cognitive priming) can influence the audience's perception of the ad, and thus, its effectiveness (e.g., \cite{singh1987arousal};\cite{soldow1981response})  Our primary hypothesis was that the way the robot is given commands might alter the way the subjects perceive its actions.
-We propose to use a neutral mood (no affective priming) and two cognitive priming conditions (Deep and Shallow), in order to remove the ``mood'' or  ``affect'' bias of the priming.
-The ``shallow'' priming consisted of giving commands to the robot which are more ``machine-like''.
-On the other hand, the ``deep'' priming had the commands to robot in a more ``human-like'' manner (Manipulation-check hypothesis).
-We also kept the time of priming to be the same in the deep and shallow conditions, in order to remove the time of priming effect on the subjects' perceptions about the robot.
+We propose to use a neutral mood (no affective priming) and two cognitive priming conditions (Human-like and Machine-like), in order to remove the ``mood'' or  ``affect'' bias of the priming.
+The ``machine-like'' priming consisted of giving commands to the robot which are more ``machine-like''.
+On the other hand, the ``human-like'' priming had the commands to robot in a more ``human-like'' manner (Manipulation-check hypothesis).
+We also kept the time of priming to be the same in the human-like and machine-like conditions, in order to remove the time of priming effect on the subjects' perceptions about the robot.
 
@@
 eye-tracker SMI RED 250) where participants watch short videos of an agent --
-either a robot (Aldebaran Robotics' Nao) or a human -- performing simple
-tasks (picking an object or pointing toward a sound source) after being primed.
-The priming is designed to elicit either shallow cognitive ascriptions onto the
-robot (leading to a \emph{machine-like} situation) or deeper cognitive
-ascriptions (leaning toward a \emph{human-like} situation).
+either a robot (Aldebaran Robotics' Nao) or a human -- performing simple tasks
+(picking an object or pointing toward a sound source) after being primed.  The
+priming is designed to elicit either low cognitive ascriptions onto the robot
+(leading to what we call hereafter a \emph{machine-like} interaction situation)
+or richer cognitive ascriptions (leaning toward what we call a \emph{human-like}
+interaction situation).
 
@@
 The study follows a 2$\times$2 design, summarised in figure~\ref{table:design}.
-Our two independent variables are the level of cognitive priming (\emph{shallow}
-\vs \emph{deep}) and the nature of the agent appearing in the stimulus (a robot
+Our two independent variables are the level of cognitive priming (\emph{machine-like}
+\vs \emph{human-like}) and the nature of the agent appearing in the stimulus (a robot
 or a human).
@@
     \begin{tabular}{l|p{4cm}|p{4cm}}
-        & \tikzmark{top1} Shallow cognitive priming & Deep cognitive priming \tikzmark{top2}  \\
+        & \tikzmark{top1} Machine-like cognitive priming & Human-like cognitive priming \tikzmark{top2}  \\
         \hline
@@
     \caption{\small The study follows a 2$\times$2 design: the \emph{robot} vs
-        \emph{human} condition is within subject, while the \emph{shallow
-        cognitive priming} \vs \emph{deep cognitive priming} is between subjects.
+        \emph{human} condition is within subject, while the \emph{machine-like
+        cognitive priming} \vs \emph{human-like cognitive priming} is between subjects.
         Two stimuli (\emph{Picking} task, {\bf A}, and \emph{Pointing} task,
@@
 The audio (and audio only) of these four videos was then edited to create two
-sets of stimuli: one for the \emph{shallow cognitive priming} condition, one for
-the \emph{deep cognitive priming} condition. The audio editing consisted of 
+sets of stimuli: one for the \emph{machine-like cognitive priming} condition, one for
+the \emph{human-like cognitive priming} condition. The audio editing consisted of 
 inserting different commands to initiate the tasks (reported in
@@
 \emph{``your favourite toy''}. In the former case, the object was referred through
-visible, objective features. They do not presuppose as deep cognitive capabilities
+visible, objective features. They do not presuppose as complex cognitive capabilities
 as in the latter case where the priming is expected to elicit the assumption
@@
 This simple verbal prompt (\emph{``brown toy''} \vs \emph{``your favourite
-toy''}) set the expectations regarding the cognitive capabilities of the robot
-(\emph{shallow} \vs \emph{deep}) and is expected to lead to different
-perceptions of the robot behaviour (\emph{machine-like} \vs \emph{human-like}). We
-reinforced this effect in the \emph{Pointing} task: not only the verbal prompt
-(\emph{``point at the noise''} \vs \emph{``point at the crying baby''}) but also
-the background sound played by the speakers during the task was altered: either a
-repetitive beep (\emph{machine-like} context) or the sound of a crying baby
-(\emph{human-like} context).
+toy''}) creates a set of expectations regarding the cognitive capabilities of
+the robot and leads to a different perceptions of the interaction situation (the
+task performed by the robot is seen by the participant as more
+\emph{machine-like} or more \emph{human-like}). We reinforced this effect in the
+\emph{Pointing} task: not only the verbal prompt (\emph{``point at the noise''}
+\vs \emph{``point at the crying baby''}) but also the background sound played by
+the speakers during the task was altered: either a repetitive beep
+(\emph{machine-like} situation) or the sound of a crying baby (\emph{human-like}
+situation).
 
@@
 As stated previously, the study followed a 2$\times$2 design
-(table~\ref{table:design}): the \emph{shallow} \vs \emph{deep cognitive priming}
-condition was between-subjects (30 participants performed the \emph{deep cognitive}
-tasks while 26 were in the \emph{shallow cognitive} condition); the \emph{robot}
+(table~\ref{table:design}): the \emph{machine-like} \vs \emph{human-like cognitive priming}
+condition was between-subjects (30 participants performed the \emph{human-like cognitive}
+tasks while 26 were in the \emph{machine-like cognitive} condition); the \emph{robot}
 \vs \emph{human} condition was within-subject (the order of stimulus presentation
@@
     \frac{\sum\limits_{{\text{{\sc aoi}s}}}\left |
-    \frac{\text{Time}_{\text{Human}}^{\text{\sc
+    \frac{\text{Duration}_{\text{Human}}^{\text{\sc
 aoi}}}{\text{Area}_{\text{Human}}^{\text{\sc aoi}}} -
-\frac{\text{Time}_{\text{Robot}}^{\text{\sc
+\frac{\text{Duration}_{\text{Robot}}^{\text{\sc
 aoi}}}{\text{Area}_{\text{Robot}}^{\text{\sc aoi}}} \right |}{N}
@@
 Based on the experiments conducted on 56 participants in the human and robot
-interactions across \emph{shallow} and \emph{deep cognitive priming} conditions,
+interactions across \emph{machine-like} and \emph{human-like cognitive priming} conditions,
 we have the following results.\footnote{The detailed statistics and code used
@@
 scale (numerical values ranging from -2 to 2, where -2 refers to robot kind of
-task). We found a significant mean difference ($M_{shallow}=TBD (SD=TBD)$
-\vs $M_{deep}=TBD (SD=TDB)$) in this
+task). We found a significant mean difference ($M_{\text{machine-like}}=TBD (SD=TBD)$
+\vs $M_{\text{human-like}}=TBD (SD=TDB)$) in this
 manipulation check ($F(1,54) = 29.0, p < .001$) which validates our manipulation
-and supports \h{1}: the participants that watched stimuli with a \emph{shallow cognitive
+and supports \h{1}: the participants that watched stimuli with a \emph{machine-like cognitive
 priming} identified the task as more robot-like and participants watching
-the videos with a deep cognitive priming perceived the tasks as more human-like.
+the videos with a human-like cognitive priming perceived the tasks as more human-like.
 
@@
 
-\subsection{Gaze Behaviours in Response to Shallow \vs Deep Cognitive Priming}
+\subsection{Gaze Behaviours in Response to Machine-like \vs Human-like Cognitive Priming}
 
@@
 torso} and {\sf legs} (the left and right arms, hands and legs are grouped
-together, other AOIs not belonging to the robot are left out). Based on ANOVA results for the robot in both the shallow and deep
-cognitive priming conditions, the fixations on the head in the deep condition
-were found to be significantly higher than that in the shallow condition
+together, other AOIs not belonging to the robot are left out). Based on ANOVA results for the robot in both the machine-like and human-like
+cognitive priming conditions, the fixations on the head in the human-like condition
+were found to be significantly higher than that in the machine-like condition
 ($F(1,54) = 4.2, p < .05$\fixme{put the exact p value here}). For all other AOIs groups, the fixations across
-shallow and deep conditions were almost the same. Figure~\ref{h3} shows the
+machine-like and human-like conditions were almost the same. Figure~\ref{h3} shows the
 distribution of proportion of time spent gazing on the 5 AOI groups for the two
@@
     \includegraphics[width=0.6\columnwidth]{GazeHighLow}\label{GazeHighLow}
-    \caption{Gaze fixations on the different areas on interest of the robot, for shallow \vs
-    deep cognitive priming conditions. TBD: what do the error bar represent?}
+    \caption{Gaze fixations on the different areas on interest of the robot, for machine-like \vs
+    human-like cognitive priming conditions. TBD: what do the error bar represent?}
     \label{h3}
@@
 
-This constitutes the main novel result of this study: priming an observer with a deeper cognitive
-context for the same interaction situation suffices to lead to significantly longer
-fixations on the robot's head (hypothesis \h{3}).
+This constitutes the main novel result of this study: priming an observer with
+the expectation of a robot endowed with richer cognitive abilities leads to significantly longer
+fixations on the robot's head, even though the actual behaviour of the robot is
+the same (hypothesis \h{3}).
 
 Note that we only analysed these possible correlations for robot condition: in
-the human condition, the presence of the human is intrinsically a source of deep
-cognitive expectations, hiding the effects of our manipulation on a shallow \vs deep
-cognitive priming.
+the human condition, the presence of the human is intrinsically a source of rich
+cognitive expectations, masking the effects of our manipulation on a
+machine-like \vs human-like cognitive priming.
 
@@
 (\deltaant) over the duration of the experiment in the two cognitive
-conditions, shows that \deltaant is greater for tasks with a deeper cognitive
-context than that for the shallow cognitive tasks ($\Delta_{shallow}=TBD (SD=TBD)$
-\vs $\Delta_{deep}=TBD (SD=TDB)$, $F(1,54) = 6.54, p < .05$\fixme{put the exact
+conditions, shows that \deltaant is greater for the participants who watched the
+human-like tasks ($\Delta_{\text{machine-like}}=TBD (SD=TBD)$
+\vs $\Delta_{\text{human-like}}=TBD (SD=TDB)$, $F(1,54) = 6.54, p < .05$\fixme{put the exact
 p value here}). In other words, after being exposed to short videos of a robot
-performing simple tasks, participants primed with a deeper cognitive
-expectations report a significantly higher tendency to anthropomorphise robots
+performing simple tasks, participants primed with a richer cognitive
+expectations regarding the robot report a significantly higher tendency to anthropomorphise robots
 \emph{in general} (as the questionnaire on anthropomorphic attributions
@@
 %    \includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}
-%    \caption{Difference between \anti{} and \antf{} in the shallow and deep
+%    \caption{Difference between \anti{} and \antf{} in the machine-like and
+%    human-like
 %    cognitive priming conditions.}
@@
 cognitive capabilities that they ascribe to the Nao robot in the
-\emph{deep} cognitive condition to ``robots'' in general (we can not, however,
+\emph{human-like} cognitive condition to ``robots'' in general (we can not, however,
 conclude on any possible \emph{lasting} anthropomorphic ascriptions to robots as we
@@
 
-The significant impact of the deep \vs shallow commands implication on the
-answers to the question \emph{Were the tasks more robot-like or human-like?}
-shows that our manipulation was well recognized, and that a shallow cognitive
-context was indeed perceived to elicit a ``robot-like'' situation, while a deeper
+The significant impact of the machine-like \vs human-like conditions on the
+answers to the question \emph{Were the tasks more ``a robot kind of task'' or
+``a human kind of task''?} shows that our manipulation was effective: framing
+the interaction situation to induce a machine-like or a human-like task context
+was successful.
+
+situation priming the participants with , and that a machine-like cognitive
+context was indeed perceived to elicit a ``robot-like'' situation, while a
+human-like
 cognitive priming was perceived as a ``human-like'' situation. This supports our
-ifirst hypothesis \h{1}: even indirect hints at the cognitive capabilities of a robot are
+first hypothesis \h{1}: even indirect hints at the cognitive capabilities of a robot are
 sufficient to elicit significantly increased attribution of human-likeness.
@@
 The third hypothesis \h{3} proposes that head fixations are related to the
-cognitive expectations, which is clearly supported by our data: after deeper cognitive
+cognitive expectations, which is clearly supported by our data: after human-like cognitive
 priming, one tends to spend more time looking at the head of the interacting
-agent than after shallow cognitive priming. We also hypothesised that, in turn,
+agent than after machine-like cognitive priming. We also hypothesised that, in turn,
 head fixations could act as a \emph{proxy to anthropomorphic projections}: as
@@
 projections, with the hypothesis that watching an interaction with a particular
-robot after a deeper cognitive priming may impact \emph{globally} the
+robot after a human-like cognitive priming may impact \emph{globally} the
 anthropomorphic perceptions of robots. This is supported by our study.
@@
 Finally, the situations needed to support two possible kind of cognitive priming
-(shallow \vs deeper cognitive priming), and triggering one or the other of these
+(machine-like \vs human-like cognitive priming), and triggering one or the other of these
 contexts needed to be done \emph{without changing} the visual part of the
@@
 \emph{Pointing} task and a \emph{Dance} task.  During the \emph{Dance} task, the
-agent was either asked to \emph{``Show some movements''} (\emph{shallow
+agent was either asked to \emph{``Show some movements''} (\emph{machine-like
 cognitive priming} condition) or to \emph{``Dance with the music''}
-(\emph{deeper cognitive priming} condition). While all the participants were
+(\emph{human-like cognitive priming} condition). While all the participants were
 shown this stimuli as well, we decided to exclude it from the results as we
@@
 evolves in significantly different ways. After observing a robot in a
-context that presupposes deeper cognitive capabilities, people increase
-their general tendency to anthropomorphise robots compared to a shallow
+context that presupposes richer cognitive capabilities, people increase
+their general tendency to anthropomorphise robots compared to a machine-like
 cognitive priming, even though the robot appearance and visual behaviour is the

### 2016-09-02 main.tex
Changed title + intro to focus on 'head gaze => anthropo'

@@
 
-\rightheader{Shaping the Perception of a Robot by Cognitive Priming}   % This should be the title, or a shortened version of the title if your title is long.
+\rightheader{Gaing at the Robot's Head Reflects our Tendency to Anthropomorphise}   % This should be the title, or a shortened version of the title if your title is long.
 \leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
-\title{Shaping the Perception of a Robot by Cognitive Priming}
+\title{Gazing at the Robot's Head Reflects our Tendency to Anthropomorphise}
 
@@
 \abstract{
-What leads us to perceive robots as human-like agents? The physical appearance
-of the robot and the design of its behaviours (the anthropomorphic \emph{design}
-of the robot) do certainly play an important role. This paper sheds light on
-another mechanism at play, less obvious because partially unconscious: the
-cognitive skills that the interaction situation \emph{presupposes}.
-
-We show that humans appear quite sensitive to this effect:
-even subtle cognitive priming is sufficient to elicit significantly different
-anthropomorphic attributions, and as such, this article provides new insights on
-how our expectations of the robot's cognitive competency shape the bonds that we
-build with the machine.
-
-We evidence the effect with a novel methodology based on eye-tracking
-and a set of stimuli that are visually identical and yet induce different
-assumptions regarding the cognitive capabilities of the robot. By correlating
-the resulting gaze patterns with answers to established questionnaires on
-anthropomorphic attributions, we further show that fixations on the head of the robot
-reflect how we anthropomorphize the machine.
+
+Could the way we look at robots betray our anthropomorphic ascriptions to the
+machine? We show in the article that indeed, the duration of gaze fixations on
+the head of a humanoid robot reflects one's tendency to anthropomorphise the
+robot.  We reach this conclusion by building on an novel experimental protocol
+involving cognitive priming: participants are shown a set of stimuli that are
+visually identical and yet induce different assumptions regarding the cognitive
+capabilities of the robot. By correlating the resulting gaze patterns with
+answers to established questionnaires on anthropomorphic attributions, we show
+that fixations on the head of the robot reflect how we anthropomorphize the
+machine. Besides, by comparing this gazing behaviour to a human baseline, we further
+show that people with a generally higher tendency to anthropomorphise exhibit
+similar gaze patterns when they look either at humans or robots.
 
@@
 
-Previous studies had shown that cognitive and/or affective priming influences human perception of the input stimulus.
-\cite{zajonc1980feeling} advocated the the use of affective priming and proposed that the affective reactions can be elicited with minimal stimulated input.
-As \cite{murphy1993affect} wrote \textit{``The experimental paradigm of priming, involves the presentation of one stimulus, or prime, alters subjects' perceptions of a second target stimulus...''}  \cite{murphy1993affect} found in their series of studies, where the subjects were shown happy and angry faces of people as a priming method, showed that the subjects' perceptions of positive emotions were higher and quicker when the priming was a happy face than for those who were primed with a angry face.
-The gender of the priming faces, however had no effect on the subjects' perception.
-
-\cite{forgas1987mood} showed that priming subjects with positive or negative moods affects their person-perception judgement\footnote{Person-perception judgement is a task where the subjects are asked to read a few characteristics of an unknown person; and once they have read the description the subjects are then asked to provide their perception about the target person}.
-In their study, \cite{forgas1987mood} showed used a bogus test with manipulated positive or negative feedback to prime the mood of the subjects in a positive or negative manner.
-Once the subjects were primed with a particular mood they were shown the descriptions of some unknown persons (with the same positive and negative characteristics).
-The results showed that the mood priming influences their person-perception, i.e, the positively primed subjects gave more positive remarks about the target perception while the negatively primed subjects gave more negative remarks.
-Moreover, the subjects in both the priming conditions spent more time on the priming specific characteristics (positive or negative).
-This shows that not only subjects' perception was altered but also their approach as well using the mood priming.
-
-\cite{yi1990cognitive} used specific attributes of a car to prime subjects' before they watched an advertisement about cars.
-The advertisement focused on explains various characteristics of a few imaginary cars in terms of the safety and the fuel efficiency.
-The priming stimulus had the size of the cars manipulated.
-The results showed that tone (affective priming) and size (cognitive priming) affects the favourability of the cars.
-For example, a big car was perceived to be more ``safe'' and less ``fuel-efficient'' than the small cars.
-
-\cite{tillmann2006cognitive}, in an fMRI study with music notes, showed that different parts of the frontal cortex gets activated when the participants were primed with sung or instrumental music.
-In their experiment, the subjects were asked to listen the first seven notes in either sung or instrumental manner (cognitive priming) and then to identify the relation between the first seven and the eighth note.
-The results showed that the subjects showed a higher activation in the inferior frontal cortex when primed with the sung notes than when they were primed with the instrumental notes.
-\cite{rholes1987emotional} showed that the memory recall is affected by the tone (affective priming) of the self-evaluation statement.
-In an experiment, where the subjects were given a set of positive or negative self-evaluation statements before being asked to recall a few good and bad memories from their past, the subjects were faster in recalling good memories when they were given a positive self-evaluation test; and vice-versa.
-
-All the above studies show that the cognitive and/or affective priming might alter the behaviour and/or the perception of the subjects about a target stimulus.
-Some of the studies found some complex interactions between cognitive and affective priming (\cite{yi1990cognitive} and \cite{storbeck2008affective} ).
-In this contribution, we were only interested in the cognitive priming aspect during a Human Robot Interaction situation, as \cite{baldwin1990priming} advocated that the cognitive priming may activate a relationship schema between the priming stimulus and the target stimulus.
-Moreover, in the context of advertisement, a number of studies suggest that the ad context (cognitive priming) can influence the audience's perception of the ad, and thus, its effectiveness (e.g., \cite{singh1987arousal};\cite{soldow1981response})  Our primary hypothesis was that the way the robot is given commands might alter the way the subjects perceive its actions.
-We propose to use a neutral mood (no affective priming) and two cognitive priming conditions (Human-like and Machine-like), in order to remove the ``mood'' or  ``affect'' bias of the priming.
-The ``machine-like'' priming consisted of giving commands to the robot which are more ``machine-like''.
-On the other hand, the ``human-like'' priming had the commands to robot in a more ``human-like'' manner (Manipulation-check hypothesis).
-We also kept the time of priming to be the same in the human-like and machine-like conditions, in order to remove the time of priming effect on the subjects' perceptions about the robot.
+Previous studies had shown that cognitive and/or affective priming influences
+human perception of the input stimulus. \cite{zajonc1980feeling} advocated the
+the use of affective priming and proposed that the affective reactions can be
+elicited with minimal stimulated input. As \cite{murphy1993affect} wrote
+\textit{``The experimental paradigm of priming, involves the presentation of one
+stimulus, or prime, alters subjects' perceptions of a second target
+stimulus...''}  \cite{murphy1993affect} found in their series of studies, where
+the subjects were shown happy and angry faces of people as a priming method,
+showed that the subjects' perceptions of positive emotions were higher and
+quicker when the priming was a happy face than for those who were primed with a
+angry face. The gender of the priming faces, however had no effect on the
+subjects' perception.
+
+\cite{forgas1987mood} showed that priming subjects with positive or negative
+moods affects their person-perception judgement\footnote{Person-perception
+judgement is a task where the subjects are asked to read a few characteristics
+of an unknown person; and once they have read the description the subjects are
+then asked to provide their perception about the target person}. In their study,
+\cite{forgas1987mood} showed used a bogus test with manipulated positive or
+negative feedback to prime the mood of the subjects in a positive or negative
+manner. Once the subjects were primed with a particular mood they were shown the
+descriptions of some unknown persons (with the same positive and negative
+characteristics). The results showed that the mood priming influences their
+person-perception, i.e, the positively primed subjects gave more positive
+remarks about the target perception while the negatively primed subjects gave
+more negative remarks. Moreover, the subjects in both the priming conditions
+spent more time on the priming specific characteristics (positive or negative).
+This shows that not only subjects' perception was altered but also their
+approach as well using the mood priming.
+
+\cite{yi1990cognitive} used specific attributes of a car to prime subjects'
+before they watched an advertisement about cars. The advertisement focused on
+explains various characteristics of a few imaginary cars in terms of the safety
+and the fuel efficiency. The priming stimulus had the size of the cars
+manipulated. The results showed that tone (affective priming) and size
+(cognitive priming) affects the favourability of the cars. For example, a big
+car was perceived to be more ``safe'' and less ``fuel-efficient'' than the small
+cars.
+
+\cite{tillmann2006cognitive}, in an fMRI study with music notes, showed that
+different parts of the frontal cortex gets activated when the participants were
+primed with sung or instrumental music. In their experiment, the subjects were
+asked to listen the first seven notes in either sung or instrumental manner
+(cognitive priming) and then to identify the relation between the first seven
+and the eighth note. The results showed that the subjects showed a higher
+activation in the inferior frontal cortex when primed with the sung notes than
+when they were primed with the instrumental notes. \cite{rholes1987emotional}
+showed that the memory recall is affected by the tone (affective priming) of the
+self-evaluation statement. In an experiment, where the subjects were given a set
+of positive or negative self-evaluation statements before being asked to recall
+a few good and bad memories from their past, the subjects were faster in
+recalling good memories when they were given a positive self-evaluation test;
+and vice-versa.
+
+All the above studies show that the cognitive and/or affective priming might
+alter the behaviour and/or the perception of the subjects about a target
+stimulus. Some of the studies found some complex interactions between cognitive
+and affective priming (\cite{yi1990cognitive} and \cite{storbeck2008affective}
+). In this contribution, we were only interested in the cognitive priming aspect
+during a Human Robot Interaction situation, as \cite{baldwin1990priming}
+advocated that the cognitive priming may activate a relationship schema between
+the priming stimulus and the target stimulus. Moreover, in the context of
+advertisement, a number of studies suggest that the ad context (cognitive
+priming) can influence the audience's perception of the ad, and thus, its
+effectiveness (e.g., \cite{singh1987arousal};\cite{soldow1981response})  Our
+primary hypothesis was that the way the robot is given commands might alter the
+way the subjects perceive its actions. We propose to use a neutral mood (no
+affective priming) and two cognitive priming conditions (Human-like and
+Machine-like), in order to remove the ``mood'' or  ``affect'' bias of the
+priming. The ``machine-like'' priming consisted of giving commands to the robot
+which are more ``machine-like''. On the other hand, the ``human-like'' priming
+had the commands to robot in a more ``human-like'' manner (Manipulation-check
+hypothesis). We also kept the time of priming to be the same in the human-like
+and machine-like conditions, in order to remove the time of priming effect on
+the subjects' perceptions about the robot.
 
@@
 
-\begin{inparaenum}[\itshape a\upshape)]
-Two nested research questions have been presented so far: \item can we
-characterise the link between expectations regarding the cognitive
-skills of a robot and the effective ascription of anthropomorphic features to
-this robot; and \item to this end, can we develop and validate a robust behavioural and
-\emph{in-the-moment} metric of anthropomorphism?  \end{inparaenum}
-
-These two questions translate into several experimental hypotheses, whose design
-was guided by the following high-level hypothesis: \emph{the more we ascribe cognitive
-capabilities to an agent, the more likely we are to focus on its head (\ie the
-brain) when interacting with it}. As such, this hypothesis naturally suggests an
-eye-tracking-based investigation.
-
-%Eye-tracking-based technique logically follows as an investigation mean, is a natural
-%methodology to investigate this intuition. We hence design audio-visual stimuli
-%that elicit different levels of cognitive ascription onto the robot while being
-%identical in every other way.
-
-Our baseline hypothesis \h{1} is that cognitive priming allows us to effectively create
-stimuli that induce \emph{lower} or \emph{higher} attribution of human-likeness
-to the robot. This hypothesis can be tested by asking
-participants to rate the interactions depicted by the stimuli as being more
-\emph{machine-like} or \emph{human-like}.
-
-Secondly, we hypothesise that people with a higher tendency to anthropomorphise
-robots will tend to physically look at robots and humans in similar ways, contrary to
-people with a lower tendency to anthropomorphise (\h{2}). If this is verified,
-it supports the idea that anthropomorphic attributions affect gaze patterns. The
-hypothesis can be tested by correlating the participants' tendency to
-anthropomorphise, measured from a standard questionnaire, with the comparative
-gazing behaviour in two conditions (human task \vs robot task).
-
-Third, we hypothesise that in the \emph{human-like} condition (which we
-interpret as well as a higher ascription of cognitive skills to the robot), the participants' gaze will be directed
-significantly more towards the head of the robot than in the \emph{machine-like}
-condition (interpreted as a lower ascription of cognitive skills) (\h{3}). If verified, it
-effectively means that the expectations held by the participants regarding the
-cognitive capabilities of the robot are reflected by the eye fixations on the
-head of the robot.  The hypothesis can be tested by comparing gaze fixations in
-the two conditions (\emph{human-like} \vs \emph{machine-like}).
-
-Finally, the hypothesis \h{4} proposes that manipulating cognitive expectations
-affects the broader tendency to anthropomorphise robots, \ie whether observing one
-robot acting in an \emph{human-like} context leads to an increased level of
-anthropomorphic attributions to robots in general. The hypothesis can be
-tested by looking at pre- and post-experiment self-reports on the tendency to
+As suggested in the previous section, we aim at verifying the following research
+hypothesis \h{}: the level of anthropomorphism ascribed by a human to a robot can be
+effectively assessed by measuring the human's gaze fixations on the robot's head.
+
+Our methodology involves showing participants video stimuli that elicit
+different levels of anthropomorphism, and measuring gaze fixations over the
+course of the video clips. To be suitable for an eye-tracking experiment, the
+video stimuli must be visually identical between conditions, and therefore
+we have to rely on non-visual cues to elicit different anthropomorphic
+projections. We choose to use cognitive priming with audio cues, as detailed in
+the next section.
+
+This approach allows us to decompose the hypothesis \h{} into two simpler
+hypotheses \h{1} and \h{2}: we want first to verify that cognitive priming
+enables us to effectively manipulate the attribution of human-likeness to robots
+(\h{1}).  We need next to verify that in the case of higher anthropomorphic
+attributions, the participants' gaze will be directed significantly more towards
+the head of the robot than in the case of low anthropomorphic attributions
+(\h{2}).
+
+If verified, these hypotheses would allow us to conclude that in a given
+human-robot interaction situation, gaze fixations on a robot's head reflects the
+ascription of anthropomorphic features to the robot. This would suggest that a
+relatively simple biometric and in-the-moment measure (eye-tracking) can
+effectively inform us about occurring anthropomorphic projections.
+
+\vspace{1em}
+
+Besides, our experimental design allows to examine two additional hypotheses:
+
+\begin{itemize}
+    \item people who generally tend to anthropomorphise exhibit gazing
+        behaviours that are similar when looking either at humans or robots, and
+        reciprocally (\h{3}). If this is verified, this would confirm that our
+        gazing behaviour towards agents is impacted by our tendency to
         anthropomorphise.
 
-If all these hypotheses are verified, the findings can be summarised as follow:
-\h{1} shows that our manipulation (based on cognitive priming) does effectively
-elicit lower or higher expectations in terms of the cognitive capabilities of
-the robot; \h{4} shows that these expectations influence our tendency to
-anthropomorphise robots in general; in parallel, \h{3} shows that these same expectations
-shape the way we look at the robot by eliciting specific eye fixations on the
-head of the robot; finally, \h{2} suggests that the fixation on the head
-reflects human-likeliness and supports the thesis that head fixation can be used
-as a behavioural measure of anthropomorphism.
+    \item the mere observation of a robot acting in an \emph{human-like}
+        situation suffice to increase the level of
+        anthropomorphic attributions to robots \emph{in general} (\h{4}).
+\end{itemize}
+
+%If all these hypotheses are verified, the findings can be summarised as follow:
+%\h{1} shows that our manipulation (based on cognitive priming) does effectively
+%elicit lower or higher expectations in terms of the cognitive capabilities of
+%the robot; \h{4} shows that these expectations influence our tendency to
+%anthropomorphise robots in general; in parallel, \h{3} shows that these same expectations
+%shape the way we look at the robot by eliciting specific eye fixations on the
+%head of the robot; finally, \h{2} suggests that the fixation on the head
+%reflects human-likeliness and supports the thesis that head fixation can be used
+%as a behavioural measure of anthropomorphism.
 
@@
 \section{Experimental Design}
+\label{sec:design}
 
@@
     \tikzmark{left}
-    \begin{tabular}{l|p{4cm}|p{4cm}}
+    \begin{tabular}{l|p{4.3cm}|p{4.3cm}}
         & \tikzmark{top1} Machine-like cognitive priming & Human-like cognitive priming \tikzmark{top2}  \\
@@
         \draw [decoration={brace,amplitude=0.5em},decorate,thick]
-        ($(left |- bottom)+(1.8,-0.3)$) --  ($(left |- left1.north)+(1.8,0.2)$) node[midway,left=1em,rotate=90,anchor=south] {\scriptsize within subject};
+        ($(left |- bottom)+(1.4,-0.3)$) --  ($(left |- left1.north)+(1.4,0.2)$) node[midway,left=1em,rotate=90,anchor=south] {\scriptsize within subject};
     \end{tikzpicture}
@@
         cognitive priming} \vs \emph{human-like cognitive priming} is between subjects.
-        Two stimuli (\emph{Picking} task, {\bf A}, and \emph{Pointing} task,
+        Two stimuli (\emph{Picking} task {\bf A}, and \emph{Pointing} task
         {\bf B}) were shown to the participants, introduced by brief verbal
@@
 inserting different commands to initiate the tasks (reported in
-table~\ref{table:design}): in the \emph{Picking} task for instance, the object
+figure~\ref{table:design}): in the \emph{Picking} task for instance, the object
 that the agent had to pick was described either as a \emph{``brown toy''} or as
@@
 As stated previously, the study followed a 2$\times$2 design
-(table~\ref{table:design}): the \emph{machine-like} \vs \emph{human-like cognitive priming}
-condition was between-subjects (30 participants performed the \emph{human-like cognitive}
-tasks while 26 were in the \emph{machine-like cognitive} condition); the \emph{robot}
-\vs \emph{human} condition was within-subject (the order of stimulus presentation
-was counter-balanced over the participants). The study lasted in average 15
-minutes per participant.
+(table~\ref{table:design}): the \emph{machine-like} \vs \emph{human-like
+cognitive priming} condition was between-subjects. 30 participants performed the
+\emph{human-like cognitive} tasks while 26 were in the \emph{machine-like
+cognitive} condition. The \emph{robot} \vs \emph{human} condition was
+within-subject. The study lasted in average 15 minutes per participant.
 
@@
 We then presented the stationary eye-tracker, conducted a brief eye-tracker
-calibration procedure (all participants could be successfully tracked), and the participants' gaze was recorded while they
-watched the \emph{robot} and \emph{human} interaction stimuli.
+calibration procedure (all participants could be successfully tracked), and the
+participants' gaze was recorded while they watched the \emph{robot} and
+\emph{human} interaction stimuli. The order of stimulus presentation
+was counter-balanced over the participants.
 
@@
 %\subsection{General Biases}
-First of all, we checked if there were any direct effects of the age, gender, familiarity with robot and robot ownership of the participants on the different aforementioned variables.
-We did not observe any such significant effects.
+First of all, we checked if there were any direct effects of the age, gender,
+familiarity with robot and robot ownership of the participants on the different
+aforementioned variables. We did not observe any such significant effects.
 
@@
 \vs $M_{\text{human-like}}=TBD (SD=TDB)$) in this
-manipulation check ($F(1,54) = 29.0, p < .001$) which validates our manipulation
-and supports \h{1}: the participants that watched stimuli with a \emph{machine-like cognitive
-priming} identified the task as more robot-like and participants watching
-the videos with a human-like cognitive priming perceived the tasks as more human-like.
-
-TBD: editor asks about possible ordering effect
+manipulation check ($F(1,54) = 29.0, p < .001$): the participants who watched
+stimuli in the \emph{machine-like priming} condition identified the tasks as more
+robot-like, while participants who watched the videos with a \emph{human-like
+priming} perceived the tasks as more human-like.
+
+Note that, expectedly, we found an order effect on the presentation of the robot
+and human stimuli (our within-subject variable): if the stimuli shown last
+involved a human, the participant reported a more human-like kind of tasks
+(ANOVA between the models with condition only and condition and order: $F(1,51)
+= 11.15, p < .001$, no interaction). This was accounted for by counter-balancing
+the presentation order.
+
+This first result supports \h{1}: cognitive priming enables us to
+effectively elicit different levels of human-likeliness attribution.
+\h{1} is however only partially supported as it specifically hypothesised that cognitive
+priming can manipulate anthropomorphic attributions to the \emph{robot} itself:
+the results of the manipulation check only indicate that the priming impacted
+the participants' anthropomorphic perception of the \emph{interaction
+situation} as a whole.
+
+\subsection{Impact of Cognitive Priming on Anthropomorphic Attributions}
+
+Running an ANOVA against the change of anthropomorphic attributions
+\deltaant before and after the experiment shows that \deltaant is greater for the participants who watched the
+human-like tasks ($\Delta_{\text{machine-like}}=TBD (SD=TBD)$
+\vs $\Delta_{\text{human-like}}=TBD (SD=TDB)$, $F(1,54) = 6.54, p < .05$\fixme{put the exact
+p value here}). In other words, after being exposed to short videos of a robot
+performing simple tasks, participants primed with richer cognitive
+expectations regarding the robot report a significantly higher tendency to anthropomorphise robots
+\emph{in general} (as the questionnaire on anthropomorphic attributions
+explicitly referred to \emph{robots in general}).
+
+This result shows that the manipulation of the cognitive requirements of our
+tasks does indeed alter the participants' perception of the robots themselves.
+Combined with the previous result, we can conclude that \h{1} is indeed
+supported: by the mean of cognitive priming, we can manipulate the
+human-likeness attributions to robots.
+
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}
+%    \caption{Difference between \anti{} and \antf{} in the machine-like and
+%    human-like
+%    cognitive priming conditions.}
+%    \label{h4}
+%\end{figure}
+
+This result also supports \h{4}: cognitive priming impacts the
+attribution of anthropomorphic features to robots beyond the specific Nao robot
+shown in the stimuli. It appears that participants transfer to some extent the
+cognitive capabilities that they ascribe to the Nao robot in the
+\emph{human-like} cognitive condition to robots in general. We can not, however,
+conclude on any possible \emph{lasting} anthropomorphic ascriptions to robots as we
+measure the anthropomorphic perception immediately after the experiment.
 
@@
 machine-like \vs human-like cognitive priming.
-
-\subsection{Impact of Cognitive Priming on Changes in Anthropomorphic
-Attributions}
-
-Running an ANOVA against the change of anthropomorphic attributions
-(\deltaant) over the duration of the experiment in the two cognitive
-conditions, shows that \deltaant is greater for the participants who watched the
-human-like tasks ($\Delta_{\text{machine-like}}=TBD (SD=TBD)$
-\vs $\Delta_{\text{human-like}}=TBD (SD=TDB)$, $F(1,54) = 6.54, p < .05$\fixme{put the exact
-p value here}). In other words, after being exposed to short videos of a robot
-performing simple tasks, participants primed with a richer cognitive
-expectations regarding the robot report a significantly higher tendency to anthropomorphise robots
-\emph{in general} (as the questionnaire on anthropomorphic attributions
-explicitly referred to \emph{robots in general}).
-
-%\begin{figure}
-%    \centering
-%    \includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}
-%    \caption{Difference between \anti{} and \antf{} in the machine-like and
-%    human-like
-%    cognitive priming conditions.}
-%    \label{h4}
-%\end{figure}
-
-This result supports \h{4}: cognitive priming impacts the
-attribution of anthropomorphic features to robots \emph{beyond the specific Nao robot
-shown in the stimuli}.  It appears that participants transfer to some extent the
-cognitive capabilities that they ascribe to the Nao robot in the
-\emph{human-like} cognitive condition to ``robots'' in general (we can not, however,
-conclude on any possible \emph{lasting} anthropomorphic ascriptions to robots as we
-measure the anthropomorphic perception immediately after the experiment).
 
@@
 \section{Conclusion}
+\label{conclusion}
 
@@
 a novel technique to assess anthropomorphic projections that relies on a
-biometric measurement (eye-tracking) to compare gaze fixation durations on
+biometric measure (eye-tracking) to compare gaze fixation durations on
 the face of the robot. We cross-validate this new metric with existing,
@@
 
-We had a comment from the reviewers: 
-`` In addition, you need to address that head fixations to the robot could increase because people are curious whether the robot really has the implied capacities, not because they assume it has them.
-Can you rule out this alternative interpretation?''
+We had a comment from the reviewers: `` In addition, you need to address that
+head fixations to the robot could increase because people are curious whether
+the robot really has the implied capacities, not because they assume it has
+them. Can you rule out this alternative interpretation?''
 
@@
 
-MORE TO APPEAR``reported eye tracking results are far too cursory'' - I will put a nice factor analysis of the eye-tracking data with the questionnaire responses and then we can answer many questions in the results section.
+MORE TO APPEAR``reported eye tracking results are far too cursory'' - I will put
+a nice factor analysis of the eye-tracking data with the questionnaire responses
+and then we can answer many questions in the results section.
 

### 2016-09-02 main.tex
Rewritten hypotheses

@@
 
-\begin{inparaenum}[\itshape a\upshape)]
-Two nested research questions have been presented so far: \item can we
-characterise the link between expectations regarding the cognitive
-skills of a robot and the effective ascription of anthropomorphic features to
-this robot; and \item to this end, can we develop and validate a robust behavioural and
-\emph{in-the-moment} metric of anthropomorphism?  \end{inparaenum}
-
-These two questions translate into several experimental hypotheses, whose design
-was guided by the following high-level hypothesis: \emph{the more we ascribe cognitive
-capabilities to an agent, the more likely we are to focus on its head (\ie the
-brain) when interacting with it}. As such, this hypothesis naturally suggests an
-eye-tracking-based investigation.
-
-%Eye-tracking-based technique logically follows as an investigation mean, is a natural
-%methodology to investigate this intuition. We hence design audio-visual stimuli
-%that elicit different levels of cognitive ascription onto the robot while being
-%identical in every other way.
-
-Our baseline hypothesis \h{1} is that cognitive priming allows us to effectively create
-stimuli that induce \emph{lower} or \emph{higher} attribution of human-likeness
-to the robot. This hypothesis can be tested by asking
-participants to rate the interactions depicted by the stimuli as being more
-\emph{machine-like} or \emph{human-like}.
-
-Secondly, we hypothesise that people with a higher tendency to anthropomorphise
-robots will tend to physically look at robots and humans in similar ways, contrary to
-people with a lower tendency to anthropomorphise (\h{2}). If this is verified,
-it supports the idea that anthropomorphic attributions affect gaze patterns. The
-hypothesis can be tested by correlating the participants' tendency to
-anthropomorphise, measured from a standard questionnaire, with the comparative
-gazing behaviour in two conditions (human task \vs robot task).
-
-Third, we hypothesise that in the \emph{human-like} condition (which we
-interpret as well as a higher ascription of cognitive skills to the robot), the participants' gaze will be directed
-significantly more towards the head of the robot than in the \emph{machine-like}
-condition (interpreted as a lower ascription of cognitive skills) (\h{3}). If verified, it
-effectively means that the expectations held by the participants regarding the
-cognitive capabilities of the robot are reflected by the eye fixations on the
-head of the robot.  The hypothesis can be tested by comparing gaze fixations in
-the two conditions (\emph{human-like} \vs \emph{machine-like}).
-
-Finally, the hypothesis \h{4} proposes that manipulating cognitive expectations
-affects the broader tendency to anthropomorphise robots, \ie whether observing one
-robot acting in an \emph{human-like} context leads to an increased level of
-anthropomorphic attributions to robots in general. The hypothesis can be
-tested by looking at pre- and post-experiment self-reports on the tendency to
+As suggested in the previous section, we aim at verifying the following research
+hypothesis \h{}: the level of anthropomorphism ascribed by a human to a robot can be
+effectively assessed by measuring the human's gaze fixations on the robot's head.
+
+Our methodology involves showing participants video stimuli that elicit
+different levels of anthropomorphism, and measuring gaze fixations over the
+course of the video clips. To be suitable for an eye-tracking experiment, the
+video stimuli must be visually identical between conditions, and we therefore
+rely on non-visual cues to elicit different anthropomorphic projections
+(cognitive priming). The next section details this methodology.
+
+This approach allows us to decompose the hypothesis \h{} into two simpler
+hypotheses \h{1} and \h{2}:  we want first to verify that cognitive priming
+enables us to effectively create stimuli that induce lower or higher attribution
+of human-likeness to robots (\h{1}).  We need next to verify that in the case of
+high anthropomorphic attributions, the participants' gaze will be directed
+significantly more towards the head of the robot than in the case of low
+anthropomorphic attributions (\h{2}).
+
+If verified, these hypotheses would allow us to conclude that in a given
+human-robot interaction situation, the more a human focuses on the robot's head,
+the more the human ascribe anthropomorphic features to the robot.
+\fixme{Attention, this conclusion seems to wrongly reverse the implication of
+the hypotheses!}
+
+%If verified, it
+%effectively means that the expectations held by the participants regarding the
+%cognitive capabilities of the robot are reflected by the eye fixations on the
+%head of the robot.  The hypothesis can be tested by comparing gaze fixations in
+%the two conditions (\emph{human-like} \vs \emph{machine-like}).
+
+\vspace{1em}
+
+Besides, our experimental design allows to examine two additional hypotheses:
+
+\begin{itemize}
+    \item people who tend to anthropomorphise a lot show gazing behaviours that
+        are similar for humans and robots, while people who show a lower
+        tendency to anthropomorphise do not look at robots and humans in the
+        same way (\h{3}). If this is verified, this would confirm that our
+        gazing behaviour towards agents is impacted by our tendency to
         anthropomorphise.
 
-If all these hypotheses are verified, the findings can be summarised as follow:
-\h{1} shows that our manipulation (based on cognitive priming) does effectively
-elicit lower or higher expectations in terms of the cognitive capabilities of
-the robot; \h{4} shows that these expectations influence our tendency to
-anthropomorphise robots in general; in parallel, \h{3} shows that these same expectations
-shape the way we look at the robot by eliciting specific eye fixations on the
-head of the robot; finally, \h{2} suggests that the fixation on the head
-reflects human-likeliness and supports the thesis that head fixation can be used
-as a behavioural measure of anthropomorphism.
+    \item the mere observation of a robot acting in an \emph{human-like}
+        situation suffice to increase the level of
+        anthropomorphic attributions to robots \emph{in general} (\h{4}).
+\end{itemize}
+
+%If all these hypotheses are verified, the findings can be summarised as follow:
+%\h{1} shows that our manipulation (based on cognitive priming) does effectively
+%elicit lower or higher expectations in terms of the cognitive capabilities of
+%the robot; \h{4} shows that these expectations influence our tendency to
+%anthropomorphise robots in general; in parallel, \h{3} shows that these same expectations
+%shape the way we look at the robot by eliciting specific eye fixations on the
+%head of the robot; finally, \h{2} suggests that the fixation on the head
+%reflects human-likeliness and supports the thesis that head fixation can be used
+%as a behavioural measure of anthropomorphism.
 

### 2016-09-05 main.tex
Refine hypotheses

@@
 course of the video clips. To be suitable for an eye-tracking experiment, the
-video stimuli must be visually identical between conditions, and we therefore
-rely on non-visual cues to elicit different anthropomorphic projections
-(cognitive priming). The next section details this methodology.
+video stimuli must be visually identical between conditions, and therefore
+we have to rely on non-visual cues to elicit different anthropomorphic
+projections. We choose to use cognitive priming with audio cues, as detailed in
+the next section.
 
@@
 hypotheses \h{1} and \h{2}: we want first to verify that cognitive priming
-enables us to effectively create stimuli that induce lower or higher attribution
-of human-likeness to robots (\h{1}).  We need next to verify that in the case of
-high anthropomorphic attributions, the participants' gaze will be directed
-significantly more towards the head of the robot than in the case of low
-anthropomorphic attributions (\h{2}).
+enables us to effectively manipulate the attribution of human-likeness to robots
+(\h{1}).  We need next to verify that in the case of higher anthropomorphic
+attributions, the participants' gaze will be directed significantly more towards
+the head of the robot than in the case of low anthropomorphic attributions
+(\h{2}).
 
 If verified, these hypotheses would allow us to conclude that in a given
-human-robot interaction situation, the more a human focuses on the robot's head,
-the more the human ascribe anthropomorphic features to the robot.
-\fixme{Attention, this conclusion seems to wrongly reverse the implication of
-the hypotheses!}
-
-%If verified, it
-%effectively means that the expectations held by the participants regarding the
-%cognitive capabilities of the robot are reflected by the eye fixations on the
-%head of the robot.  The hypothesis can be tested by comparing gaze fixations in
-%the two conditions (\emph{human-like} \vs \emph{machine-like}).
+human-robot interaction situation, gaze fixations on a robot's head reflects the
+ascription of anthropomorphic features to the robot. This would suggest that a
+relatively simple biometric and in-the-moment measure (eye-tracking) can
+effectively inform us about occurring anthropomorphic projections.
 
@@
 \begin{itemize}
-    \item people who tend to anthropomorphise a lot show gazing behaviours that
-        are similar for humans and robots, while people who show a lower
-        tendency to anthropomorphise do not look at robots and humans in the
-        same way (\h{3}). If this is verified, this would confirm that our
+    \item people who generally tend to anthropomorphise exhibit gazing
+        behaviours that are similar when looking either at humans or robots, and
+        reciprocally (\h{3}). If this is verified, this would confirm that our
         gazing behaviour towards agents is impacted by our tendency to
@@
 \section{Conclusion}
+\labe{conclusion}
 

### 2016-09-05 main.tex
Rewritten section on cognitive priming

@@
 
-This article attempts to address the issue with a different experimental design
-and a novel methodology to measure \emph{in-the-moment} anthropomorphic
-attributions.  Our approach is built on a combination of cognitive priming and
-eye-tracking. By doing so, we evidence specific gaze fixations on the head
-of the robot when the participants are primed with higher expectations
-regarding the cognitive skills of the robot. We then establish the link
-between head fixations and anthropomorphic ascriptions, to eventually show how
-subtle interaction manipulations do significantly impact our tendency
-to ascribe human traits to machines.
-
-\subsection{Cognitive Priming and Interaction Situation}
-
-Previous studies had shown that cognitive and/or affective priming influences
-human perception of the input stimulus. \cite{zajonc1980feeling} advocated the
-the use of affective priming and proposed that the affective reactions can be
-elicited with minimal stimulated input. As \cite{murphy1993affect} wrote
-\textit{``The experimental paradigm of priming, involves the presentation of one
-stimulus, or prime, alters subjects' perceptions of a second target
-stimulus...''}  \cite{murphy1993affect} found in their series of studies, where
-the subjects were shown happy and angry faces of people as a priming method,
-showed that the subjects' perceptions of positive emotions were higher and
-quicker when the priming was a happy face than for those who were primed with a
-angry face. The gender of the priming faces, however had no effect on the
-subjects' perception.
-
-\cite{forgas1987mood} showed that priming subjects with positive or negative
-moods affects their person-perception judgement\footnote{Person-perception
-judgement is a task where the subjects are asked to read a few characteristics
-of an unknown person; and once they have read the description the subjects are
-then asked to provide their perception about the target person}. In their study,
-\cite{forgas1987mood} showed used a bogus test with manipulated positive or
-negative feedback to prime the mood of the subjects in a positive or negative
-manner. Once the subjects were primed with a particular mood they were shown the
-descriptions of some unknown persons (with the same positive and negative
-characteristics). The results showed that the mood priming influences their
-person-perception, i.e, the positively primed subjects gave more positive
-remarks about the target perception while the negatively primed subjects gave
-more negative remarks. Moreover, the subjects in both the priming conditions
-spent more time on the priming specific characteristics (positive or negative).
-This shows that not only subjects' perception was altered but also their
-approach as well using the mood priming.
-
-\cite{yi1990cognitive} used specific attributes of a car to prime subjects'
-before they watched an advertisement about cars. The advertisement focused on
-explains various characteristics of a few imaginary cars in terms of the safety
-and the fuel efficiency. The priming stimulus had the size of the cars
-manipulated. The results showed that tone (affective priming) and size
-(cognitive priming) affects the favourability of the cars. For example, a big
-car was perceived to be more ``safe'' and less ``fuel-efficient'' than the small
-cars.
-
-\cite{tillmann2006cognitive}, in an fMRI study with music notes, showed that
-different parts of the frontal cortex gets activated when the participants were
-primed with sung or instrumental music. In their experiment, the subjects were
-asked to listen the first seven notes in either sung or instrumental manner
-(cognitive priming) and then to identify the relation between the first seven
-and the eighth note. The results showed that the subjects showed a higher
-activation in the inferior frontal cortex when primed with the sung notes than
-when they were primed with the instrumental notes. \cite{rholes1987emotional}
-showed that the memory recall is affected by the tone (affective priming) of the
-self-evaluation statement. In an experiment, where the subjects were given a set
-of positive or negative self-evaluation statements before being asked to recall
-a few good and bad memories from their past, the subjects were faster in
-recalling good memories when they were given a positive self-evaluation test;
-and vice-versa.
-
-All the above studies show that the cognitive and/or affective priming might
-alter the behaviour and/or the perception of the subjects about a target
-stimulus. Some of the studies found some complex interactions between cognitive
-and affective priming (\cite{yi1990cognitive} and \cite{storbeck2008affective}
-). In this contribution, we were only interested in the cognitive priming aspect
-during a Human Robot Interaction situation, as \cite{baldwin1990priming}
-advocated that the cognitive priming may activate a relationship schema between
-the priming stimulus and the target stimulus. Moreover, in the context of
-advertisement, a number of studies suggest that the ad context (cognitive
-priming) can influence the audience's perception of the ad, and thus, its
-effectiveness (e.g., \cite{singh1987arousal};\cite{soldow1981response})  Our
-primary hypothesis was that the way the robot is given commands might alter the
-way the subjects perceive its actions. We propose to use a neutral mood (no
-affective priming) and two cognitive priming conditions (Human-like and
-Machine-like), in order to remove the ``mood'' or  ``affect'' bias of the
-priming. The ``machine-like'' priming consisted of giving commands to the robot
-which are more ``machine-like''. On the other hand, the ``human-like'' priming
-had the commands to robot in a more ``human-like'' manner (Manipulation-check
-hypothesis). We also kept the time of priming to be the same in the human-like
-and machine-like conditions, in order to remove the time of priming effect on
-the subjects' perceptions about the robot.
+This article introduces a different experimental design and a novel methodology
+to measure \emph{in-the-moment} anthropomorphic attributions.  Our approach is
+built on a combination of cognitive priming and eye-tracking. By doing so, we
+evidence specific gaze fixations on the head of the robot when the participants
+are primed with higher expectations regarding the cognitive skills of the robot.
+We then show how subtle interaction manipulations do significantly impact our
+tendency to ascribe human traits to machines, to eventually establish the link
+between head fixations and anthropomorphic ascriptions.
 
@@
 interact.
+
+\subsection{Cognitive Priming and Interaction Situation}
+
+Cognitive priming is the primary mean of condition manipulation that we rely on.
+Many previous studies have investigated how cognitive and/or affective priming
+influence human perception of an input stimulus. \cite{zajonc1980feeling}
+advocated the use of affective priming and proposed that the affective reactions
+can be elicited with minimal stimulated input: \cite{murphy1993affect} found in
+a series of studies where participants were shown happy and angry faces as a
+priming method, that the participants' perceptions of positive emotions were
+higher and quicker when the priming was a happy face than for those who were
+primed with a angry face. The gender of the priming faces, however had no effect
+on the participants' perception.
+
+\cite{forgas1987mood} showed that priming participants with positive or negative
+moods affects their person-perception judgement\footnote{Person-perception
+judgement is a task where the participants are asked to read a few
+characteristics of an unknown person; and once they have read the description
+the participants are then asked to provide their perception about the target
+person}. In their study, they used a test with manipulated positive or negative
+feedback to prime the mood of the participants in a positive or negative manner.
+The results showed that the priming influenced their person-perception, \ie the
+positively primed participants provided more positive remarks about a new,
+unknown face, while the negatively primed participants made more negative
+remarks. Moreover, the participants in both the priming conditions spent more
+time elaborating on the specific characteristics they were primed with. This
+shows that mood priming influenced not only the participants' perceptions, but
+also their behaviours during the test.
+
+Similarly, \cite{yi1990cognitive} used specific attributes of a car to prime
+participants before they watched an advertisement about cars. The advertisement
+discussed characteristics of imaginary cars in terms of their safety and fuel
+efficiency.  The priming stimulus had manipulated the size of the car, as well
+as the tone of the description. The results showed that both the tone (affective
+priming) and the size (cognitive priming) affects the likeability of the car.
+In the context of advertising, a number of studies suggest that the context
+(cognitive priming) influences the perception of the advertisement by the
+audience, and therefore, its effectiveness~\citep{singh1987arousal,soldow1981response}.
+
+In an fMRI study with music notes, \cite{tillmann2006cognitive} showed that
+different parts of the frontal cortex gets activated when the participants were
+primed with sung or instrumental music. In their experiment, the participants were
+asked to listen the first seven notes in either sung or instrumental manner
+(cognitive priming) and then to identify the relation between the first seven
+and the eighth note. The results showed that the participants showed a higher
+activation in the inferior frontal cortex when primed with the sung notes than
+when they were primed with the instrumental notes.
+
+\cite{rholes1987emotional} showed that the memory recall is affected by the tone
+(affective priming) of self-evaluation statement: In an experiment, where
+the participants were given a set of positive or negative self-evaluation
+statements before being asked to recall a few good and bad memories from their
+past, the participants were faster in recalling good memories when they were
+given a positive self-evaluation test and vice-versa.
+
+All the above studies show that cognitive and/or affective priming can alter
+both the perception by the participant of a target stimulus, and the behaviour
+of the participant while processing the stimulus. Some of the studies also
+evidenced interactions between cognitive and affective
+priming~\citep{yi1990cognitive,storbeck2008affective}.
+
+We focus here on cognitive priming: as~\cite{baldwin1990priming} pointed out, we
+expect that cognitive priming may activate a relationship schema between the
+priming stimulus (the context of the interaction) and the
+target stimulus (the interaction situation, and in particular, the robot).
+More specifically, we designed stimuli in which the way the robot is given
+commands pre-supposes a specific interaction situation (more or less
+`human-like') and is expected in turn to alter the way the participants perceive the
+actions of the robot.
+
+We use a neutral mood/tone (no affective priming) and, as detailed in the
+Methodology section hereafter, two cognitive priming conditions (hereafter
+referred as `machine-like' and `human-like').
 
@@
 
-This study is built as an eye-tracking experiment (using a stationary
+As mentioned, this study is built as an eye-tracking experiment (using a stationary
 eye-tracker SMI RED 250) where participants watch short videos of an agent --
-either a robot (Aldebaran Robotics' Nao) or a human -- performing simple tasks
+either a robot (the Aldebaran Robotics' Nao) or a human -- performing simple tasks
 (picking an object or pointing toward a sound source) after being primed.  The
@@
 (leading to what we call hereafter a \emph{machine-like} interaction situation)
-or richer cognitive ascriptions (leaning toward what we call a \emph{human-like}
+or richer cognitive ascriptions (leading to what we call a \emph{human-like}
 interaction situation).
@@
 \section{Conclusion}
-\labe{conclusion}
+\label{conclusion}
 

### 2016-09-05 main.tex
WIP on the discussion

@@
 the interaction situation to induce a machine-like or a human-like task context
-was successful.
-
-situation priming the participants with , and that a machine-like cognitive
-context was indeed perceived to elicit a ``robot-like'' situation, while a
-human-like
-cognitive priming was perceived as a ``human-like'' situation. This supports our
-first hypothesis \h{1}: even indirect hints at the cognitive capabilities of a robot are
-sufficient to elicit significantly increased attribution of human-likeness.
+was successful. By further showing that the conditions also impact the
+reported tendency to attribute anthropomorphic traits to robots in general (as assessed by
+the Godspeed questionnaire), we conclude that our manipulation of the commands
+given to the robot effectively influenced how anthropomorphic the participants
+perceived the robot.
+
+We interpret this result as the participants building in each condition a different set of
+expected cognitive skills for the robot: when a participant hears the robot
+being instructed ``Pick up your favourite toy'', she implicitly (and likely,
+unconsciously) supposes that the robot has the cognitive capabilities required
+to \emph{prefer} one toy to another one, which would typically implies that the robot
+understand the affective dimensions of the different toys. By performing this
+reasoning, we believe the human (likely unconsciously) does attribute cognitive and emotional
+traits to the robot that are akin to humans, and as a result, anthropomorphise
+more the robot.
 
@@
 
-\subsection{Design of the Stimuli and Applicability of the Method to Real World
+\paragraph{Design of the Stimuli and Applicability of the Method to Real World
 Scenarios}

### 2016-09-06 main.tex
WIP on Discussion

--- 2016-09-05 main.tex
@@
 \subsection{Cognitive Priming and Interaction Situation}
+\label{cognitive-priming}
 
@@
 the interaction situation to induce a machine-like or a human-like task context
-was successful.
-
-situation priming the participants with , and that a machine-like cognitive
-context was indeed perceived to elicit a ``robot-like'' situation, while a
-human-like
-cognitive priming was perceived as a ``human-like'' situation. This supports our
-first hypothesis \h{1}: even indirect hints at the cognitive capabilities of a robot are
-sufficient to elicit significantly increased attribution of human-likeness.
+was successful. By further showing that the conditions also impact the
+reported tendency to attribute anthropomorphic traits to robots in general (as assessed by
+the Godspeed questionnaire), we conclude that our manipulation of the commands
+given to the robot effectively influenced the participants in perceiving the
+robot as anthropomorphic.
+
+We interpret this result as the consequence of building in each condition a
+different set of expectation regarding the cognitive skills of the robot: when a
+participant hears the robot being instructed ``Pick up your favourite toy'', she
+implicitly (and likely, unconsciously) supposes that the robot has the cognitive
+capabilities required to \emph{prefer} one toy to another one, which would also
+typically implies that the robot understand the affective dimensions of toys. By
+performing this reasoning, the human would (likely unconsciously) attribute
+cognitive and emotional traits to the robot that are akin to humans, and as a
+result, anthropomorphise more the robot. Similarly for the command ``Point at
+the crying baby'' that elicits not only emotional attributions related to cries
+and babies, but also suggests that the robot has a sense of the urgency of
+the situation (a baby is crying!). Our manipulation makes the robot appear as it
+possesses a commonsense knowledge of a typically human situation.
+
+Remarkably (and in line with the literature reviewed in
+section~\ref{cognitive-priming}), these cognitive ascriptions lead to a visible
+change in the participants' behaviour: they gaze more at the head of the robot
+when they watch a scene that elicits stronger anthropomorphic attributions.
+Several explanations can be thought of. At an abstract level, the head may
+typically be seen as embodying the mind and the emotions. As such, the head of
+an agent that is believed to be endowed with such cognitive and emotional
+abilities could be thought to be of higher importance, attracting more
+attention. Another explanation pertains to the social norms elicited by a moral
+agent~\citep{malle2014moral}. We can reasonably suppose that a robot thought to
+be endowed with rich cognitive skills is likely to be considered more as a moral
+agent as a robot with an apparent mechanical behaviour. As a result, the
+participant might be led to adhere to social norms (including looking at the
+face when interacting) when watching the robot. A third explanation involves
+automatic social behaviours: if the participant is tricked into believing that
+the robot might have rich cognitive skills, she might automatically search for
+even more socio-cognitive cues, and the face is a particularly rich source of
+such cues (facial expressions, gaze, back-channel communication like nodding).
 

### 2016-09-06 main.tex
WIP discussion

@@
 
-\rightheader{Gaing at the Robot's Head Reflects our Tendency to Anthropomorphise}   % This should be the title, or a shortened version of the title if your title is long.
+\rightheader{Gazing at the Robot's Head Reflects our Tendency to Anthropomorphise}   % This should be the title, or a shortened version of the title if your title is long.
 \leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
@@
 automatic social behaviours: if the participant is tricked into believing that
-the robot might have rich cognitive skills, she might automatically search for
-even more socio-cognitive cues, and the face is a particularly rich source of
-such cues (facial expressions, gaze, back-channel communication like nodding).
+the robot might have a richer set of cognitive skills, she might automatically
+search for other socio-cognitive confirmation cues, and the face is a
+particularly rich source of such cues (facial expressions, gaze, back-channel
+communication like nodding). This would therefore also lead to longer observed
+gaze fixations on the robot's head.
+
+Our experimental protocol enabled us to examine two additional questions: by
+administrating the Godspeed questionnaire on anthropomorphism and mind
+attribution first as pre-test, we gained a picture of the initial tendency of
+our participants to anthropomorphise robots. Using our \deltaant measure of the
+gazing behaviour similarity, we have evidenced that people with an higher
+tendency to anthropomorphise robots, also exhibit a more similar gazing
+behaviour when they watch either a human or a robot performing the same task. If
+confirmed (in particular with balanced human genders), this is a significant
+result. The Godspeed questionnaire assesses how likely we are to
+anthropomorphise machines in an abstract way: no concrete robots nor interaction
+situations are shown; the participants might react to the sentence ``Please rate
+your impression of robots'' in widely different ways depending on their own
+constructed images of what robots are. And yet, our results show a significant
+correlation with gazing behaviour: the more you tend to anthropomorphise, the
+more you look at robots the way you look at humans. This implies that the mere
+propensity to attribute physical or mental human traits to robots suffice to
+influence a mostly unconscious (yet easy to observe) physical behaviour.  This
+link between psychological attributions and a resulting physical behaviour might
+be of interest to the Human-Robot Interaction community, especially if we endow
+the robot with the ability to measure itself, \emph{during} the interaction, the
+time spent by the human on its face. This would for instance allow the robot to
+build an initial model of the cognitive expectations held by the human regarding
+the robot.
 

### 2016-09-06 main.tex
Added computed Mean and SD for section 4.2
But they'll be updated once we use mind attribution questions instead of likeability questions

@@
 \deltaant before and after the experiment shows that \deltaant is greater for the participants who watched the
-human-like tasks ($\Delta_{\text{machine-like}}=TBD (SD=TBD)$
-\vs $\Delta_{\text{human-like}}=TBD (SD=TDB)$, $F(1,54) = 6.54, p < .05$\fixme{put the exact
+human-like tasks ($\Delta_{\text{machine-like}}=-0.44 (SD=5.23)$
+\vs $\Delta_{\text{human-like}}=3.55 (SD=4.64)$, $F(1,54) = 6.54, p < .05$\fixme{put the exact
 p value here}). In other words, after being exposed to short videos of a robot

### 2016-09-06 main.tex
WIP discussion

@@
 \newcommand{\deltaant}{{$\Delta_{\mathcal{A}}$\xspace}}
+\newcommand{\deltagaze}{{$\delta_{\mathcal{H},\mathcal{R}}^{\text{gaze}}$\xspace}}
 
@@
     \item the mere observation of a robot acting in an \emph{human-like}
-        situation suffice to increase the level of
+        situation should not suffice to increase the level of
         anthropomorphic attributions to robots \emph{in general} (\h{4}).
@@
 
-This result also supports \h{4}: cognitive priming impacts the
+This result also contradicts \h{4}: cognitive priming impacts the
 attribution of anthropomorphic features to robots beyond the specific Nao robot
@@
 We found a significant negative correlation between
-$\delta_{\mathcal{H},\mathcal{R}}^{\text{gaze}}$ and
+\deltagaze and
 the initial tendency to anthropomorphise \anti{} (Pearson Correlation Coefficient $r(54) = -0.43,
@@
     \includegraphics[width=0.5\columnwidth]{H2}\label{GazeDifference-vs-ICA}
-    \caption{Gaze distribution difference $\delta_{\mathcal{H},
-    \mathcal{R}}^{\text{gaze}}$ \vs initial tendency to anthropomorphise \anti{}}
+    \caption{Gaze distribution difference \deltagaze \vs initial tendency to anthropomorphise \anti{}}
     \label{h2}
@@
 attribution first as pre-test, we gained a picture of the initial tendency of
-our participants to anthropomorphise robots. Using our \deltaant measure of the
+our participants to anthropomorphise robots. Using our \deltagaze measure of the
 gazing behaviour similarity, we have evidenced that people with an higher
@@
 
-Hypothesis \h{2} looked at a possible interaction between our tendency to
-anthropomorphise (as measured in the pre-questionnaire) and our actual gaze
-behaviour, the hypothesis being that high anthropomorphisers would show smaller
-differences between the way they look at robots and humans (since they would
-consider robots closer to humans than low anthropomorphisers). Our data supports
-this hypothesis: participants reporting an higher tendency to anthropomorphise
-tend to have closer gazing behaviours when they look at humans or at robots:
-statistically speaking, the tendency to anthropomorphise robots
-is reflected in the way one looks at them: you look at them
-like you would look at humans.
-
-The third hypothesis \h{3} proposes that head fixations are related to the
-cognitive expectations, which is clearly supported by our data: after human-like cognitive
-priming, one tends to spend more time looking at the head of the interacting
-agent than after machine-like cognitive priming. We also hypothesised that, in turn,
-head fixations could act as a \emph{proxy to anthropomorphic projections}: as
-underlined in the previous section, our data also support this.
-
-Finally, the hypothesis \h{4} looks at the dynamic of anthropomorphic
-projections, with the hypothesis that watching an interaction with a particular
-robot after a human-like cognitive priming may impact \emph{globally} the
-anthropomorphic perceptions of robots. This is supported by our study.
+Lastly, we investigated one of the dynamics of anthropomorphic projections: is
+watching a specific robot after a human-like cognitive priming sufficient to
+impact the \emph{general} perception of robots as anthropomorphic agents. By
+administrating the same Godspeed questionnaire as a post-test, we computed 
+\deltaant to assess possible change in the participants' general tendency to
+anthropomorphise. The stimuli were short videos of `toy' interaction scenarios,
+and we did not anticipate any transfer of the anthropomorphic traits ascribed onto
+the robot seen in the videos, to the broader tendency to anthropomorphise
+robots in general, as assessed in the post-questionnaire. Our result challenge
+this assumption: \deltaant is significantly higher for the participants who have been
+primed with higher cognitive expectation before watching the robot performing
+the tasks. This suggests a form of transfer: participants changed somewhat their
+minds about robots being with however
 

### 2016-09-06 main.tex
WIP on discussion

@@
 
-\rightheader{Gazing at the Robot's Head Reflects our Tendency to Anthropomorphise}   % This should be the title, or a shortened version of the title if your title is long.
+\rightheader{Gazing at a Robot's Head Reflects our Tendency to Anthropomorphise}   % This should be the title, or a shortened version of the title if your title is long.
 \leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
-\title{Gazing at the Robot's Head Reflects our Tendency to Anthropomorphise}
+\title{Gazing at a Robot's Head Reflects our Tendency to Anthropomorphise}
 
@@
 anthropomorphise. The stimuli were short videos of `toy' interaction scenarios,
-and we did not anticipate any transfer of the anthropomorphic traits ascribed onto
-the robot seen in the videos, to the broader tendency to anthropomorphise
+and we did not anticipate any transfer of the anthropomorphic traits ascribed
+onto the robot seen in the videos, to the broader tendency to anthropomorphise
 robots in general, as assessed in the post-questionnaire. Our result challenge
-this assumption: \deltaant is significantly higher for the participants who have been
-primed with higher cognitive expectation before watching the robot performing
-the tasks. This suggests a form of transfer: participants changed somewhat their
-minds about robots being with however
+this assumption: \deltaant is significantly higher for the participants who have
+been primed with higher cognitive expectations before watching the robot
+performing the tasks. This suggests a form of transfer: participants changed
+their minds about how human-like robots are from their perception of one
+specific interaction situation with a specific robot. We did not test
+how long this effect lasts (we suspect it might quickly decrease).
 

### 2016-09-09 main.tex
Updated stats

@@
 that fixations on the head of the robot reflect how we anthropomorphize the
-machine. Besides, by comparing this gazing behaviour to a human baseline, we further
+machine. Besides, by comparing this gaze behaviour to a human baseline, we further
 show that people with a generally higher tendency to anthropomorphise exhibit
@@
 eye-tracking. By looking at the eyes fixation on the head of the robot, we show
-significantly different gazing behaviours in two experimental conditions that
+significantly different gaze behaviours in two experimental conditions that
 differ in terms of the (projected) robot's human-likeness. This eye-tracking
@@
         reciprocally (\h{3}). If this is verified, this would confirm that our
-        gazing behaviour towards agents is impacted by our tendency to
+        gaze behaviour towards agents is impacted by our tendency to
         anthropomorphise.
@@
 
-To compare gazing behaviours across the robot and human conditions, we besides
+To compare gaze behaviours across the robot and human conditions, we besides
 computed a \emph{gaze distribution difference} over the 10 AOIs ($N=10$):
@@
 scale (numerical values ranging from -2 to 2, where -2 refers to robot kind of
-task). We found a significant mean difference ($M_{\text{machine-like}}=TBD (SD=TBD)$
-\vs $M_{\text{human-like}}=TBD (SD=TDB)$) in this
-manipulation check ($F(1,54) = 29.0, p < .001$): the participants who watched
+task). We found a significant mean difference ($M_{\text{machine-like}}=-0.46
+(SD=1.21)$
+\vs $M_{\text{human-like}}=1.16 (SD=1.00)$) in this
+manipulation check ($F(1,55) = 30.73, p < .001$): the participants who watched
 stimuli in the \emph{machine-like priming} condition identified the tasks as more
@@
 \deltaant before and after the experiment shows that \deltaant is greater for the participants who watched the
-human-like tasks ($\Delta_{\text{machine-like}}=-0.44 (SD=5.23)$
-\vs $\Delta_{\text{human-like}}=3.55 (SD=4.64)$, $F(1,54) = 6.54, p < .05$\fixme{put the exact
-p value here}). In other words, after being exposed to short videos of a robot
+human-like tasks ($\Delta_{\text{machine-like}}=2.97 (SD=9.60)$
+\vs $\Delta_{\text{human-like}}=9.94 (SD=9.93)$, $F(1,55) = 7.27, p = .009$. In other words, after being exposed to short videos of a robot
 performing simple tasks, participants primed with richer cognitive
@@
 \subsection{Impact of the Tendency to Anthropomorphise on Human
-Gazing Behaviours}
+Gaze Behaviours}
 
@@
 \deltagaze and
-the initial tendency to anthropomorphise \anti{} (Pearson Correlation Coefficient $r(54) = -0.43,
-p < .001$, figure~\ref{h2}). The higher the (initial) tendency to anthropomorphise, the smaller
-the difference in gazing behaviours between the robot and human conditions. This
+the initial tendency to anthropomorphise \anti{} (Pearson Correlation
+Coefficient $r(55) = -0.38,
+p = .003$, figure~\ref{h2}). The higher the (initial) tendency to anthropomorphise, the smaller
+the difference in gaze behaviours between the robot and human conditions. This
 supports hypothesis \h{2}.
@@
 were found to be significantly higher than that in the machine-like condition
-($F(1,54) = 4.2, p < .05$\fixme{put the exact p value here}). For all other AOIs groups, the fixations across
+($F(1,55) = 4.07, p = .04$\fixme{put the exact p value here}). For all other AOIs groups, the fixations across
 machine-like and human-like conditions were almost the same. Figure~\ref{h3} shows the
@@
 our participants to anthropomorphise robots. Using our \deltagaze measure of the
-gazing behaviour similarity, we have evidenced that people with an higher
+gaze behaviour similarity, we have evidenced that people with an higher
 tendency to anthropomorphise robots, also exhibit a more similar gazing
@@
 constructed images of what robots are. And yet, our results show a significant
-correlation with gazing behaviour: the more you tend to anthropomorphise, the
+correlation with gaze behaviour: the more you tend to anthropomorphise, the
 more you look at robots the way you look at humans. This implies that the mere
